---
title: "model parameters visualized"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))
library(ggnewscale)
```


First, make basic plot that shows temperature gradient on x-axis, foraging rate on y-axis, and a geom layer for resource concentration. This will be the actual data and will be consistent between each of the model fit visualizations.

```{r, data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))
m0 <- readRDS(here("mle", "m0_f_fit.rds"))
m1 <- readRDS(here("mle", "m1_f_fit.rds"))
m2 <- readRDS(here("mle", "m2_f_fit.rds"))
m3 <- readRDS(here("mle", "m3_f_fit.rds"))
m3a <- readRDS(here("mle", "m3a_f_fit.rds"))
m4 <- readRDS(here("mle", "m4_f_fit.rds"))
m5 <- readRDS(here("mle", "m5_f_fit.rds"))
m6 <- readRDS(here("mle", "m6_f_fit.rds"))
m7 <- readRDS(here("mle", "m7_f_fit.rds"))
m7a <- readRDS(here("mle", "m7a_f_fit.rds"))
```

```{r}
m0_coef <- m0@coef
m1_coef <- m1@coef
m2_coef <- m2@coef
m3_coef <- m3@coef
m3a_coef <- m3a@coef
m4_coef <- m4@coef
m5_coef <- m5@coef
m6_coef <- m6@coef
m7_coef <- m7@coef
m7a_coef <- m7a@coef

gamma <- 2
ref_t <- 15
vol <- 15
mean_time <- mean(data$time/60/24)
mean_length <- mean(data$mm, na.rm=T)
```

Change units to mL/day. We could have also changed our estimates back to mL/min
```{r, units}
data_summ %<>% mutate(rate_mean = rate_mean*60*24,
                      rate_len_mean = rate_len_mean*60*24)
```


```{r}
temp_range <- seq(15,25,by=0.1)
resource_range <- seq(0.1,1,by=0.01)

seq_data <- tibble(temp=c(),
                   resourece=c())

for (i in 1:length(temp_range)){
  tmp <- tibble(temp = temp_range[i],
                resource = seq(0.1,1,by=0.01))
  seq_data %<>% bind_rows(., tmp)
}


seq_data %<>% mutate(temp_factor = case_when(temp==15 ~ 15,
                                             temp==20 ~ 20,
                                             temp==25 ~ 25))


```


# Fitting foraging rate

```{r}
# data_summ %>% ggplot(., aes(x=as.factor(temp), y=rate_len_mean, color=as.factor(resource))) + 
#   geom_point() + 
#   # geom_linerange(aes(ymin=rate_mean-rate_se, 
#   #                    ymax=rate_mean+rate_se)) +
#   labs(x="Temperature", y="Foraging rate (mL/day)", color="Resource")

# data_summ %>% ggplot(., aes(x=as.factor(temp), y=rate_mean, color=as.factor(resource))) + 
#   geom_point() + 
#   geom_linerange(aes(ymin=rate_mean-rate_se,
#                      ymax=rate_mean+rate_se)) +
#   labs(x="Temperature", y="Foraging rate (mL/min)", color="Resource")
# 
# data_summ %>% ggplot(., aes(x=as.factor(resource), y=rate_mean, color=as.factor(temp))) + 
#   geom_point() + 
#   geom_linerange(aes(ymin=rate_mean-rate_se, 
#                      ymax=rate_mean+rate_se)) +
#   labs(x="Resource", y="Foraging rate (mL/min)", color="Temperature")
```



Now let's get the results from the model
```{r}
m0_f <- as.numeric(m0_coef)
data_summ %<>% mutate(m0_rate = m0_f)
seq_data %<>% mutate(m0_rate = m0_f)
```


```{r, echo=F}
m0_plot <- data_summ %>% ggplot(., aes(x=as.factor(resource), 
                          y=rate_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_hline(yintercept=m0_f) +
# geom_linerange(aes(ymin=rate_mean-rate_se, 
#                  ymax=rate_mean+rate_se)) +
labs(x="Resource", y="Foraging rate (mL/min)", color="Temperature", shape="Temperature", title = "Independent model without size correction")
```


```{r}
m1_f <- as.numeric(m1_coef)
data_summ %<>% mutate(m1_rate = mm_mean^gamma*m1_f)
seq_data %<>% mutate(m1_rate = mean_length^gamma*m1_f)
```


```{r, echo=F}
m1_plot <- seq_data %>% 
ggplot(.) +
geom_line(aes(x=resource, 
               y=m1_rate)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "Size-dependent model") 
```


$$
(observed\; f) = (reference\; f)*e^{T_{A}(1/T_{R}-1/T)}  \\
$$

```{r}
m2_coef
m2_f <- as.numeric(m2_coef[1])
m2_arr <- as.numeric(m2_coef[2])

data_summ %<>% mutate(m2_rate = (mm_mean^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
seq_data %<>% mutate(m2_rate = (mean_length^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
```

```{r, echo=F}
m2_plot <- seq_data %>% filter(resource %in% c(1)) %>%
ggplot(.) +
geom_line(aes(x=temp, 
               y=m2_rate)) +
geom_point(data=data_summ, aes(x=temp, 
                          y=rate_len_mean, 
                          group = as.factor(resource), 
                          color = as.factor(resource),
                          shape = as.factor(resource))) + 
labs(x="Temperature", y="Foraging rate (mL/min)", color="Resource", shape="Resource", title = "Temperature-dependent model") 
```


$$
observed\; f  = \frac{f}{1 + fL^{\gamma}hR} \\
$$

```{r}
m3_coef
m3_f <- as.numeric(m3_coef[1])
m3_h <- as.numeric(m3_coef[2])

data_summ %<>% mutate(m3_rate = ((m3_f)/(1+m3_f*m3_h*resource)))

seq_data %<>% mutate(m3_rate=((m3_f)/(1+m3_f*m3_h*resource)))
```



```{r, echo=F}
m3_plot <- seq_data %>% filter(temp %in% c(15)) %>%
ggplot(.) +
geom_line(aes(x=resource, 
               y=m3_rate)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/min)", color="Temperature", shape="Temperature", title = "Resource-dependent model") 
```


$$
observed\; f  = \frac{f}{k + R} \\
$$

```{r}
m3a_coef
m3a_f <- as.numeric(m3_coef[1])
m3a_k <- as.numeric(m3_coef[2])

data_summ %<>% mutate(m3a_rate = ((m3a_f)/(m3a_k + resource)))

seq_data %<>% mutate(m3a_rate=((m3a_f)/(m3a_k + resource)))
```



$$
observed\; f = \frac{fe^{T_{A}(1/T_{R}-1/T)}}{1 + fe^{T_{A}(1/T_{R}-1/T)}hR} \\
$$

```{r}
m4_coef
m4_f <- as.numeric(m4_coef[1])
m4_arr <- as.numeric(m4_coef[2])
m4_h <- as.numeric(m4_coef[3])


data_summ %<>% mutate(m4_rate = ((m4_f*exp(m4_arr*(1/ref_t - 1/temp)))/
                                   (1+m4_f*exp(m4_arr*(1/ref_t - 1/temp))*m4_h*resource)))

seq_data %<>% mutate(m4_rate = ((m4_f*exp(m4_arr*(1/ref_t - 1/temp)))/
                                   (1+m4_f*exp(m4_arr*(1/ref_t - 1/temp))*m4_h*resource)))
```



```{r, echo=F}
m4_plot <- seq_data %>% na.omit() %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m4_rate,
              group=temp_factor)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "Full model") 
```

```{r}
m5_coef
m5_f <- as.numeric(m5_coef[1])
m5_arr_0.1 <- as.numeric(m5_coef[2])
m5_arr_0.5 <- as.numeric(m5_coef[3])
m5_arr_1 <- as.numeric(m5_coef[4])
m5_h <- as.numeric(m5_coef[5])

data_summ %<>% mutate(m5_arr = case_when(resource==0.1 ~ m5_arr_0.1,
                                         resource==0.5 ~ m5_arr_0.5,
                                         resource==1 ~ m5_arr_1),
                      m5_rate = ((m5_f*exp(m5_arr*(1/ref_t - 1/temp)))/
                                   (1+m5_f*exp(m5_arr*(1/ref_t - 1/temp))*m5_h*resource)))
  

seq_data %<>% mutate(m5_arr = case_when(resource==0.1 ~ m5_arr_0.1,
                                         resource==0.5 ~ m5_arr_0.5,
                                         resource==1 ~ m5_arr_1),
                     m5_rate = ((m5_f*exp(m5_arr*(1/ref_t - 1/temp)))/
                                   (1+m5_f*exp(m5_arr*(1/ref_t - 1/temp))*m5_h*resource)))
```

```{r, echo=F}
m5_plot <- seq_data %>% na.omit() %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m5_rate,
              group=temp_factor)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "Resource on temp interaction model") 
```



```{r}
m6_coef
m6_f <- as.numeric(m6_coef[1])
m6_arr <- as.numeric(m6_coef[2])
m6_h_15 <- as.numeric(m6_coef[3])
m6_h_20 <- as.numeric(m6_coef[4])
m6_h_25 <- as.numeric(m6_coef[5])


data_summ %<>% mutate(m6_h = case_when(temp==15 ~ m6_h_15,
                                       temp==20 ~ m6_h_20,
                                       temp==25 ~ m6_h_25),
                      m6_rate = ((m6_f*exp(m6_arr*(1/ref_t - 1/temp)))/
                                   (1+m6_f*exp(m6_arr*(1/ref_t - 1/temp))*m6_h*resource)))
  

seq_data %<>% mutate(m6_h = case_when(temp==15 ~ m6_h_15,
                                       temp==20 ~ m6_h_20,
                                       temp==25 ~ m6_h_25),
                     m6_rate = ((m6_f*exp(m6_arr*(1/ref_t - 1/temp)))/
                                   (1+m6_f*exp(m6_arr*(1/ref_t - 1/temp))*m6_h*resource)))
```

```{r, echo=F}
m6_plot <- seq_data %>% na.omit() %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m6_rate,
              group=temp_factor)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "Temp on resource interaction model") 
```


```{r}
m7_coef
m7_f <- as.numeric(m7_coef[1])
m7_arr_0.1 <- as.numeric(m7_coef[2])
m7_arr_0.5 <- as.numeric(m7_coef[3])
m7_arr_1 <- as.numeric(m7_coef[4])
m7_h_15 <- as.numeric(m7_coef[5])
m7_h_20 <- as.numeric(m7_coef[6])
m7_h_25 <- as.numeric(m7_coef[7])

data_summ %<>% mutate(m7_h = case_when(temp==15 ~ m7_h_15,
                                       temp==20 ~ m7_h_20,
                                       temp==25 ~ m7_h_25),
                      m7_arr = case_when(resource==0.1 ~ m7_arr_0.1,
                                         resource==0.5 ~ m7_arr_0.5,
                                         resource==1 ~ m7_arr_1),
                      m7_rate = ((m7_f*exp(m7_arr*(1/ref_t - 1/temp)))/
                                   (1+m7_f*exp(m7_arr*(1/ref_t - 1/temp))*m7_h*resource)))
  

seq_data %<>% mutate(m7_h = case_when(temp==15 ~ m7_h_15,
                                       temp==20 ~ m7_h_20,
                                       temp==25 ~ m7_h_25),
                     m7_arr = case_when(resource==0.1 ~ m7_arr_0.1,
                                         resource==0.5 ~ m7_arr_0.5,
                                         resource==1 ~ m7_arr_1),
                     m7_rate = ((m7_f*exp(m7_arr*(1/ref_t - 1/temp)))/
                                   (1+m7_f*exp(m7_arr*(1/ref_t - 1/temp))*m7_h*resource)))
```

```{r, echo=F}
m7_plot <- seq_data %>% na.omit() %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m7_rate,
              group=temp_factor)) +
geom_point(data=data_summ, aes(x=resource, 
                          y=rate_len_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "Full interaction model") 
```



```{r}
m0_plot
m1_plot
m2_plot
m3_plot
m4_plot
m5_plot
m6_plot
m7_plot

ggsave("m0_fit.png", m0_plot, path=here("mle/fit_plots"))
ggsave("m1_fit.png", m1_plot, path=here("mle/fit_plots"))
ggsave("m2_fit.png", m2_plot, path=here("mle/fit_plots"))
ggsave("m3_fit.png", m3_plot, path=here("mle/fit_plots"))
#ggsave("m4_fit.png", m4_plot, path=here("mle/fit_plots"))
ggsave("m5_fit.png", m5_plot, path=here("mle/fit_plots"))
ggsave("m6_fit.png", m6_plot, path=here("mle/fit_plots"))
ggsave("m7_fit.png", m7_plot, path=here("mle/fit_plots"))
```




# Fitting final concentration

I am having difficulty relating foraging rate from our models to foraging rate from the data so I can do this slightly more explicitly by comparing the average amount consumed over the assay between the models and the data. This is actually what we were using to calculate our residuals.

```{r}
data_summ %>% ggplot(., aes(x=as.factor(temp), y=conc_mean, color=as.factor(resource))) + 
  geom_point() + 
  geom_linerange(aes(ymin=conc_mean-conc_se, 
                     ymax=conc_mean+conc_se)) +
  labs(x="Temperature", y="Final concentration", color="Resource")

data_summ %>% ggplot(., aes(x=as.factor(resource), y=conc_mean, color=as.factor(temp))) + 
  geom_point() + 
  geom_linerange(aes(ymin=conc_mean-conc_se, 
                     ymax=conc_mean+conc_se)) +
  labs(x="Resource", y="Final concentration", color="Temperature")
```


For each, I will define the models and then loop through each treatment and use the solver to get the final resource concentration under each treatment under each model
```{r}
model_conc <- data_summ %>% dplyr::select(temp, resource, rate_mean, 
                                          conc_mean, conc_se, 
                                          amt_mean, time_mean, mm_mean, ID) %>% ungroup()
```



```{r}
m0_sim <- function(f, R, temp){
    m0_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -f*R
      res <- c(dR)
      list(res)}
      )
    }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m0_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```

```{r}
seq_data %<>% mutate(m0_end = mapply(m0_sim, f=m0_f, R=seq_data$resource, temp=seq_data$temp))

model_conc %<>% mutate(m0_conc = mapply(m0_sim, f=m0_f, R=model_conc$resource, temp=model_conc$temp))
```



```{r}
m1_sim <- function(f, R, temp, length, gamma){
  m1_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -(length^gamma)*f*R
      res <- c(dR)
      list(res)}
      )
  }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m1_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```


```{r}
seq_data %<>% mutate(m1_end = mapply(m1_sim, f=m1_f, R=seq_data$resource, temp=seq_data$temp,
                                     length=mean_length,
                                     gamma=gamma))

model_conc %<>% mutate(m1_conc = mapply(m1_sim, f=m1_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma))

```


```{r}
m2_sim <- function(f, R, temp, length, gamma, arr_t, ref_t){
  m2_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*R
      res <- c(dR)
      list(res)}
      )
  }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m2_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```


```{r}
seq_data %<>% mutate(m2_end = mapply(m2_sim, f=m2_f, R=seq_data$resource, temp=seq_data$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=m2_arr,
                                     ref_t=15))
model_conc %<>% mutate(m2_conc = mapply(m2_sim, f=m2_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=m2_arr,
                                     ref_t=15))
```



```{r}
m3_sim <- function(f, R, temp, length, gamma, h){
  m3_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -((f*length^gamma*R)/(1+f*h*R))
      res <- c(dR)
      list(res)}
      )
  }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma,
              h=h*vol)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m3_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```


```{r}
seq_data %<>% mutate(m3_end = mapply(m3_sim, f=m3_f, R=seq_data$resource, temp=seq_data$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     h=m3_h))

model_conc %<>% mutate(m3_conc = mapply(m3_sim, f=m3_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     h=m3_h))
```

```{r}
m3a_sim <- function(f, R, temp, length, gamma, k){
  m3a_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -((f*length^gamma*R)/(k + R))
      res <- c(dR)
      list(res)}
      )
  }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma,
              k=k)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m3a_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```


```{r}
seq_data %<>% mutate(m3a_end = mapply(m3a_sim, f=m3a_f, R=seq_data$resource, temp=seq_data$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     k=m3a_k))

model_conc %<>% mutate(m3a_conc = mapply(m3a_sim, f=m3a_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     k=m3a_k))
```


```{r}
m4_sim <- function(f, R, temp, length, gamma, arr_t, ref_t, h){
  m4_num_sol <- function(t, x, params){
    R <- x[1]
    with(as.list(params),{
      dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*h*(length^gamma)*R))
      res <- c(dR)
      list(res)}
      )
  }
  times <- seq(0,mean_time,by=0.01)
  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              h=h*vol)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m4_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```

```{r}
seq_data %<>% mutate(m4_end = mapply(m4_sim, f=m4_f, R=seq_data$resource, temp=seq_data$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=m4_arr,
                                     ref_t=15,
                                     h=m4_h))

model_conc %<>% mutate(m4_conc = mapply(m4_sim, f=m4_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=m4_arr,
                                     ref_t=15,
                                     h=m4_h))
```

```{r}
m7_coef
m7_f <- as.numeric(m7_coef[1])

```


```{r}
m7_sim <- function(f, R, temp, length, gamma, arr_t, ref_t, h){
  
  m4_num_sol <- function(t, x, params){
      R <- x[1]
      with(as.list(params),{
        dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/
                  (1+f*exp(arr_t*(1/ref_t - 1/temp))*h*(length^gamma)*R))
        res <- c(dR)
        list(res)}
        )
  }
  
    times <- seq(0,mean_time,by=0.01)

  params <- c(f=m0_f/vol,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              h=h*vol)
  xstart <- c(R=R)
  output <- as.data.frame(lsoda(xstart, times, m4_num_sol, params))
  r_end <- slice_max(output, time)[,2]
  return(r_end)
}
```

```{r}
seq_data_subset <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>% filter(resource %in% c(0.1, 0.5, 1))

```

```{r}
seq_data_subset %<>% mutate(m7_end = mapply(m7_sim, f=m7_f, R=seq_data_subset$resource, temp=seq_data_subset$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=seq_data_subset$m7_arr,
                                     ref_t=15,
                                     h=seq_data_subset$m7_h))

model_conc %<>% mutate(m7_conc = mapply(m7_sim, f=m7_f, R=model_conc$resource, temp=model_conc$temp,
                                     length=mean_length,
                                     gamma=gamma,
                                     arr_t=seq_data_subset$m7_arr,
                                     ref_t=15,
                                     h=seq_data_subset$m7_h))
```







```{r, echo=F}
m0_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Independent model without size correction") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m0_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m0_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Independent model without size correction") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m0_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")
```

```{r, echo=F}
m0_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m0_end,
              group=temp)) +
geom_point(data=model_conc, aes(x=resource, 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Independent model w/0 size correction") 
```



```{r, echo=F}
m1_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Independent model with size correction") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m1_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m1_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Independent model with size correction") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m1_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")
```


```{r, echo=F}
m1_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m1_end,
              group=temp)) +
geom_point(data=model_conc, aes(x=resource, 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Independent model w/ size correction") 
```


```{r, echo=F}
m2_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Temperature-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m2_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m2_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Temperature-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m2_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")


```

```{r, echo=F}
m2_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m2_end,
              group=temp,
              color=as.factor(temp))) +
new_scale_color() +
geom_point(data=model_conc, aes(x=resource, 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Temperature-dependent model") 

# m2_plot_conc <- seq_data %>% filter(resource %in% c(0.1, 0.5, 1)) %>%
# ggplot(.) +
# geom_line(aes(x=temp, 
#               y=m2_end,
#               group=resource)) +
# geom_point(data=model_conc, aes(x=temp, 
#                           y=conc_mean, 
#                           group = as.factor(resource), 
#                           color = as.factor(resource),
#                           shape = as.factor(resource))) + 
# labs(x="Temperature", y="Resource concentration", color="Resource", shape="Resource", title = "Temperature-dependent model") 
```


```{r, echo=F}
m3_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Resource-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m3_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m3_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Resource-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m3_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")
```

```{r, echo=F}
m3_plot_conc <- seq_data %>% filter(resource %in% c(0.1, 0.5, 1)) %>%
ggplot(.) +
geom_line(aes(x=temp, 
              y=m3_end,
              group=resource,
              color=as.factor(resource))) +
new_scale_color() +
geom_point(data=model_conc, aes(x=temp, 
                          y=conc_mean, 
                          group = as.factor(resource), 
                          color = as.factor(resource),
                          shape = as.factor(resource))) + 
labs(x="Temperature", y="Resource concentration", color="Resource", shape="Resource", title = "Resource-dependent model") 

# m3_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
# ggplot(.) +
# geom_line(aes(x=resource, 
#               y=m3_end,
#               group=temp,
#               color=as.factor(temp))) +
# new_scale_color() +
# geom_point(data=model_conc, aes(x=resource, 
#                           y=conc_mean, 
#                           group = as.factor(temp), 
#                           color = as.factor(temp),
#                           shape = as.factor(temp))) + 
# labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Resource-dependent model") 
```


```{r, echo=F}
m3a_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Resource-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m3a_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m3a_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Resource-dependent model") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m3a_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")
```

```{r, echo=F}
m3a_plot_conc <- seq_data %>% filter(resource %in% c(0.1, 0.5, 1)) %>%
ggplot(.) +
geom_line(aes(x=temp, 
              y=m3a_end,
              group=resource,
              color=as.factor(resource))) +
new_scale_color() +
geom_point(data=model_conc, aes(x=temp, 
                          y=conc_mean, 
                          group = as.factor(resource), 
                          color = as.factor(resource),
                          shape = as.factor(resource))) + 
labs(x="Temperature", y="Resource concentration", color="Resource", shape="Resource", title = "Resource-dependent model") 

# m3_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
# ggplot(.) +
# geom_line(aes(x=resource, 
#               y=m3_end,
#               group=temp,
#               color=as.factor(temp))) +
# new_scale_color() +
# geom_point(data=model_conc, aes(x=resource, 
#                           y=conc_mean, 
#                           group = as.factor(temp), 
#                           color = as.factor(temp),
#                           shape = as.factor(temp))) + 
# labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Resource-dependent model") 
```


```{r, echo=F}
m4_temp <- model_conc %>% ggplot(., aes(x=as.factor(temp),
                          y=conc_mean,
                          group = as.factor(resource),
                          color = as.factor(resource),
                          shape = as.factor(resource))) +
geom_point() +
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Temperature", y="Final Concentration", color="Resource", shape="Resource", title = "Full model") +
new_scale_color() +
geom_point(aes(x=as.factor(temp),
               y=m4_conc,
               shape=as.factor(resource))) +
scale_color_manual(name="",values="black")


m4_resource <- model_conc %>% ggplot(., aes(x=as.factor(resource), 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
geom_point() + 
geom_linerange(aes(ymin=conc_mean-conc_se, ymax=conc_mean+conc_se)) +
labs(x="Resource", y="Final Concentration", color="Temperature", shape="Temperature", title = "Full model") +
new_scale_color() +
geom_point(aes(x=as.factor(resource), 
               y=m4_conc, 
               shape=as.factor(temp))) +
scale_color_manual(name="",values="black")
```

```{r, echo=F}
m4_plot_conc <- seq_data %>% filter(temp %in% c(15, 20, 25)) %>%
ggplot(.) +
geom_line(aes(x=resource, 
              y=m4_end,
              group=temp,
              color=as.factor(temp))) +
new_scale_color() +
geom_point(data=model_conc, aes(x=resource, 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Full model") 
```


```{r, echo=F}
m7_plot_conc <- seq_data_subset %>% 
ggplot(.) +
geom_line(aes(x=resource, 
              y=m7_end,
              group=temp,
              color=as.factor(temp))) +
new_scale_color() +
geom_point(data=model_conc, aes(x=resource, 
                          y=conc_mean, 
                          group = as.factor(temp), 
                          color = as.factor(temp),
                          shape = as.factor(temp))) + 
labs(x="Resource", y="Resource concentration", color="Temperature", shape="Temperature", title = "Full model") 
```


```{r, include=F}
m0_temp
m1_temp
m2_temp
m3_temp
m4_temp
```


```{r, include=F}
m0_resource
m1_resource
m2_resource
m3_resource
m4_resource
```

```{r}
m1_plot_conc
m2_plot_conc
m3_plot_conc
m4_plot_conc
m7_plot_conc
```


