---
title: "foraging rate estimates"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Objective: recreate results from Alex's script

```{r packages, message=FALSE}
library(here)
library(tidyverse)
library(deSolve)
library(magrittr)
library(bbmle)
library(latex2exp)
library(AICcmodavg)
```

```{r, set theme}
theme_set(theme_minimal())

```


```{r, real data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


vol <- 15
```

Some of the lengths are missing so we impute these missing values by using the average length from that treatment
```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))
```

Test with Alex's method of converting rfu to dry weight
```{r}
# data %<>% mutate(amt_rem = read/299.4443)
# data %<>% mutate(resource = control_read/299.4443)
```



# Model 0 - Basic model


Let's try this with the same units as the foraging rate data. ml/min. So R should be mgC/mL and S should be hosts/mL
$$
\frac{dR}{dt} = -fRS \\
$$

```{r, m0_num_sol}
m0_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -f*R
    res <- c(dR)
    list(res)}
    )
}

```



```{r, m0_sim}
m0_sim <- function(R, time, f){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f)
  output <- as.data.frame(lsoda(y=xstart, times, m0_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m0_ll}
m0_ll <- function(f){
  data <- tmp
  m0_end <- as.data.frame(mapply(m0_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol))
  colnames(m0_end) <- "m0_end"
  data$end <- m0_end$m0_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```



```{r, m0_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m0_f_fit <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10),
                control=list(parscale=c(f=10), maxit=10000))
end_time <- Sys.time()
m0_runtime <- end_time - start_time
m0_runtime

coef(m0_f_fit)

saveRDS(m0_f_fit, file = here("mle","m0_f_fit.rds"))

```

```{r, m0_f_fit output}
summary(readRDS(here("mle","m0_f_fit.rds")))
```


# Model 1 - Independent model

Recreate Alex's results from Model 1

$$
\frac{dR}{dt} = -L^{\gamma} fRS\\
$$

```{r, m1_num_sol}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*R
    res <- c(dR)
    list(res)}
    )
}

```

```{r, m1_sim}
m1_sim <- function(R, time, f, length, gamma){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m1_ll}
m1_ll <- function(f){
  data <- tmp
  m1_end <- as.data.frame(mapply(m1_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2))
  colnames(m1_end) <- "m1_end"
  data$end <- m1_end$m1_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


Now we use the optimizer
```{r, m1_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m1_f_fit <- mle2(minuslogl=m1_ll, skip.hessian=T, #method="Nelder-Mead", 
              start=list(f=10),
              control=list(parscale=c(f=10), maxit=10000))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_f_fit)

saveRDS(m1_f_fit, file = here("mle","m1_f_fit.rds"))
```

```{r, m1_f_fit}
summary(readRDS(here("mle","m1_f_fit.rds")))
```



# Model 2 - Temperature-dependent model


$$
\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\\
$$


```{r, m2_num_sol}
m2_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*R
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m2_sim}
m2_sim <- function(R, time, f, length, gamma, ref_t, arr_t, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp)
  output <- as.data.frame(lsoda(y=xstart, times, m2_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m2_ll}
m2_ll <- function(f, arr_t){
  data <- tmp
  m2_end <- as.data.frame(mapply(m2_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp))
  colnames(m2_end) <- "m2_end"
  data$end <- m2_end$m2_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```





```{r, m2_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m2_f_fit <- mle2(m2_ll,
                skip.hessian = T,
                start=list(f=5,
                           arr_t=50),
                method = "L-BFGS-B",
                lower = c(0, 0),
                upper = c(Inf, Inf),
                control=list(parscale=c(f=5, T_A=50), maxit=10000))

end_time <- Sys.time()
m2_runtime <- end_time - start_time
m2_runtime

coef(m2_f_fit)

saveRDS(m2_f_fit, file = here("mle","m2_f_fit.rds"))
```

```{r, m2_f_fit}
summary(readRDS(here("mle", "m2_f_fit.rds")))
```




# Model 3 - Resource-dependent model

I try to incorporate resource-dependence by using an equation for the type II functional response.



$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{1 + fhR} \\
$$




```{r, m3_num_sol}
m3_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(1+f*h*R))
    res <- c(dR)
    list(res)}
    )
}
```


```{r, m3_sim}
m3_sim <- function(R, time, f, length, gamma, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m3_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m3_ll}
m3_ll <- function(f, h){
  data <- tmp
  output <- as.data.frame(mapply(m3_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, h=h*data$vol))
  colnames(output) <- "end"
  data$end <- output$end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r, m3_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m3_f_fit <- mle2(m3_ll,
                skip.hessian = T,
                start=list(f=40,
                           h=0.2),
                method = "L-BFGS-B",
                lower = c(0, 0),
                upper = c(Inf, Inf),
                control=list(parscale=c(f=40, h=0.2), maxit=10000))
end_time <- Sys.time()
m3_runtime <- end_time-start_time
m3_runtime

coef(m3_f_fit)

saveRDS(m3_f_fit, file = here("mle","m3_f_fit.rds"))
```

```{r, m3_f_fit}
summary(readRDS(here("mle", "m3_f_fit.rds")))
```

# Model 3b - Half-Saturation Method


I try to incorporate resource-dependence by using an equation for the type II functional response.



$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{k + R} \\
$$




```{r, m3a_num_sol}
m3a_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(k+R))
    res <- c(dR)
    list(res)}
    )
}
```


```{r, m3a_sim}
m3a_sim <- function(R, time, f, length, gamma, k){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              k=k)
  output <- as.data.frame(lsoda(y=xstart, times, m3a_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m3a_ll}
m3a_ll <- function(f, k){
  data <- tmp
  output <- as.data.frame(mapply(m3a_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, k=k))
  colnames(output) <- "end"
  data$end <- output$end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r, m3a_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m3a_f_fit <- mle2(m3a_ll,
                skip.hessian = T,
                start=list(f=5,
                           k=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0),
                upper = c(Inf, Inf),
                control=list(parscale=c(f=5, k=0.1), maxit=10000))
end_time <- Sys.time()
m3a_runtime <- end_time-start_time
m3a_runtime

coef(m3a_f_fit)

saveRDS(m3a_f_fit, file = here("mle","m3a_f_fit.rds"))
```

```{r, m3a_f_fit}
summary(readRDS(here("mle", "m3_f_fit.rds")))
```



# Model 4 - Temperature and resource-dependent model

I try to incorporate both here by just smashing everything together.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{1 + fe^{T_{A}(1/T_{R}-1/T)}hR} \\
$$


```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m4_ll}
m4_ll <- function(f, arr_t, h){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, h=h*data$vol))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```



```{r, m4_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m4_f_fit <- mle2(m4_ll,
                skip.hessian = T,
                start=list(f=5, arr_t=50, h=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=5, arr_t=50, h=0.1), maxit=10000))
end_time <- Sys.time()
m4_runtime <- end_time-start_time
m4_runtime

coef(m4_f_fit)

saveRDS(m4_f_fit, file = here("mle","m4_f_fit.rds"))
```

```{r, m4_f_fit}
summary(readRDS(here("mle","m4_f_fit.rds")))
```


# Model 4a - Temperature and resource-dependent model - half saturation method

I try to incorporate both here by just smashing everything together.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{k + R} \\
$$


```{r, m4_num_sol}
m4a_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(k+R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4a_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, k){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              k=k)
  output <- as.data.frame(lsoda(y=xstart, times, m4a_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m4_ll}
m4a_ll <- function(f, arr_t, k){
  data <- tmp
  output <- as.data.frame(mapply(m4a_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, k=k))
  colnames(output) <- "end"
  data$end <- output$end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r, m4_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m4a_f_fit <- mle2(m4a_ll,
                skip.hessian = T,
                start=list(f=5, arr_t=50, k=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=5, arr_t=50, k=0.1), maxit=10000))
end_time <- Sys.time()
m4a_runtime <- end_time-start_time
m4a_runtime

coef(m4a_f_fit)

saveRDS(m4a_f_fit, file = here("mle","m4a_f_fit.rds"))
```

```{r, m4_f_fit}
summary(readRDS(here("mle","m4a_f_fit.rds")))
```


# Parameter Check

How different are the parameters for each treatment?

```{r}
test_fit <- list(c())
for(i in 1:length(treatment_IDs)){
  tmp <- data %>% filter(treatment_ID==treatment_IDs[i])
  test_fit[i] <- mle2(m4_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=1), maxit=10000))
}
```

```{r}
for(i in 1:length(treatment_IDs)){
  print(test_fit[[i]]@coef)
}
```



# Model 5 - Resource on Temperature Interaction

This model uses a different Arrhenius coefficient for each resource level to see if there is an effect of resource level on the temperature effect.

```{r, m5_ll}
m5_ll <- function(f, arr_t_0.1, arr_t_0.5, arr_t_1, h){
  arr_t_vec <- c(arr_t_0.1, arr_t_0.5, arr_t_1)
  nll_vec <- c()
  for (i in 1:length(resource_IDs)){
  data <- tmp %>% filter(resource == resource_IDs[i])
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t_vec[i], ref_t=15, temp=data$temp, h=h))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_vec[i] <- -sum(nll, na.rm = T)
  }
  sum(nll_vec)
}
```

```{r}
start_time <- Sys.time()
tmp <- data
m5_f_fit <- mle2(m5_ll,
                skip.hessian = T,
                start=list(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h=1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h=1), maxit=10000))
end_time <- Sys.time()
m5_runtime <- end_time-start_time
m5_runtime

coef(m5_f_fit)

saveRDS(m5_f_fit, file = here("mle","m5_f_fit.rds"))
```


# Model 6 - Temperature on Resource Interaction

This model uses a different handling time for each temperature level to see if there is an effect of temperature on the resource effect.

```{r}
m6_ll <- function(f, arr_t, h_15, h_20, h_25){
  h_vec <- c(h_15, h_20, h_25)
  nll_vec <- c()
  for (i in 1:length(temp_IDs)){
  data <- tmp %>% filter(temp == temp_IDs[i])
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, h=h_vec[i]))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_vec[i] <- -sum(nll, na.rm = T)
  }
  sum(nll_vec)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m6_f_fit <- mle2(m6_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h_15=1, h_20=1, h_25=1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h_15=1, h_20=1, h_25=1), maxit=10000))
end_time <- Sys.time()
m6_runtime <- end_time-start_time
m6_runtime

coef(m6_f_fit)

saveRDS(m6_f_fit, file = here("mle","m6_f_fit.rds"))
```


# Model 7 - Full Interaction Model

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.

```{r}
for(i in 1:3){
  for(j in 1:3){
    print(i*3 + j - 3) #fun check to make sure we count from 1 to 9
  }
}
```

```{r}
m7_ll <- function(f, arr_t_0.1, arr_t_0.5, arr_t_1, h_15, h_20, h_25){
  arr_t_vec <- c(arr_t_0.1, arr_t_0.5, arr_t_1)
  h_vec <- c(h_15, h_20, h_25)
  nll_vec <- c()
  for (i in 1:length(temp_IDs)){
  data <- tmp %>% filter(temp == temp_IDs[i])

    for (j in 1:length(resource_IDs)){
    data <- tmp %>% filter(resource == resource_IDs[j])
    output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                   length=data$mm, gamma=2, arr_t=arr_t_vec[j], ref_t=15, temp=data$temp, h=h_vec[i]))
    colnames(output) <- "endpoint"
    data$end <- output$endpoint
    data %<>% mutate(resid = log(end) - log(amt_rem))
    
      nll <- dnorm(data$resid, 
                   mean = 0, 
                   sd = sd(data$resid, na.rm = T), 
                   log = T)
      nll_vec[i*3 + j - 3] <- -sum(nll, na.rm = T)
    }
  }
  sum(nll_vec)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7_f_fit <- mle2(m7_ll,
                skip.hessian = T,
                start=list(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h_15=1, h_20=1, h_25=1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h_15=1, h_20=1, h_25=1), maxit=10000))
end_time <- Sys.time()
m7_runtime <- end_time-start_time
m7_runtime

coef(m7_f_fit)

saveRDS(m7_f_fit, file = here("mle","m7_f_fit.rds"))
```





Model results
```{r, results}
# summary(readRDS(here("mle","m0_f_fit.rds"))) #no size correction
# summary(readRDS(here("mle","m1_f_fit.rds"))) #with size correction
# summary(readRDS(here("mle","m2_f_fit.rds"))) #temperature-dependent
# summary(readRDS(here("mle","m3_f_fit.rds"))) #resource-dependent
# summary(readRDS(here("mle","m4_f_fit.rds"))) #temperature and resource-dependent
# summary(readRDS(here("mle","m5_f_fit.rds"))) #resource on temp effect
# summary(readRDS(here("mle","m6_f_fit.rds"))) #temp on resource effect
# summary(readRDS(here("mle","m7_f_fit.rds"))) #full interaction
```



```{r, AIC}
m0 <- readRDS(here("mle","m0_f_fit.rds"))
m1 <- readRDS(here("mle","m1_f_fit.rds"))
m2 <- readRDS(here("mle","m2_f_fit.rds"))
m3 <- readRDS(here("mle","m3_f_fit.rds"))
m3a <- readRDS(here("mle","m3a_f_fit.rds"))
m4 <- readRDS(here("mle","m4_f_fit.rds"))
m4a <- readRDS(here("mle","m4a_f_fit.rds"))
m5 <- readRDS(here("mle","m5_f_fit.rds"))
m6 <- readRDS(here("mle","m6_f_fit.rds"))
m7 <- readRDS(here("mle","m7_f_fit.rds"))
```

```{r}
m0@coef
m1@coef
m2@coef
m3@coef
m3a@coef
m4@coef
m4a@coef
m5@coef
m6@coef
m7@coef
```

```{r}
m0@min
m1@min
m2@min
m3@min
m3a@min
m4@min
m4a@min
m5@min
m6@min
m7@min
```


```{r}
getAIC <- function(n, L){
  return(2*length(n)-(2*L))
}
```


```{r}
getAIC(m0@coef, m0@min)
getAIC(m1@coef, m1@min)
getAIC(m2@coef, m2@min)
getAIC(m3@coef, m3@min)
getAIC(m3a@coef, m3a@min)
getAIC(m4@coef, m4@min)
getAIC(m4a@coef, m4a@min)
getAIC(m5@coef, m5@min)
getAIC(m6@coef, m6@min)
getAIC(m7@coef, m7@min)
```


