---
title: "bootstrap f"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))


```

Objective: Bootstrap confidence intervals for f and u and associated parameters for the best fitting model from the model comparison

Which model is the best fitting model?
```{r}
m5a_u_f_fit <- readRDS(file = here("mle", "final", "m5a_fit_alt.rds"))
```


In order to bootstrap confidence intervals around the estimate, we will resample with replacement from the data used to generate these estimates. We will do this many times (~1000) and measure quantiles of the data to understand the bounds in which 95% of the estimates lie.

```{r}
source(here("model_fitting", "combined", "final_prep.R")) #data, global variables and functions
```


```{r}
dataset %<>% filter(exposed==T)
life_data <- dataset
fora_data <- data
```


```{r}
m5a_u_est <- coef(m5a_u_f_fit)[1]
m5a_f_est <- coef(m5a_u_f_fit)[2]
m5a_arr_est <- coef(m5a_u_f_fit)[3]
m5a_arr_u_est <- coef(m5a_u_f_fit)[4]
m5a_h_est <- coef(m5a_u_f_fit)[5]
m5a_w_est <- coef(m5a_u_f_fit)[6]
m5a_rho_15_est <- coef(m5a_u_f_fit)[7]
m5a_rho_20_est <- coef(m5a_u_f_fit)[8]
m5a_rho_25_est <- coef(m5a_u_f_fit)[9]
```



We want to subset the data randomly but we don't want to oversample from some treatments and undersample from other treatments.

This is just a test
```{r, eval=F}
data_boot <- data %>% 
  group_by(treatment_ID) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- data %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

jkl <- data_boot %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

asdf
jkl
```


```{r}
dataset_boot <- dataset %>% 
  group_by(treatment) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- dataset %>% group_by(treatment) %>%
  summarize(mean = mean(inf_status),
            n = n())

jkl <- dataset_boot %>% group_by(treatment) %>%
  summarize(mean = mean(inf_status),
            n = n())

asdf
jkl
```


slice_sample is set to keep the amount of data per treatment the same (30), but resamples from the data with replacement which causes the means to be different. It looks like it is working!



```{r, m4_ll}
m5a_ll <- function(u, f, arr_t_f, arr_t_u, h, w, rho_15, rho_20, rho_25){
  data <- boot_data
  R_end <- as.data.frame(mapply(m4_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*exp(w*data$temp),
                                temp = data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  
  rho_vec <- c(rho_15, rho_20, rho_25)
  
  for(i in 1:3){
  exp_data <- boot_dataset %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  }
  return(nll_sum)
}
```




Finally, we use our optimizer to get the maximum likelihood estimate for all parameters
We'll include the bootstrapping here

```{r, 00}

  iterations <- 1
  
  boot_00 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_00[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est),
                                  maxit = 1000),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```
 


```{r}

  iterations <- 20
  
  boot_01 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_01[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est)),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


```{r}

  iterations <- 20
  
  boot_02 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_02[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est)),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


```{r}

  iterations <- 20
  
  boot_03 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_03[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est)),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


```{r}

  iterations <- 20
  
  boot_04 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_04[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est)),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r}

  iterations <- 20
  
  boot_05 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      boot_05[[i]] <- mle2(m5a_ll, start=list(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est), 
                     control=list(parscale = c(u = m5a_u_est,
                                        f= m5a_f_est, 
                                        arr_t_f= m5a_arr_est,
                                        arr_t_u= m5a_arr_u_est,
                                        h= m5a_h_est,
                                        w= m5a_w_est,
                                        rho_15= m5a_rho_15_est,
                                     rho_20= m5a_rho_20_est,
                                     rho_25= m5a_rho_25_est)),
                     skip.hessian=F, method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r}
beet <- c(boot_00, boot_01, boot_02, boot_03)
```


```{r}
saveRDS(beet, file = here("model_fitting", "combined", "beet", "80_051224.rds"))
#mod_f_boot <- readRDS(file = here("model_fitting", "combined", "beet", "25_050824.rds"))
```


```{r}
tib_length <- length(mod_f_boot)

mod_boot_coefs <- tibble(f = rep_len(0, tib_length),
                         u = rep_len(0, tib_length),
                         arr = rep_len(0, tib_length),
                         arr_u = rep_len(0, tib_length),
                         h = rep_len(0, tib_length),
                         w = rep_len(0, tib_length),
                         rho_15 = rep_len(0, tib_length),
                         rho_20 = rep_len(0, tib_length),
                         rho_25 = rep_len(0, tib_length))


for(i in 1:length(mod_f_boot)){
  if(mod_f_boot[[i]]@details[4] == 52){
    print(paste(i, "convergence_failure", sep="_"))
    mod_boot_coefs$f[i] <- NA
    mod_boot_coefs$u[i] <- NA
    mod_boot_coefs$arr[i] <- NA
    mod_boot_coefs$arr_u[i] <- NA
    mod_boot_coefs$h[i] <- NA
    mod_boot_coefs$w[i] <- NA
    mod_boot_coefs$rho[i] <- NA
  }
  else if(mod_f_boot[[i]]@min == 0){
    print(paste(i, "zero_ll", sep="_"))
    mod_boot_coefs$f[i] <- NA
    mod_boot_coefs$u[i] <- NA
    mod_boot_coefs$arr[i] <- NA
    mod_boot_coefs$arr_u[i] <- NA
    mod_boot_coefs$h[i] <- NA
    mod_boot_coefs$w[i] <- NA
    mod_boot_coefs$rho[i] <- NA
  }
  else{
  boot_coef <- coef(mod_f_boot[[i]])
  mod_boot_coefs$u[i] <- as.numeric(boot_coef[1])
  mod_boot_coefs$f[i] <- as.numeric(boot_coef[2])
  mod_boot_coefs$arr[i] <- as.numeric(boot_coef[3])
  mod_boot_coefs$arr_u[i] <- as.numeric(boot_coef[4])
  mod_boot_coefs$h[i] <- as.numeric(boot_coef[5])
  mod_boot_coefs$w[i] <- as.numeric(boot_coef[6])
  mod_boot_coefs$rho_15[i] <- as.numeric(boot_coef[7])
  mod_boot_coefs$rho_20[i] <- as.numeric(boot_coef[8])
  mod_boot_coefs$rho_25[i] <- as.numeric(boot_coef[9])
  }
}
```


```{r}
mod_boot_coefs %<>% drop_na()

mod_boot_coefs %>% ggplot(., aes(x = f)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = u)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = arr)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = arr_u)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = h)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = w)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_15)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_20)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_25)) + geom_histogram()
```




quantiles
```{r}
mod_quantiles <- tibble(id = c("est", "mean", "lower.025", "upper.975"),
                        f = NA,
                        u = NA,
                        arr = NA,
                        arr_u = NA,
                        h = NA,
                        w = NA,
                        rho_15 = NA,
                        rho_20 = NA,
                        rho_25 = NA)

mod_quantiles$f[1] <- coef(m5a_u_f_fit)[2]
mod_quantiles$f[2] <- mean(mod_boot_coefs$f)
mod_quantiles$f[3] <- quantile(mod_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$f[4] <- quantile(mod_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$u[1] <- coef(m5a_u_f_fit)[1]
mod_quantiles$u[2] <- mean(mod_boot_coefs$u)
mod_quantiles$u[3] <- quantile(mod_boot_coefs$u, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$u[4] <- quantile(mod_boot_coefs$u, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$arr[1] <- coef(m5a_u_f_fit)[3]
mod_quantiles$arr[2] <- mean(mod_boot_coefs$arr)
mod_quantiles$arr[3] <- quantile(mod_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$arr[4] <- quantile(mod_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$arr_u[1] <- coef(m5a_u_f_fit)[4]
mod_quantiles$arr_u[2] <- mean(mod_boot_coefs$arr_u)
mod_quantiles$arr_u[3] <- quantile(mod_boot_coefs$arr_u, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$arr_u[4] <- quantile(mod_boot_coefs$arr_u, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$h[1] <- coef(m5a_u_f_fit)[5]
mod_quantiles$h[2] <- mean(mod_boot_coefs$h)
mod_quantiles$h[3] <- quantile(mod_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$h[4] <- quantile(mod_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$w[1] <- coef(m5a_u_f_fit)[6]
mod_quantiles$w[2] <- mean(mod_boot_coefs$w)
mod_quantiles$w[3] <- quantile(mod_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$w[4] <- quantile(mod_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$rho_15[1] <- coef(m5a_u_f_fit)[7]
mod_quantiles$rho_15[2] <- mean(mod_boot_coefs$rho_15)
mod_quantiles$rho_15[3] <- quantile(mod_boot_coefs$rho_15, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_15[4] <- quantile(mod_boot_coefs$rho_15, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$rho_20[1] <- coef(m5a_u_f_fit)[8]
mod_quantiles$rho_20[2] <- mean(mod_boot_coefs$rho_20)
mod_quantiles$rho_20[3] <- quantile(mod_boot_coefs$rho_20, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_20[4] <- quantile(mod_boot_coefs$rho_20, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$rho_25[1] <- coef(m5a_u_f_fit)[9]
mod_quantiles$rho_25[2] <- mean(mod_boot_coefs$rho_25)
mod_quantiles$rho_25[3] <- quantile(mod_boot_coefs$rho_25, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_25[4] <- quantile(mod_boot_coefs$rho_25, probs=seq(0.025, 0.975, 0.95))[2]

```





