---
title: "bootstrap f"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))


```

Objective: Bootstrap confidence intervals for f and u and associated parameters for the best fitting model from the model comparison

Which model is the best fitting model?
```{r}
m4_u_f_fit <- readRDS(file = here("mle", "final", "m4_fit.rds"))
```


In order to bootstrap confidence intervals around the estimate, we will resample with replacement from the data used to generate these estimates. We will do this many times (~1000) and measure quantiles of the data to understand the bounds in which 95% of the estimates lie.

```{r}
source(here("model_fitting", "combined", "final_prep.R")) #data, global variables and functions
```


```{r}
dataset %<>% filter(exposed==T)
life_data <- dataset
fora_data <- data
```





We want to subset the data randomly but we don't want to oversample from some treatments and undersample from other treatments.

This is just a test
```{r, eval=F}
data_boot <- data %>% 
  group_by(treatment_ID) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- data %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

jkl <- data_boot %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

asdf
jkl
```

slice_sample is set to keep the amount of data per treatment the same (30), but resamples from the data with replacement which causes the means to be different. It looks like it is working!

```{r}
m5_ll <- function(f, u_15, u_20, u_25, arr_t_f, h, w, rho_15, rho_20, rho_25){
  data <- boot_data
  R_end <- as.data.frame(mapply(m3_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*data$temp),
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  tmp_dataset <- boot_dataset

  u_vec <- c(u_15, u_20, u_25)
  rho_vec <- c(rho_15, rho_20, rho_25)
  
  for(i in 1:3){
  exp_data <- tmp_dataset %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m3_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u_vec[i]*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  }
  return(nll_sum)
}
```

```{r, eval=F}
start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5_u_f_fit <- mle2(m5_ll, start=list(u_15 = 0.0001,
                                     u_20 = 0.0001,
                                     u_25 = 0.0001,
                                        f=1, 
                                        arr_t_f=10, 
                                        h=1,
                                        w=0.1,
                                        rho_15=0.1,
                                     rho_20=0.1,
                                     rho_25=0.1), 
                     control=list(parscale = c(u_15 = 0.0001,
                                     u_20 = 0.0001,
                                     u_25 = 0.0001,
                                        f=1, 
                                        arr_t_f=10, 
                                        h=1,
                                        w=0.1,
                                        rho_15=0.1,
                                     rho_20=0.1,
                                     rho_25=0.1)),
                     skip.hessian=F, method="BFGS")

end_time <- Sys.time()
end_time - start_time


coef(m5_u_f_fit)


```



Finally, we use our optimizer to get the maximum likelihood estimate for all parameters
We'll include the bootstrapping here

```{r, 00}

  iterations <- 50
  
  boot_00 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_00[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=10, arr_t=30, h=15, w=0.1), maxit=10000))
      boot_00[[i]] <- mle2(m5_ll, start=list(u_15 = 0.0001,
                                           u_20 = 0.0001,
                                           u_25 = 0.0001,
                                              f=1, 
                                              arr_t_f=10, 
                                              h=1,
                                              w=0.1,
                                              rho_15=0.1,
                                           rho_20=0.1,
                                           rho_25=0.1), 
                           control=list(parscale = c(u_15 = 0.0001,
                                           u_20 = 0.0001,
                                           u_25 = 0.0001,
                                              f=1, 
                                              arr_t_f=10, 
                                              h=1,
                                              w=0.1,
                                              rho_15=0.1,
                                           rho_20=0.1,
                                           rho_25=0.1)),
                           skip.hessian=F, method="BFGS")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 01}

  iterations <- 50
  
  m6c_f_boot_01 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_01[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 02}

  iterations <- 50
  
  m6c_f_boot_02 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_02[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 03}

  iterations <- 50
  
  m6c_f_boot_03 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_03[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 04}

  iterations <- 50
  
  m6c_f_boot_04 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_04[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 05}

  iterations <- 50
  
  m6c_f_boot_05 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_05[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


262 iterations run by 4/8/24

60 iterations run later on 4/8/24

300 iterations on 4/9/24

142 iterations on 4/10/24

bind lists
```{r}
length(m6c_f_boot_00)
length(m6c_f_boot_01)
length(m6c_f_boot_02)
length(m6c_f_boot_03)
length(m6c_f_boot_04)
length(m6c_f_boot_05)

m6c_f_boot <- c(m6c_f_boot_00,
                m6c_f_boot_01,
                m6c_f_boot_02,
                m6c_f_boot_03,
                m6c_f_boot_04,
                m6c_f_boot_05)
```

Add to older iterations
```{r}
#m6c_f_boot_read <- readRDS(file = here("mle", "m6c_f_boot_full.rds"))
#m6c_f_boot <- c(m6c_f_boot, m6c_f_boot_read)
# # 
#saveRDS(m6c_f_boot, file = here("mle", "m6c_f_boot_full.rds"))
```


```{r}
m6c_f_boot <- readRDS(file = here("mle", "m6c_f_boot_full.rds"))
```



```{r}
tib_length <- length(m6c_f_boot)

m6c_boot_coefs <- tibble(f = rep_len(0, tib_length),
                         arr = rep_len(0, tib_length),
                         h = rep_len(0, tib_length),
                         w = rep_len(0, tib_length))


for(i in 1:length(m6c_f_boot)){
  if(m6c_f_boot[[i]]@details[4] == 52){
    print(paste(i, "convergence_failure", sep="_"))
    m6c_boot_coefs$f[i] <- NA
    m6c_boot_coefs$arr[i] <- NA
    m6c_boot_coefs$h[i] <- NA
    m6c_boot_coefs$w[i] <- NA
  }
  else if(m6c_f_boot[[i]]@min == 0){
    print(paste(i, "zero_ll", sep="_"))
    m6c_boot_coefs$f[i] <- NA
    m6c_boot_coefs$arr[i] <- NA
    m6c_boot_coefs$h[i] <- NA
    m6c_boot_coefs$w[i] <- NA
  }
  else{
  boot_coef <- coef(m6c_f_boot[[i]])
  m6c_boot_coefs$f[i] <- as.numeric(boot_coef[1])
  m6c_boot_coefs$arr[i] <- as.numeric(boot_coef[2])
  m6c_boot_coefs$h[i] <- as.numeric(boot_coef[3])
  m6c_boot_coefs$w[i] <- as.numeric(boot_coef[4])
  }
}
```

```{r}
m6c_boot_coefs %<>% drop_na()

m6c_boot_coefs %>% ggplot(., aes(x = f)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = arr)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = h)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = w)) + geom_histogram()

```

quantiles
```{r}
m6c_quantiles <- tibble(id = c("est", "mean", "lower.025", "upper.975"),
                        f = NA,
                        arr = NA,
                        h = NA,
                        w = NA)

m6c_quantiles$f[1] <- coef(m6c)[1]
m6c_quantiles$f[2] <- mean(m6c_boot_coefs$f)
m6c_quantiles$f[3] <- quantile(m6c_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$f[4] <- quantile(m6c_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$arr[1] <- coef(m6c)[2]
m6c_quantiles$arr[2] <- mean(m6c_boot_coefs$arr)
m6c_quantiles$arr[3] <- quantile(m6c_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$arr[4] <- quantile(m6c_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$h[1] <- coef(m6c)[3]
m6c_quantiles$h[2] <- mean(m6c_boot_coefs$h)
m6c_quantiles$h[3] <- quantile(m6c_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$h[4] <- quantile(m6c_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$w[1] <- coef(m6c)[4]
m6c_quantiles$w[2] <- mean(m6c_boot_coefs$w)
m6c_quantiles$w[3] <- quantile(m6c_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$w[4] <- quantile(m6c_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[2]
```

```{r}
saveRDS(m6c_quantiles, file = here("mle", "m6c_quantiles.rds"))
```



Everything below here is still being workshopped









```{r}
get_fits <- function(iters){
  
  iterations <- iters
  
  m6c_f_boot <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=10, arr_t=50, h=1, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=10, arr_t=50, h=1, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)
  
  return(m6c_f_boot)
}
```


```{r}
asdf <- get_fits(3)
```



```{r}
m6c_fits_a <- get_fits(50)
saveRDS(m6c_fits_a, file = here("mle", "m6c_fits_a.rds"))

m6c_fits_b <- get_fits(50)
saveRDS(m6c_fits_b, file = here("mle", "m6c_fits_b.rds"))

m6c_fits_c <- get_fits(50)
saveRDS(m6c_fits_c, file = here("mle", "m6c_fits_c.rds"))

m6c_fits_d <- get_fits(50)
saveRDS(m6c_fits_d, file = here("mle", "m6c_fits_d.rds"))

m6c_fits_e <- get_fits(50)
saveRDS(m6c_fits_e, file = here("mle", "m6c_fits_e.rds"))

m6c_fits_f <- get_fits(50)
saveRDS(m6c_fits_f, file = here("mle", "m6c_fits_f.rds"))

m6c_fits_g <- get_fits(50)
saveRDS(m6c_fits_g, file = here("mle", "m6c_fits_g.rds"))

m6c_fits_h <- get_fits(50)
saveRDS(m6c_fits_h, file = here("mle", "m6c_fits_h.rds"))

m6c_fits_i <- get_fits(50)
saveRDS(m6c_fits_i, file = here("mle", "m6c_fits_i.rds"))

m6c_fits_j <- get_fits(50)
saveRDS(m6c_fits_j, file = here("mle", "m6c_fits_j.rds"))

```

```{r}
m6c_fits_1 <- get_fits(100)
saveRDS(m6c_fits_1, file = here("mle", "m6c_fits_1.rds"))

m6c_fits_2 <- get_fits(100)
saveRDS(m6c_fits_2, file = here("mle", "m6c_fits_2.rds"))

m6c_fits_3 <- get_fits(100)
saveRDS(m6c_fits_3, file = here("mle", "m6c_fits_3.rds"))

m6c_fits_4 <- get_fits(100)
saveRDS(m6c_fits_4, file = here("mle", "m6c_fits_4.rds"))

m6c_fits_5 <- get_fits(100)
saveRDS(m6c_fits_5, file = here("mle", "m6c_fits_5.rds"))

```


```{r}
head(m6c_fits_b)
```




```{r}
saveRDS(m6c_f_boot, file = here("mle","m6c_f_boot.rds"))
```

```{r}
saveRDS(m6c_fits_a, file = here("mle", "m6c_fits_a.rds"))
```





This should bootstrap the data. The only confusing part is that tmp must be declared before running the foreach loop. The results from the loop are all different so it appears to be reinitializing tmp within each loop but I'm not sure why it doesn't work without this being initialized first.
```{r}
registerDoParallel()
getDoParWorkers()

iterations <- 10

start_time <- Sys.time()

tmp <- data

m6c_f_boot_par <- foreach(1:iterations) %dopar% {

    tmp <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
    
      
    estimate <-mle2(m6c_ll,
                    skip.hessian = T,
                    start=list(f=10, arr_t=50, h=0.01, w=0.1),
                    method = "L-BFGS-B",
                    lower = c(f=0, arr_t=0, h=0, w=-Inf),
                    upper = c(Inf, Inf, Inf, Inf),
                    control=list(parscale=c(f=10, arr_t=50, h=0.01, w=0.1), maxit=10000))
    estimate
    

}
end_time <- Sys.time()

end_time-start_time
registerDoSEQ()

saveRDS(m6c_f_boot_par, file = here("mle","m6c_f_boot_par.rds"))
```



# Test
Parallelization does appear to make it faster

```{r, m0_num_sol}
m0_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -f*R
    res <- c(dR)
    list(res)}
    )
}

```



```{r, m0_sim}
m0_sim <- function(R, time, f){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f)
  output <- as.data.frame(lsoda(y=xstart, times, m0_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m0_ll}
m0_ll <- function(f){
  data <- tmp
  m0_end <- as.data.frame(mapply(m0_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol))
  colnames(m0_end) <- "m0_end"
  data$end <- m0_end$m0_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```



```{r}
get_m0_fits <- function(iters){

iterations <- iters

m0_f_fit_boot <- list()

start_time <- Sys.time()
for(i in 1:iterations){
    print(i)
    boot_data <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
      
    tmp <- boot_data
    
    m0_f_fit_boot[[i]] <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10),
                control=list(parscale=c(f=10), maxit=10000))

}
end_time <- Sys.time()

end_time-start_time
return(m0_f_fit_boot)
}


#saveRDS(m7c_f_fit, file = here("mle","m7c_f_boot.rds"))
```

```{r}
jkl <- get_m0_fits(5)
```




```{r}
registerDoParallel()
getDoParWorkers()

iterations <- 10

start_time <- Sys.time()

m0_f_boot_par_ <- foreach(1:iterations) %dopar% {
    
    tmp <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
    
    
    estimate <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10),
                control=list(parscale=c(f=10), maxit=10000))
    
    estimate
}


end_time <- Sys.time()

end_time-start_time
registerDoSEQ()

#saveRDS(m0_f_boot_par, file = here("mle","m0_f_boot_100.rds"))

```
