---
title: "arr function"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=F}
library(tidyverse)
library(magrittr)
```



We use a form of the Arrhenius equation that is meant to capture the exponentially increasing portion of a thermal reaction norm. However, we are able to generate results for per-parasite susceptibility that exhibit a non-monotonic, unimodal response. How is this possible?

At current, we only observe this effect at high resource conditions.

Fake data
```{r}
temp_range <- seq(15, 35, 1)

dat <- 
  tibble(temp = NA,
         resource = NA,
         u = NA)

for (i in 1:length(temp_range)){
  tmp <- tibble(temp = temp_range[i],
                resource = c(0.1, 0.5, 1))
  dat %<>% bind_rows(., tmp)
}

arr_t <- 93.4 #arrhenius coefficient

ref_t <- 15 #reference temperature

pps <- 12.25/100000 #per-parasite susceptibility

dat %<>%
  mutate(u_arr = exp(arr_t*(1/ref_t - 1/temp)))
```

```{r}
dat %>%
  ggplot(., aes(x = temp, y = u_arr)) + 
  geom_line()
```


The full form also includes an effect of resources and the interaction between temperature and resources. However, the effects of resources shouldn't matter here when I am only considering one resource condition.


```{r}
rho <- 5.28 

phi <- -0.215

dat %<>%
  mutate(u_rho = pps*exp(rho*resource),
         u_phi = pps*exp(phi*resource*temp),
         u_inter = u_arr*u_rho*u_phi)
```

```{r}
dat %>%
  ggplot(., aes(x = temp, y = u_inter, group = as.factor(resource))) + 
  geom_line()
```




