---
title: "u_f_fits"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))

library(ggnewscale)
```

# Notes

```{r}
fitness <- read.csv(here("raw_data/main_fitness_edit.csv")) #must be read.csv
fitness %<>% dplyr::select(tube, temp_id, REMOVED, KBP, final_date) #remove unnecessary variables
mort <-  read_csv(here("raw_data/main_mort_edit.csv")) #mortality data
lengths <- read_csv(here("raw_data", "day5_length.csv")) #get average lengths
lengths %<>% filter(temp_id %in% const_temp)


dataset <- left_join(mort,fitness) #life table data
```


```{r}
data <- readRDS(here("processed_data","foraging_raw.rds")) #foraging rate data
data_summ <- readRDS(here("processed_data", "foraging.rds")) #foraging rate data summary

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube
```


```{r}
treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


fora_vol <- 15 #mL
life_vol <- 50 #mL
spore_conc <- 200 #spores/mL
gamma <- 2 
ref_t <- 15 #celsius

```

```{r}
dataset %<>% filter(species == "D") %>% #only daphnia for this analysis
  filter(temp %in% const_temp) #only constant temp for this analysis

dataset %<>% mutate(birthdate = ifelse(species == "daphnia", "4/5/22", "4/6/22"), 
                    lifespan = as.numeric(mdy(final_date) - mdy(birthdate)),
                    temp = as.numeric(temp),
                    treatment = paste(temp, resource, sep = "_")) %>% 
  filter(is.na(male)) %>% #remove males
  filter(is.na(missing)) %>% #remove missing
  filter(!is.na(inf)) #remove NAs for inf for estimating beta. sometimes they died too young to tell

dataset %<>% mutate(inf_status = inf, dead = ifelse(is.na(REMOVED) & is.na(KBP), 1, 0))


dataset %<>% mutate(spore_exposure = 200, #spores/mL
                    uninf = 1-inf_status,
                    time = 1, #duration of exposure in days
                    trt = paste(temp, resource, species, sep = "_"))
```

```{r}
lengths %<>% mutate(mm = raw_meas*17.86/1000)
#at default magnification (5.6x), 1 unit is equal to 17.86 micron

length_summ <- lengths %>% 
  group_by(temp_id, resource) %>% 
  summarize(life_mm = mean(mm),
            var = var(mm),
            sd = sd(mm),
            se = sd(mm)/sqrt(n())) %>%
  ungroup() %>%
  dplyr::select(temp_id, resource, life_mm)

length_summ %<>% add_row(temp_id=as.character(25), resource=as.numeric(0.5), life_mm=1.16) #midpoint between 1.0 and 0.1

dataset %<>% left_join(length_summ)

length_summ %<>% mutate(ID = paste(temp_id, resource, sep="_")) %>% dplyr::select(-c(temp_id, resource))

```

```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))

mean_length_summ %<>% rename(fora_mm = "mm_mean")
dataset %<>% left_join(., mean_length_summ)
```

```{r}
inf_out <- function(inf_status, I_end){
  dbinom(x = inf_status, size = 1, prob=I_end, log=T)
}
```


```{r}
getAIC <- function(model){
  return(2*length(coef(model))-(2*summary(model)@m2logL/-2))
}
```



$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{1 + fe^{T_{A}(1/T_{R}-1/T)}hL^{\gamma}R} S \\
$$


# Independent Model

$$
\frac{dR}{dt} = -L^{\gamma} fRS\\
$$

```{r}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  
  with(as.list(params),{
    dR <- -((f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R))*R*(S+I)
    dS <- -u*((f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R))*Z*S
    dI <- u*((f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R))*Z*S
    dZ <- -((f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R))*Z*(S+I)
    res <- c(dR, dS, dI, dZ)
    list(res)}
    )
}
```


```{r, m1_sim}
m1_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u,
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              h = h,
              temp = temp)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  return(end_data)
}
```

```{r, m1_ll}
m1_ll <- function(u, f, arr_t_f, h, w, sd_est){
  data <- tmp
  R_end <- as.data.frame(mapply(m1_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*data$temp),
                                temp=data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))
  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```

Testing to see why the new model fits are better than the old.

```{r, eval=F}
u <- 0.00075
f <- as.numeric(m6c_coef[1])
arr_t_f <- as.numeric(m6c_coef[2])
h <- as.numeric(m6c_coef[3])
w <- as.numeric(m6c_coef[4])

  data <- tmp
  R_end <- as.data.frame(mapply(m1_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*data$temp),
                                temp=data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid), 
                 log = T)
    nll_sum_f_m6c <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))
  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum_u_m6c <- -sum(exp_data$ll)

```


```{r, eval=F}
m1_coef <- coef(m1_u_f_fit)
u <- m1_coef[1]
f <- m1_coef[2]
arr_t_f <- m1_coef[3]
h <- m1_coef[4]
w <- m1_coef[5]


  data <- tmp
  R_end <- as.data.frame(mapply(m1_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*data$temp),
                                temp=data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))
  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum_u_m1 <- -sum(exp_data$ll)

```


New algo splits the difference and has a lower log-likelihood overall because it can better match the infection data

```{r, eval=F}
nll_sum_f_m6c
nll_sum_u_m6c
nll_sum_f_m6c + nll_sum_u_m6c


nll_sum_f_m1
nll_sum_u_m1
nll_sum_f_m1 + nll_sum_u_m1


```



Now we use the optimizer

```{r, m1_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m1_u_f_fit <- mle2(m1_ll, start=list(u = 0.0001, 
                                     f=18, 
                                     arr_t_f=30, 
                                     h=17000, 
                                     w=-0.2,
                                     sd_est = 0.01),
                     control=list(parscale = c(u = 0.0001, 
                                               f=1, 
                                               arr_t_f=10, 
                                               h=10000, 
                                               w=0.1,
                                               sd_est = 0.01)),
                     skip.hessian=F, method="Nelder-Mead")

# m1_u_f_fit <- mle2(m1_ll, start=list(u = 0.0001, f=18, arr_t_f=30, h=17000, w=-0.2),
#                      control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, h=10000, w=0.1)),
#                      skip.hessian=F, method="L-BFGS-B",
#                    lower=c(u = 0, f = 0, arr_t_f=0, h=0, w=-Inf),
#                    upper=c(u = 1, f = Inf, arr_t_f=Inf, h=Inf, w=Inf))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_u_f_fit)

saveRDS(m1_u_f_fit, file = here("mle","final","m1_fit.rds"))
```


# Temperature-Dependent Model

$$
\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\\  
$$

```{r, m2_sim}
m2_sim <-  function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)),
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              h = h,
              temp = temp)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  return(end_data)
}
```

```{r, m2_ll}
m2_ll <- function(f, u, arr_t_f, arr_t_u, h, w, sd_est){
  data <- tmp
  R_end <- as.data.frame(mapply(m2_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                ref_t=ref_t,
                                h=h*exp(w*data$temp),
                                temp=data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)


  
  I_end <- as.data.frame(mapply(m2_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                ref_t=ref_t,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```

Now we use the optimizer

```{r, m2_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m2_u_f_fit <- mle2(m2_ll, start=list(u = 0.0001, 
                                     f=18,
                                     arr_t_f = 30,
                                     arr_t_u = 65,
                                     h=16000,
                                     w=-0.1,
                                     sd_est = 0.01), 
                     control=list(parscale = c(u = 0.0001, 
                                               f=1,
                                               arr_t_f = 10,
                                               arr_t_u = 10,
                                               h=10000,
                                               w=0.1,
                                     sd_est = 0.01)),
                     skip.hessian=F, method="BFGS")

# m2_u_f_fit <- mle2(m2_ll, start=list(u = 0.0001, 
#                                      f=30,
#                                      arr_t_f = 30,
#                                      arr_t_u = 10,
#                                      h=10000,
#                                      w=-0.1), 
#                      control=list(parscale = c(u = 0.0001, 
#                                                f=1,
#                                                arr_t_f = 10,
#                                                arr_t_u = 10,
#                                                h=10000,
#                                                w=0.1)),
#                      skip.hessian=F, method="L-BFGS-B", 
#                    lower=c(u = 0, f = 0, arr_t_f=0, arr_t_u=0, h=0, w=-Inf), 
#                    upper=c(u = 1, f = Inf, arr_t_f=Inf, arr_t_u=Inf, h=Inf, w=Inf))

end_time <- Sys.time()
m2_runtime <- end_time - start_time
m2_runtime

coef(m2_u_f_fit)

saveRDS(m2_u_f_fit, file = here("mle","final","m2_fit.rds"))
```

# Resource-depdendent Model

$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{1 + fL^{\gamma}hR}S \\
$$

```{r, m3_sim}
m3_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u,
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              h = h,
              temp = temp)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }

  return(end_data)
}
```

```{r, m3_ll}
m3_ll <- function(f, u, arr_t_f, h, w, rho, sd_est){
  data <- tmp
  R_end <- as.data.frame(mapply(m3_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                arr_t_f=arr_t_f,
                                ref_t=ref_t,
                                h=h*exp(w*data$temp),
                                temp=data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)


  
  I_end <- as.data.frame(mapply(m3_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u*exp(exp_data$resource*rho), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                arr_t_f=arr_t_f,
                                ref_t=ref_t,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```

Now we use the optimizer

```{r, m3_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m3_u_f_fit <- mle2(m3_ll, start=list(u = 0.0001, 
                                     f=30, 
                                     arr_t_f = 30,
                                     h=16000,
                                     w=0.1,
                                     rho = 0.1,
                                     sd_est = 0.01), 
                     control=list(parscale = c(u = 0.0001, 
                                               f=1, 
                                               arr_t_f = 1,
                                               h=10000,
                                               w=0.1,
                                               rho = 0.1,
                                     sd_est = 0.01)),
                     skip.hessian=F, method="Nelder-Mead")

# m3_u_f_fit <- mle2(m3_ll, start=list(u = 0.0001, 
#                                      f=30, 
#                                      h=10000,
#                                      w=0.1
#                                      rho = 0.1), 
#                      control=list(parscale = c(u = 0.0001, 
#                                                f=1, 
#                                                h=10000,
#                                                w=0.1
#                                                rho = 0.1)),
#                      skip.hessian=F, method="L-BFGS-B", 
#                    lower=c(u = 0, f = 0, h=0, w = -Inf, rho = -Inf), 
#                    upper=c(u = 1, f = Inf, h=Inf, w = Inf, rho = Inf))
end_time <- Sys.time()
m3_runtime <- end_time - start_time
m3_runtime

coef(m3_u_f_fit)

saveRDS(m3_u_f_fit, file = here("mle","final","m3_fit.rds"))
```


# Full Model


```{r}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  
  with(as.list(params),{
    dR <- -R*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dS <- -Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dI <- Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
               (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dZ <- -Z*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    res <- c(dR, dS, dI, dZ)
    list(res)}
  )
}

    # dS = -S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dI = S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dZ = -(S+I)*Z*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dA = -(S+I)*A*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
```






```{r, m4_sim}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp, resource, w, rho){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u,
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              arr_t_u = arr_t_u,
              h = h,
              temp = temp,
              resource = resource,
              w = w,
              rho = rho)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }

  return(end_data)
}
```


```{r, eval=F}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)),
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              arr_t_u = arr_t_u,
              h = h,
              temp = temp)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }

  return(end_data)
}
```






```{r, m4_ll}
m4_ll <- function(f, u, arr_t_f, arr_t_u, h, w, rho, sd_est){
  
    if(f<0 | h<0 | u<0 | arr_t_f<0 | arr_t_u<0 |
      (u/100000*exp(arr_t_u*((1/15)-(1/15)))*exp(0.1/1000*rho)) <0 |
     (u/100000*exp(arr_t_u*((1/15)-(1/25)))*exp(1.0/1000*rho)) <0) {
  
      return(NA)
  
  } 
  
  else {  
  
  
  data <- tmp
  R_end <- as.data.frame(mapply(m4_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp = data$temp,
                                resource = data$resource,
                                w = w,
                                rho = rho))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=(u/100000), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp=exp_data$temp,
                                resource=exp_data$resource,
                                w = w,
                                rho = rho))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
  
  }
}
```

Now we use the optimizer

```{r, eval=F}
m4_fit <- readRDS(file = here("mle","final","m4_fit.rds"))
m4_coef <- coef(m4_fit)

adjust_factor <- 1

m4_f <- m4_coef[1]*adjust_factor
m4_u <- m4_coef[2]*adjust_factor
m4_arr_t_f <- m4_coef[3]*adjust_factor
m4_arr_t_u <- m4_coef[4]*adjust_factor
m4_h <- m4_coef[5]*adjust_factor
m4_w <- m4_coef[6]*adjust_factor
m4_rho <- m4_coef[7]*adjust_factor


```

```{r, eval=F}
adjust_factor <- 1

start_time <- Sys.time()
tmp <- data
m4_u_f_fit <- mle2(m4_ll, start=list(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor,
                                     sd_est = 0.01),
                     control=list(parscale = c(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor,
                                     sd_est = 0.01), maxit = 10000),
                     skip.hessian=F, method="Nelder-Mead")


end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_f_fit)


saveRDS(m4_u_f_fit, file = here("model_fitting","m4_coef_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_coef_log_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("mle","final","m4_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1_fit_log.rds"))
# saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1.1_fit.rds"))
# saveRDS(m4_u_f_fit, file = here("model_fitting","m4_0.5_fit.rds"))
```


```{r}
adjust_factor <- 1

start_time <- Sys.time()
tmp <- data
m4_u_f_fit <- mle2(m4_ll, start=list(u = 21*adjust_factor, 
                                     f=5.5*adjust_factor,
                                     arr_t_f=76*adjust_factor,
                                     arr_t_u=31*adjust_factor,
                                     h=16000*adjust_factor,
                                     w=-0.002*adjust_factor,
                                     rho=0.1*adjust_factor,
                                     sd_est = 0.01),
                     control=list(parscale = c(u = 21*adjust_factor, 
                                     f=5.5*adjust_factor,
                                     arr_t_f=76*adjust_factor,
                                     arr_t_u=31*adjust_factor,
                                     h=1000*adjust_factor,
                                     w=-0.002*adjust_factor,
                                     rho=0.1*adjust_factor,
                                     sd_est = 0.01), maxit = 10000),
                     skip.hessian=F, method="Nelder-Mead")


end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_f_fit)

#saveRDS(m4_u_f_fit, file = here("mle","final","m4_fit.rds"))
saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1_fit_log.rds"))
# saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1.1_fit.rds"))
# saveRDS(m4_u_f_fit, file = here("model_fitting","m4_0.5_fit.rds"))
```




```{r}
adjust_factor <- 1.1

start_time <- Sys.time()
tmp <- data
m4_u_f_fit <- mle2(m4_ll,  start=list(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor),
                     control=list(parscale = c(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor), maxit = 10000),
                     skip.hessian=F, method="Nelder-Mead")


end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_f_fit)


saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1.1_coef_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_1.1_fit_log.rds"))

```




```{r}
adjust_factor <- 0.5

start_time <- Sys.time()
tmp <- data
m4_u_f_fit <- mle2(m4_ll, start=list(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor),
                     control=list(parscale = c(u = m4_u*adjust_factor*100000, 
                                     f=m4_f*adjust_factor,
                                     arr_t_f=m4_arr_t_f*adjust_factor,
                                     arr_t_u=m4_arr_t_u*adjust_factor,
                                     h=m4_h*adjust_factor,
                                     w=m4_w*adjust_factor,
                                     rho=m4_rho*adjust_factor), maxit=10000),
                     skip.hessian=F, method="Nelder-Mead")


end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_f_fit)


saveRDS(m4_u_f_fit, file = here("model_fitting","m4_0.5_coef_fit.rds"))
#saveRDS(m4_u_f_fit, file = here("model_fitting","m4_0.5_fit_log.rds"))

```

# Interaction Model


```{r, eval=F}
m5_coef

f <- m5_coef[1]
u_15 <- m5_coef[2]
u_20 <- m5_coef[3]
u_25 <- m5_coef[4]
arr_t_f <- m5_coef[5]
h <- m5_coef[6]
w <- m5_coef[7]
rho_15 <- m5_coef[8]
rho_20 <- m5_coef[9]
rho_25 <- m5_coef[10]

```


```{r}

m5_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  
  with(as.list(params),{
    dR <- -R*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dS <- -Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*exp(resource*temp*phi)*
      (f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dI <- Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*exp(resource*temp*phi)*
      (f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
               (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dZ <- -Z*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    res <- c(dR, dS, dI, dZ)
    list(res)}
  )
}


    # dS = -S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*exp(R_trt*T_trt*u3)*
    #   f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dI = S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*exp(R_trt*T_trt*u3)*
    #   f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dZ = -(S+I)*Z*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dA = -(S+I)*A*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
```


```{r}
m5_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp, resource, w, rho, phi){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u,
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              arr_t_u = arr_t_u,
              h = h,
              temp = temp,
              resource = resource,
              w = w,
              rho = rho,
              phi = phi)
  output <- as.data.frame(lsoda(y=xstart, times, m5_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }

  return(end_data)
}
```


```{r}
m5_ll <- function(f, u, arr_t_f, arr_t_u, h, w, rho, phi, sd_est){
  
  if(f<0 | h<0 | u<0 | arr_t_f<0 | arr_t_u<0 |
      (u/100000*exp(arr_t_u*((1/15)-(1/15)))*exp(0.1/1000*rho)*exp(0.1/1000*15*phi)) <0 |
     (u/100000*exp(arr_t_u*((1/15)-(1/25)))*exp(1.0/1000*rho)*exp(1.0/1000*25*phi)) <0) {
  
      return(NA)
  
  } 
  
  else {  
  
  
  data <- tmp
  R_end <- as.data.frame(mapply(m5_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp = data$temp,
                                resource = data$resource,
                                w = w,
                                rho = rho,
                                phi = phi))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll)
  exp_data <- tmp_dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m5_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u/100000, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp=exp_data$temp,
                                resource=exp_data$resource,
                                w = w,
                                rho = rho,
                                phi = phi))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
  
  }
}
```

```{r, eval=F}
start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5_u_f_fit <- mle2(m5_ll, start=list(f = 10,
                                      u=10, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1,
                                     sd_est = 0.01), 
                     control=list(parscale = c(f = 10,
                                      u=10, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1,
                                     sd_est = 0.01),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")

end_time <- Sys.time()
end_time - start_time


coef(m5_u_f_fit)

saveRDS(m5_u_f_fit, file = here("model_fitting","m5_phi_fit.rds"))
```

```{r, eval=F}
adjust_factor <- 1.1

start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5_u_f_fit <- mle2(m5_ll, start=list(u = 20*adjust_factor,
                                      f=30*adjust_factor, 
                                      arr_t_f=30*adjust_factor, 
                                      arr_t_u=30*adjust_factor,
                                      h=100*adjust_factor,
                                      w=0.1*adjust_factor,
                                      rho=0.1*adjust_factor,
                                      phi=0.1*adjust_factor), 
                     control=list(parscale = c(u = 20*adjust_factor,
                                      f=30*adjust_factor, 
                                      arr_t_f=30*adjust_factor, 
                                      arr_t_u=30*adjust_factor,
                                      h=100*adjust_factor,
                                      w=0.1*adjust_factor,
                                      rho=0.1*adjust_factor,
                                      phi=0.1*adjust_factor),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")

end_time <- Sys.time()
end_time - start_time


coef(m5_u_f_fit)

saveRDS(m5_u_f_fit, file = here("model_fitting","m5_phi_fit_1.1.rds"))
```

```{r}
adjust_factor <- 0.5

start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5_u_f_fit <- mle2(m5_ll, start=list(u = 20*adjust_factor,
                                      f=30*adjust_factor, 
                                      arr_t_f=30*adjust_factor, 
                                      arr_t_u=30*adjust_factor,
                                      h=100*adjust_factor,
                                      w=0.1*adjust_factor,
                                      rho=0.1*adjust_factor,
                                      phi=0.1*adjust_factor), 
                     control=list(parscale = c(u = 20*adjust_factor,
                                      f=30*adjust_factor, 
                                      arr_t_f=30*adjust_factor, 
                                      arr_t_u=30*adjust_factor,
                                      h=100*adjust_factor,
                                      w=0.1*adjust_factor,
                                      rho=0.1*adjust_factor,
                                      phi=0.1*adjust_factor),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")

end_time <- Sys.time()
end_time - start_time


coef(m5_u_f_fit)

saveRDS(m5_u_f_fit, file = here("model_fitting","m5_phi_fit_0.5.rds"))
```



```{r}
m5_ll <- function(f, u_15, u_20, u_25, arr_t_f, h, w, rho_15, rho_20, rho_25){
  data <- tmp
  R_end <- as.data.frame(mapply(m3_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*data$temp),
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }
  
    # nll <- dnorm(data$resid, 
    #              mean = 0, 
    #              sd = sd(data$resid), 
    #              log = T)
    # nll_sum <- -sum(nll) 
  tmp_dataset %<>% filter(exposed==TRUE)

  u_vec <- c(u_15, u_20, u_25)
  rho_vec <- c(rho_15, rho_20, rho_25)
  
  for(i in 1:3){
  exp_data <- tmp_dataset %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m3_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u_vec[i]*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  }
  return(nll_sum)
}
```

```{r, eval=F}
start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5_u_f_fit <- mle2(m5_ll, start=list(u_15 = 0.0001,
                                     u_20 = 0.0001,
                                     u_25 = 0.0001,
                                        f=30, 
                                        arr_t_f=30, 
                                        h=16000,
                                        w=0.1,
                                        rho_15=0.1,
                                     rho_20=0.1,
                                     rho_25=0.1), 
                     control=list(parscale = c(u_15 = 0.0001,
                                     u_20 = 0.0001,
                                     u_25 = 0.0001,
                                        f=1, 
                                        arr_t_f=10, 
                                        h=100,
                                        w=0.1,
                                        rho_15=0.1,
                                     rho_20=0.1,
                                     rho_25=0.1)),
                     skip.hessian=F, method="BFGS")

# m5_u_f_fit <- mle2(m5_ll, start=list(u_15 = 0.0001,
#                                      u_20 = 0.0001,
#                                      u_25 = 0.0001,
#                                         f=1, 
#                                         arr_t_f=10, 
#                                         h=1,
#                                         w=0.1,
#                                         rho_15=0.1,
#                                      rho_20=0.1,
#                                      rho_25=0.1), 
#                      control=list(parscale = c(u_15 = 0.0001,
#                                      u_20 = 0.0001,
#                                      u_25 = 0.0001,
#                                         f=1, 
#                                         arr_t_f=10, 
#                                         h=1,
#                                         w=0.1,
#                                         rho_15=0.1,
#                                      rho_20=0.1,
#                                      rho_25=0.1)),
#                      skip.hessian=F, method="L-BFGS-B", 
#                    lower=c(u_15 = 0, u_20 = 0, u_25 = 0, 
#                            f=0, arr_t_f=0, h=0, w=-Inf, rho_15=-Inf, rho_20=-Inf, rho_25=-Inf), 
#                    upper=c(u_15 = 1, u_20 = 1, u_25 = 1, 
#                            f=Inf, arr_t_f=Inf, h=Inf, w=Inf, rho_15=Inf, rho_20=Inf, rho_25=Inf))

end_time <- Sys.time()
end_time - start_time


coef(m5_u_f_fit)

#saveRDS(m5_u_f_fit, file = here("mle","final","m5_fit.rds"))
saveRDS(m5_u_f_fit, file = here("mle","final","m5_fit_alt.rds"))
```


```{r, eval=F}
m5a_profile <- readRDS(file = here("mle", "final", "m5a_profile_fit.rds"))
coef(m5a_profile)

adjust_factor <- 1

u_m5a <- coef(m5a_profile)[1]*adjust_factor
f_m5a <- coef(m5a_profile)[2]*adjust_factor
arr_t_f_m5a <- coef(m5a_profile)[3]*adjust_factor
arr_t_u_m5a <- coef(m5a_profile)[4]*adjust_factor
h_m5a <- coef(m5a_profile)[5]*adjust_factor
w_m5a <- coef(m5a_profile)[6]*adjust_factor
rho_15_m5a <- coef(m5a_profile)[7]*adjust_factor
rho_20_m5a <- coef(m5a_profile)[8]*adjust_factor
rho_25_m5a <- coef(m5a_profile)[9]*adjust_factor

```


```{r}
m5a_ll <- function(u, f, arr_t_f, arr_t_u, h, w, rho_15, rho_20, rho_25){
  data <- tmp
  R_end <- as.data.frame(mapply(m4_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*exp(w*data$temp),
                                temp = data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll)
  
  tmp_dataset %<>% filter(exposed==TRUE)

  rho_vec <- c(rho_15, rho_20, rho_25)
  
  for(i in 1:3){
  exp_data <- tmp_dataset %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*exp(w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  }
  return(nll_sum)
}
```

```{r, eval=F}
start_time <- Sys.time()
tmp <- data
tmp_dataset <- dataset
m5a_u_f_fit <- mle2(m5a_ll, start=list(u = u_m5a,
                                        f=f_m5a, 
                                        arr_t_f=arr_t_f_m5a,
                                        arr_t_u=arr_t_u_m5a,
                                        h=h_m5a,
                                        w=w_m5a,
                                        rho_15=rho_15_m5a,
                                     rho_20=rho_20_m5a,
                                     rho_25=rho_25_m5a), 
                     control=list(parscale = c(u = u_m5a,
                                        f=f_m5a, 
                                        arr_t_f=arr_t_f_m5a,
                                        arr_t_u=arr_t_u_m5a,
                                        h=h_m5a,
                                        w=w_m5a,
                                        rho_15=rho_15_m5a,
                                     rho_20=rho_20_m5a,
                                     rho_25=rho_25_m5a),
                                  maxit = 5000),
                     skip.hessian=F, method="Nelder-Mead")





end_time <- Sys.time()
end_time - start_time


coef(m5a_u_f_fit)

#saveRDS(m5a_u_f_fit, file = here("mle","final","m5a_fit_alt2.rds"))
```




```{r}
m1_u_f_fit <- readRDS(file = here("mle", "final", "m1_fit.rds"))
m2_u_f_fit <- readRDS(file = here("mle", "final", "m2_fit.rds"))
m3_u_f_fit <- readRDS(file = here("mle", "final", "m3_fit.rds"))
m4_u_f_fit <- readRDS(file = here("mle", "final", "m4_fit.rds"))
m5_u_f_fit <- readRDS(file = here("mle", "final", "m5_fit.rds"))
m5_u_f_fit <- readRDS(file = here("mle", "final", "m5_fit_alt.rds"))
m5a_u_f_fit <- readRDS(file = here("mle", "final", "m5a_fit.rds"))
m5a_u_f_fit <- readRDS(file = here("mle", "final", "m5a_fit_alt.rds"))
m5a_u_f_fita <- readRDS(file = here("mle", "final", "m5a_fit_alt1.rds"))
m5a_u_f_fit <- readRDS(file = here("mle", "final", "m5a_fit_alt2.rds"))
```



```{r}
getAIC(m1_u_f_fit) #constant u
getAIC(m2_u_f_fit) #temperature-dependent u 
getAIC(m3_u_f_fit) #rho
getAIC(m4_u_f_fit) #temperature-dependent u and rho
getAIC(m5_u_f_fit) #per-temperature u and rho
getAIC(m5a_u_f_fit) #arrhenius u and per-temperature rhos
```





```{r}
fora_summ <- data %>% 
  mutate(ID = treatment_ID) %>%
  group_by(ID) %>% 
  summarize(end_r_mean = mean(amt_rem)*fora_vol/1000,
            end_r_se = (sd(amt_rem)/sqrt(n()))*fora_vol/1000)

prevalence <- readRDS(here("processed_data", "prevalence.rds"))
prevalence %<>% filter(temp %in% c(15, 20, 25)) %>% filter(species=="D") %>% mutate(ID = paste(temp, resource, sep="_")) %>% dplyr::select(-c(temp, resource, species))


viz_summ <- left_join(fora_summ, prevalence)
viz_summ %<>% left_join(., data_summ)
viz_summ %<>% left_join(., length_summ)
```

```{r}
m1_coef <- coef(m1_u_f_fit)
m1_u <- as.numeric(m1_coef[1])
m1_f <- as.numeric(m1_coef[2])
m1_arr <- as.numeric(m1_coef[3])
m1_h <- as.numeric(m1_coef[4])
m1_w <- as.numeric(m1_coef[5])

data_summ %<>% mutate(m1_rate = (m1_f*exp(m1_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m1_f*exp(m1_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m1_h*exp(m1_w*temp)*resource/1000),
                      m1_u = m1_u)
```

```{r}
m2_coef <- coef(m2_u_f_fit)
m2_f <- as.numeric(m2_coef[1])
m2_u <- as.numeric(m2_coef[2])
m2_arr <- as.numeric(m2_coef[3])
m2_arr_u <- as.numeric(m2_coef[4])
m2_h <- as.numeric(m2_coef[5])
m2_w <- as.numeric(m2_coef[6])


data_summ %<>% mutate(m2_rate = (m2_f*exp(m2_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m2_f*exp(m2_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m2_h*exp(m2_w*temp)*resource/1000),
                      m2_u = m2_u*exp(m2_arr_u*(1/ref_t - 1/temp)))
```

```{r}
m3_coef <- coef(m3_u_f_fit)
m3_f <- as.numeric(m3_coef[1])
m3_u <- as.numeric(m3_coef[2])
m3_arr <- as.numeric(m3_coef[3])
m3_h <- as.numeric(m3_coef[4])
m3_w <- as.numeric(m3_coef[5])
m3_rho <- as.numeric(m3_coef[6])

data_summ %<>% mutate(m3_rate = (m3_f*exp(m3_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m3_f*exp(m2_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m3_h*exp(m3_w*temp)*resource/1000),
                      m3_u = m3_u*exp(m3_rho*temp))
```


```{r}
m4_coef <- coef(m4_u_f_fit)
m4_f <- as.numeric(m4_coef[1])
m4_u <- as.numeric(m4_coef[2])
m4_arr <- as.numeric(m4_coef[3])
m4_arr_u <- as.numeric(m4_coef[4])
m4_h <- as.numeric(m4_coef[5])
m4_w <- as.numeric(m4_coef[6])
m4_rho <- as.numeric(m4_coef[7])

data_summ %<>% mutate(m4_rate = (m4_f*exp(m4_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m4_f*exp(m4_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m4_h*exp(m4_w*temp)*resource/1000),
                      m4_u = m4_u*exp(m4_arr_u*(1/ref_t - 1/temp))*exp(m4_rho*temp))
```


```{r}
m5_coef <- coef(m5_u_f_fit)
m5_f <- as.numeric(m5_coef[1])
m5_u_15 <- as.numeric(m5_coef[2])
m5_u_20 <- as.numeric(m5_coef[3])
m5_u_25 <- as.numeric(m5_coef[4])
m5_arr <- as.numeric(m5_coef[5])
m5_h <- as.numeric(m5_coef[6])
m5_w <- as.numeric(m5_coef[7])
m5_rho_15 <- as.numeric(m5_coef[8])
m5_rho_20 <- as.numeric(m5_coef[9])
m5_rho_25 <- as.numeric(m5_coef[10])

data_summ %<>% mutate(m5_rate = (m5_f*exp(m5_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m5_f*exp(m5_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m5_h*exp(m5_w*temp)*resource/1000),
                      m5_u = case_when(temp == 15 ~ m5_u_15*exp(m5_rho_15*resource),
                                       temp == 20 ~ m5_u_20*exp(m5_rho_20*resource),
                                       temp == 25 ~ m5_u_25*exp(m5_rho_25*resource)))

```

```{r}
m5a_coef <- coef(m5a_u_f_fit)
m5a_f <- as.numeric(m5a_coef[1])
m5a_u <- as.numeric(m5a_coef[2])
m5a_arr <- as.numeric(m5a_coef[3])
m5a_arr_u <- as.numeric(m5a_coef[4])
m5a_h <- as.numeric(m5a_coef[5])
m5a_w <- as.numeric(m5a_coef[6])
m5a_rho_15 <- as.numeric(m5a_coef[7])
m5a_rho_20 <- as.numeric(m5a_coef[8])
m5a_rho_25 <- as.numeric(m5a_coef[9])

data_summ %<>% mutate(m5a_rate = (m5a_f*exp(m5a_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/
                        (1+m5a_f*exp(m5a_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m5a_h*exp(m5a_w*temp)*resource/1000),
                      m5a_u = case_when(temp == 15 ~ m5a_u*exp(m5a_arr_u*(1/ref_t - 1/temp))*exp(m5a_rho_15*resource),
                                       temp == 20 ~ m5a_u*exp(m5a_arr_u*(1/ref_t - 1/temp))*exp(m5a_rho_20*resource),
                                       temp == 25 ~ m5a_u*exp(m5a_arr_u*(1/ref_t - 1/temp))*exp(m5a_rho_25*resource)))

```



```{r}
data_summ %<>% mutate(rate_mean_ml_day=rate_len_mean*60*24,
                      rate_se_ml_day=rate_len_mean_se*60*24)
```

```{r}
viz_summ %<>% mutate(m1_I_end = mapply(m1_sim, 
                                       R=resource*life_vol/1000, 
                                       time=1, 
                                       f=m1_f/life_vol, 
                                       u = m1_u, 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m1_arr,
                                       h = m1_h*exp(m1_w*resource),
                                       temp = temp))

```


```{r}
viz_summ %<>% mutate(m2_I_end = mapply(m2_sim, 
                                       R=resource*life_vol/1000,
                                       time=1,
                                       f=m2_f/life_vol,
                                       u = m2_u,
                                       length=life_mm,
                                       gamma=gamma,
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m2_arr,
                                       arr_t_u = m2_arr_u,
                                       h = m2_h*exp(m2_w*temp),
                                       temp = temp))
```


```{r}
viz_summ %<>% mutate(m3_I_end = mapply(m3_sim, 
                                       R=resource*life_vol/1000,
                                       time=1,
                                       f=m3_f/life_vol,
                                       u = m3_u*exp(m3_rho*resource),
                                       length=life_mm,
                                       gamma=gamma,
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m3_arr,
                                       h = m3_h*exp(m3_w*temp),
                                       temp = temp))
```


```{r}
viz_summ %<>% mutate(m4_I_end = mapply(m4_sim, 
                                       R=resource*life_vol/1000, 
                                       time=1, 
                                       f=m4_f/life_vol, 
                                       u = m4_u*exp(m4_rho*resource), 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m4_arr,
                                       arr_t_u = m4_arr_u,
                                       h = m4_h*exp(m4_w*temp),
                                       temp = temp))
```


```{r}
viz_summ %<>% mutate(m5_I_end = mapply(m3_sim, 
                                       R=resource*life_vol/1000, 
                                       time=1, 
                                       f=m5_f/life_vol, 
                                       u = case_when(temp == 15 ~ m5_u_15*exp(m5_rho_15*resource),
                                                     temp == 20 ~ m5_u_20*exp(m5_rho_20*resource),
                                                     temp == 25 ~ m5_u_25*exp(m5_rho_25*resource)), 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m5_arr,
                                       h = m5_h*exp(m5_w*temp),
                                       temp = temp))
```

```{r}
viz_summ %<>% mutate(m5a_I_end = mapply(m4_sim, 
                                       R=resource*life_vol/1000, 
                                       time=1, 
                                       f=m5a_f/life_vol, 
                                       u = case_when(temp == 15 ~ m5a_u*exp(m5a_rho_15*resource),
                                                     temp == 20 ~ m5a_u*exp(m5a_rho_20*resource),
                                                     temp == 25 ~ m5a_u*exp(m5a_rho_25*resource)), 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m5a_arr,
                                       arr_t_u = m5a_arr_u,
                                       h = m5a_h*exp(m5a_w*temp),
                                       temp = temp))
```

```{r}
viz_summ %>% ggplot(.,aes(x=resource, y=prev, color=as.factor(temp)))  +
  geom_point(size=4) + 
  geom_linerange(aes(ymin = conf$lower, ymax=conf$upper)) +
  labs(title="experimental data")


viz_summ %>% ggplot(.,aes(x=resource, y=m1_I_end, color=as.factor(temp))) + 
  geom_point(size = 4, shape=2) +
  new_scale_color() + 
  geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + 
  geom_linerange(aes(ymin = conf$lower, ymax=conf$upper, color=as.factor(temp))) +
  labs(title="independent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m2_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="temperature-dependent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m3_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="resource-dependent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m4_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="full model")

viz_summ %>% ggplot(.,aes(x=resource, y=m5_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="interaction model")


viz_summ %>% ggplot(.,aes(x=resource, y=m5a_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="interaction model alt")

# viz_summ %>% ggplot(.,aes(x=resource, y=m4_I_end, color=as.factor(temp))) + 
#   geom_point(size = 4, shape=2) +
#   new_scale_color() + 
#   geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + 
#   geom_linerange(aes(ymin = conf$lower, ymax=conf$upper, color=as.factor(temp))) +
#   labs(title="full model")
# 
# viz_summ %>% ggplot(.,aes(x=resource, y=m5_I_end, color=as.factor(temp))) + 
#   geom_point(size = 4, shape=2) +
#   new_scale_color() + 
#   geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + 
#   geom_linerange(aes(ymin = conf$lower, ymax=conf$upper, color=as.factor(temp))) +
#   labs(title="interaction model")

```

```{r}
data_summ %>% ggplot(.,aes(x=resource, y=m1_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="independent model")

data_summ %>% ggplot(.,aes(x=resource, y=m2_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="temperature-dependent model")

data_summ %>% ggplot(.,aes(x=resource, y=m3_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="resource_dependent model")

data_summ %>% ggplot(.,aes(x=resource, y=m4_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="full model")

data_summ %>% ggplot(.,aes(x=resource, y=m5_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="interaction model")
```

```{r, eval=F}
data_summ %>% ggplot(.,aes(x=resource, y=m1_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m2_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m3_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m4_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m5_u, color=as.factor(temp))) + geom_point()
```


How well are the full and interactive model estimating f and u separately



model 4 - full model
```{r}

R_end <- as.data.frame(mapply(m4_sim, 
                              R=data$amt_init*fora_vol/1000, 
                              time=data$time/60/24, 
                              f=m4_f/fora_vol,
                              u = 0, 
                              length=data$mm, 
                              gamma=gamma, 
                              Z=0,
                              ref_t=ref_t,
                              arr_t_f=m4_arr,
                              arr_t_u=m4_arr_u,
                              h=m4_h*exp(m4_w*data$temp),
                              temp=data$temp))

colnames(R_end) <- "R_end"
data$end <- R_end$R_end
data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))

  nll <- dnorm(data$resid, 
               mean = 0, 
               sd = sd(data$resid, na.rm = T), 
               log = T)
  nll_sum_f_m4 <- -sum(nll, na.rm = T)

exp_data <- dataset %>% filter(exposed==TRUE)

I_end <- as.data.frame(mapply(m4_sim, 
                              R=exp_data$resource*life_vol/1000, 
                              time=exp_data$time, 
                              f=m4_f/life_vol, 
                              u=m4_u*exp(exp_data$resource*m4_rho), 
                              length=exp_data$life_mm, 
                              gamma=gamma, 
                              Z=spore_conc*life_vol,
                              ref_t=ref_t,
                              arr_t_f=m4_arr,
                              arr_t_u=m4_arr_u,
                              h=m4_h*exp(m4_w*exp_data$temp),
                              temp=exp_data$temp))


colnames(I_end) <- "I_end"

exp_data %<>% cbind(I_end)

exp_data %<>% 
  mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
nll_sum_u_m4 <- -sum(exp_data$ll)
```


model 5 - interaction model


```{r}

R_end <- as.data.frame(mapply(m3_sim, 
                              R=data$amt_init*fora_vol/1000, 
                              time=data$time/60/24, 
                              f=m5_f/fora_vol,
                              u = 0, 
                              length=data$mm, 
                              gamma=gamma, 
                              Z=0,
                              ref_t=ref_t,
                              arr_t_f=m5_arr,
                              h=m5_h*exp(m5_w*data$temp),
                              temp=data$temp))

colnames(R_end) <- "R_end"
data$end <- R_end$R_end
data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))

  nll <- dnorm(data$resid, 
               mean = 0, 
               sd = sd(data$resid, na.rm = T), 
               log = T)
  nll_sum_f_m5 <- -sum(nll, na.rm = T)

  nll_sum_u_m5 <- 0
  u_vec <- c(m5_u_15, m5_u_20, m5_u_25)
  rho_vec <- c(m5_rho_15, m5_rho_20, m5_rho_25)
  
  for(i in 1:3){
  exp_data <- dataset %>% filter(exposed==TRUE) %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m3_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=m5_f/life_vol, 
                                u=u_vec[i]*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=m5_arr,
                                h=m5_h*exp(m5_w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum_u_m5 <- nll_sum_u_m5 + -sum(exp_data$ll)
  }

```


```{r}

m5a_u_f_fit <- readRDS(here("mle","final","m5a_fit_alt1.rds"))


m5a_coef <- coef(m5a_u_f_fit)
m5a_u <- as.numeric(m5a_coef[1])
m5a_f <- as.numeric(m5a_coef[2])
m5a_arr <- as.numeric(m5a_coef[3])
m5a_arr_u <- as.numeric(m5a_coef[4])
m5a_h <- as.numeric(m5a_coef[5])
m5a_w <- as.numeric(m5a_coef[6])
m5a_rho_15 <- as.numeric(m5a_coef[7])
m5a_rho_20 <- as.numeric(m5a_coef[8])
m5a_rho_25 <- as.numeric(m5a_coef[9])

  R_end <- as.data.frame(mapply(m4_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=m5a_f/fora_vol,
                                u = 0, 
                                length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=m5a_arr,
                                arr_t_u=m5a_arr_u,
                                h=m5a_h*exp(m5a_w*data$temp),
                                temp = data$temp))
  
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum_f_m5a <- -sum(nll, na.rm = T)
  
  tmp_dataset <- dataset %>% filter(exposed==TRUE)

  nll_sum_u_m5a <- 0
  
  rho_vec <- c(m5a_rho_15, m5a_rho_20, m5a_rho_25)
  
  for(i in 1:3){
  exp_data <- tmp_dataset %>% filter(temp == temp_IDs[i])

  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=m5a_f/life_vol, 
                                u=m5a_u*exp(exp_data$resource*rho_vec[i]), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=m5a_arr,
                                arr_t_u=m5a_arr_u,
                                h=m5a_h*exp(m5a_w*exp_data$temp),
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
 nll_sum_u_m5a <- nll_sum_u_m5a + -sum(exp_data$ll)
  }

```



```{r}
m4_coef
nll_sum_f_m4
nll_sum_u_m4
(nll_sum_f_m4 + nll_sum_u_m4)
```


```{r}
m5_coef
nll_sum_f_m5
nll_sum_u_m5
(nll_sum_f_m5 + nll_sum_u_m5)
```


```{r}
m5a_coef
nll_sum_f_m5a
nll_sum_u_m5a
(nll_sum_f_m5a + nll_sum_u_m5a)
```

```{r}
summary(m4_u_f_fit)
summary(m5_u_f_fit)
summary(m5a_u_f_fit)
```



```{r}
getAIC(m4_u_f_fit)
getAIC(m5_u_f_fit)
getAIC(m5a_u_f_fit)

2*length(coef(m4_u_f_fit))
2*length(coef(m5_u_f_fit))
2*length(coef(m5a_u_f_fit))

2*summary(m4_u_f_fit)@m2logL/-2
2*summary(m5_u_f_fit)@m2logL/-2
2*summary(m5a_u_f_fit)@m2logL/-2
```


