---
title: "bootstrap f"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))


```

Objective: Bootstrap confidence intervals for f and u and associated parameters for the best fitting model from the model comparison

Which model is the best fitting model?
```{r}
m5_u_f_fit <- readRDS(file = here("model_fitting", "m5_phi_fit.rds"))
```


In order to bootstrap confidence intervals around the estimate, we will resample with replacement from the data used to generate these estimates. We will do this many times (~1000) and measure quantiles of the data to understand the bounds in which 95% of the estimates lie.

```{r}
source(here("model_fitting", "combined", "final_prep.R")) #data, global variables and functions
```


```{r}
dataset %<>% filter(exposed==T)
life_data <- dataset
fora_data <- data
```


```{r}

m5_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  
  with(as.list(params),{
    dR <- -R*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dS <- -Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*exp(resource*temp*phi)*
      (f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dI <- Z*S*u*exp(arr_t_u*(1/ref_t - 1/temp))*exp(resource*rho)*exp(resource*temp*phi)*
      (f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
               (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    
    dZ <- -Z*(S+I)*(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R*exp(w*temp))
    res <- c(dR, dS, dI, dZ)
    list(res)}
  )
}


    # dS = -S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*exp(R_trt*T_trt*u3)*
    #   f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dI = S*Z*u*exp(T_A_u*((1/15)-(1/T_trt)))*exp(R_trt*u2)*exp(R_trt*T_trt*u3)*
    #   f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dZ = -(S+I)*Z*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
    # dA = -(S+I)*A*f*(l^2)*exp(T_A_f*((1/15)-(1/T_trt))) / (1+(A*f*(l^2)*h*exp(h2*T_trt)))
```


```{r}
m5_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp, resource, w, rho, phi){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f,
              u=u,
              length = length,
              gamma = gamma,
              Z = Z,
              ref_t = ref_t,
              arr_t_f = arr_t_f,
              arr_t_u = arr_t_u,
              h = h,
              temp = temp,
              resource = resource,
              w = w,
              rho = rho,
              phi = phi)
  output <- as.data.frame(lsoda(y=xstart, times, m5_num_sol, params))
  
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }

  return(end_data)
}
```

```{r}
m5_coef <- coef(m5_u_f_fit)
m5_f <- as.numeric(m5_coef[1])
m5_u <- as.numeric(m5_coef[2])/100000
m5_arr <- as.numeric(m5_coef[3])
m5_arr_u <- as.numeric(m5_coef[4])
m5_h <- as.numeric(m5_coef[5])
m5_w <- as.numeric(m5_coef[6])
m5_rho <- as.numeric(m5_coef[7])
m5_phi <- as.numeric(m5_coef[8])
```


We want to subset the data randomly but we don't want to oversample from some treatments and undersample from other treatments.

This is just a test
```{r, eval=F}
data_boot <- data %>% 
  group_by(treatment_ID) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- data %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

jkl <- data_boot %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

asdf
jkl
```


```{r}
dataset_boot <- dataset %>% 
  group_by(treatment) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- dataset %>% group_by(treatment) %>%
  summarize(mean = mean(inf_status),
            n = n())

jkl <- dataset_boot %>% group_by(treatment) %>%
  summarize(mean = mean(inf_status),
            n = n())

asdf
jkl
```


slice_sample is set to keep the amount of data per treatment the same (30), but resamples from the data with replacement which causes the means to be different. It looks like it is working!



```{r}
m5_ll <- function(f, u, arr_t_f, arr_t_u, h, w, rho, phi){
  
  if(f<0 | h<0 | u<0 | arr_t_f<0 | arr_t_u<0 |
      (u/100000*exp(arr_t_u*((1/15)-(1/15)))*exp(0.1/1000*rho)*exp(0.1/1000*15*phi)) <0 |
     (u/100000*exp(arr_t_u*((1/15)-(1/25)))*exp(1.0/1000*rho)*exp(1.0/1000*25*phi)) <0) {
  
      return(NA)
  
  } 
  
  else {  
  
  
  data <- boot_data
  R_end <- as.data.frame(mapply(m5_sim, 
                                R=data$amt_init*fora_vol/1000, 
                                time=data$time/60/24, 
                                f=f/fora_vol,
                                u = 0, 
                                length=data$mm, 
                                gamma=gamma, 
                                Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp = data$temp,
                                resource = data$resource,
                                w = w,
                                rho = rho,
                                phi = phi))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid), 
                 log = T)
    nll_sum <- -sum(nll)
  
  exp_data <- boot_dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m5_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u/100000, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h,
                                temp=exp_data$temp,
                                resource=exp_data$resource,
                                w = w,
                                rho = rho,
                                phi = phi))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
  
  }
}
```


Finally, we use our optimizer to get the maximum likelihood estimate for all parameters
We'll include the bootstrapping here

```{r, 00, eval=F}

  iterations <- 1
  
  boot_00 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()

      boot_00[[i]] <- mle2(m5_ll, start=list(u = 20,
                                      f=30, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=10000,
                                      w=-0.1,
                                      rho=0.1,
                                      phi=-0.1), 
                     control=list(parscale = c(u = 20,
                                      f=1, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```
 


```{r}

  iterations <- 5
  
  boot_01 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()

      boot_01[[i]] <- mle2(m5_ll, start=list(u = 20,
                                      f=30, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1), 
                     control=list(parscale = c(u = 20,
                                      f=1, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="Nelder-Mead")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


```{r}

  iterations <- 5
  
  boot_02 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()

      boot_02[[i]] <- mle2(m5_ll, start=list(u = 20,
                                      f=30, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1), 
                     control=list(parscale = c(u = 20,
                                      f=1, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


```{r}

  iterations <- 10
  
  boot_03 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()

      boot_03[[i]] <- mle2(m5_ll, start=list(u = 20,
                                      f=30, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1), 
                     control=list(parscale = c(u = 20,
                                      f=1, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r}

  iterations <- 5
  
  boot_04 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- fora_data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
      
      boot_dataset <- life_data %>% 
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()

      boot_04[[i]] <- mle2(m5_ll, start=list(u = 20,
                                      f=30, 
                                      arr_t_f=30, 
                                      arr_t_u=30,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1), 
                     control=list(parscale = c(u = 20,
                                      f=1, 
                                      arr_t_f=10, 
                                      arr_t_u=10,
                                      h=100,
                                      w=0.1,
                                      rho=0.1,
                                      phi=0.1),
                                  maxit=5000),
                                  skip.hessian=F, 
                                  method="BFGS")
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```



```{r}
beet <- c(boot_01, boot_02, boot_03, boot_04)
```



```{r}
# saveRDS(beet, file = here("model_fitting", "combined", "beet", "25_052124.rds"))
mod_f_boot <- c(readRDS(file = here("model_fitting", "combined", "beet", "20_051524.rds")),
                readRDS(file = here("model_fitting", "combined", "beet", "20_051624.rds")),
                readRDS(file = here("model_fitting", "combined", "beet", "35_051724.rds")),
                readRDS(file = here("model_fitting", "combined", "beet", "28_052024.rds")),
                readRDS(file = here("model_fitting", "combined", "beet", "25_052124.rds")))
#mod_f_boot <- readRDS(file = here("model_fitting", "combined", "beet", "47_051324.rds"))
```


```{r}
tib_length <- length(mod_f_boot)

mod_boot_coefs <- tibble(f = rep_len(0, tib_length),
                         u = rep_len(0, tib_length),
                         arr = rep_len(0, tib_length),
                         arr_u = rep_len(0, tib_length),
                         h = rep_len(0, tib_length),
                         w = rep_len(0, tib_length),
                         rho_15 = rep_len(0, tib_length),
                         rho_20 = rep_len(0, tib_length),
                         rho_25 = rep_len(0, tib_length),
                         warning = NA)


for(i in 1:length(mod_f_boot)){
  if(mod_f_boot[[i]]@details[4] == 52){
    print(paste(i, "convergence_failure", sep="_"))
    mod_boot_coefs$f[i] <- NA
    mod_boot_coefs$u[i] <- NA
    mod_boot_coefs$arr[i] <- NA
    mod_boot_coefs$arr_u[i] <- NA
    mod_boot_coefs$h[i] <- NA
    mod_boot_coefs$w[i] <- NA
    mod_boot_coefs$rho_15[i] <- NA
    mod_boot_coefs$rho_20[i] <- NA
    mod_boot_coefs$rho_25[i] <- NA
    mod_boot_coefs$warning[i] <- "52"
  }
  else if(mod_f_boot[[i]]@details[4] == 10){
    print(paste(i, "convergence_failure", sep="_"))
    mod_boot_coefs$f[i] <- NA
    mod_boot_coefs$u[i] <- NA
    mod_boot_coefs$arr[i] <- NA
    mod_boot_coefs$arr_u[i] <- NA
    mod_boot_coefs$h[i] <- NA
    mod_boot_coefs$w[i] <- NA
    mod_boot_coefs$rho_15[i] <- NA
    mod_boot_coefs$rho_20[i] <- NA
    mod_boot_coefs$rho_25[i] <- NA
    mod_boot_coefs$warning[i] <- "10"
  }
  else if(mod_f_boot[[i]]@min == 0){
    print(paste(i, "zero_ll", sep="_"))
    mod_boot_coefs$f[i] <- NA
    mod_boot_coefs$u[i] <- NA
    mod_boot_coefs$arr[i] <- NA
    mod_boot_coefs$arr_u[i] <- NA
    mod_boot_coefs$h[i] <- NA
    mod_boot_coefs$w[i] <- NA
    mod_boot_coefs$rho_15[i] <- NA
    mod_boot_coefs$rho_20[i] <- NA
    mod_boot_coefs$rho_25[i] <- NA
    mod_boot_coefs$warning[i] <- "zero_ll"
  }
  else if(mod_f_boot[[i]]@details[4] == 1){
  print(paste(i, "max_iter_reached", sep="_"))
  boot_coef <- coef(mod_f_boot[[i]])
  mod_boot_coefs$u[i] <- as.numeric(boot_coef[1])/u_factor
  mod_boot_coefs$f[i] <- as.numeric(boot_coef[2])
  mod_boot_coefs$arr[i] <- as.numeric(boot_coef[3])
  mod_boot_coefs$arr_u[i] <- as.numeric(boot_coef[4])
  mod_boot_coefs$h[i] <- as.numeric(boot_coef[5])*h_factor
  mod_boot_coefs$w[i] <- as.numeric(boot_coef[6])
  mod_boot_coefs$rho_15[i] <- as.numeric(boot_coef[7])
  mod_boot_coefs$rho_20[i] <- as.numeric(boot_coef[8])/rho_20_factor
  mod_boot_coefs$rho_25[i] <- as.numeric(boot_coef[9])/rho_25_factor
  mod_boot_coefs$warning[i] <- "1"
  }
  else{
  boot_coef <- coef(mod_f_boot[[i]])
  mod_boot_coefs$u[i] <- as.numeric(boot_coef[1])/u_factor
  mod_boot_coefs$f[i] <- as.numeric(boot_coef[2])
  mod_boot_coefs$arr[i] <- as.numeric(boot_coef[3])
  mod_boot_coefs$arr_u[i] <- as.numeric(boot_coef[4])
  mod_boot_coefs$h[i] <- as.numeric(boot_coef[5])*h_factor
  mod_boot_coefs$w[i] <- as.numeric(boot_coef[6])
  mod_boot_coefs$rho_15[i] <- as.numeric(boot_coef[7])
  mod_boot_coefs$rho_20[i] <- as.numeric(boot_coef[8])/rho_20_factor
  mod_boot_coefs$rho_25[i] <- as.numeric(boot_coef[9])/rho_25_factor
  mod_boot_coefs$warning[i] <- "0"
  }
}
```


```{r}
mod_boot_coefs %<>% drop_na()

mod_boot_coefs %>% ggplot(., aes(x = f)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = u)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = arr)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = arr_u)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = h)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = w)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_15)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_20)) + geom_histogram()
mod_boot_coefs %>% ggplot(., aes(x = rho_25)) + geom_histogram()
```




quantiles
```{r}
mod_quantiles <- tibble(id = c("est", "mean", "lower.025", "upper.975"),
                        f = NA,
                        u = NA,
                        arr = NA,
                        arr_u = NA,
                        h = NA,
                        w = NA,
                        rho_15 = NA,
                        rho_20 = NA,
                        rho_25 = NA)

mod_quantiles$f[1] <- coef(m5a_u_f_fit)[2]
mod_quantiles$f[2] <- mean(mod_boot_coefs$f)
mod_quantiles$f[3] <- quantile(mod_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$f[4] <- quantile(mod_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$u[1] <- coef(m5a_u_f_fit)[1]
mod_quantiles$u[2] <- mean(mod_boot_coefs$u)
mod_quantiles$u[3] <- quantile(mod_boot_coefs$u, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$u[4] <- quantile(mod_boot_coefs$u, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$arr[1] <- coef(m5a_u_f_fit)[3]
mod_quantiles$arr[2] <- mean(mod_boot_coefs$arr)
mod_quantiles$arr[3] <- quantile(mod_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$arr[4] <- quantile(mod_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$arr_u[1] <- coef(m5a_u_f_fit)[4]
mod_quantiles$arr_u[2] <- mean(mod_boot_coefs$arr_u)
mod_quantiles$arr_u[3] <- quantile(mod_boot_coefs$arr_u, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$arr_u[4] <- quantile(mod_boot_coefs$arr_u, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$h[1] <- coef(m5a_u_f_fit)[5]
mod_quantiles$h[2] <- mean(mod_boot_coefs$h)
mod_quantiles$h[3] <- quantile(mod_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$h[4] <- quantile(mod_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$w[1] <- coef(m5a_u_f_fit)[6]
mod_quantiles$w[2] <- mean(mod_boot_coefs$w)
mod_quantiles$w[3] <- quantile(mod_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$w[4] <- quantile(mod_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$rho_15[1] <- coef(m5a_u_f_fit)[7]
mod_quantiles$rho_15[2] <- mean(mod_boot_coefs$rho_15)
mod_quantiles$rho_15[3] <- quantile(mod_boot_coefs$rho_15, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_15[4] <- quantile(mod_boot_coefs$rho_15, probs=seq(0.025, 0.975, 0.95))[2]

mod_quantiles$rho_20[1] <- coef(m5a_u_f_fit)[8]
mod_quantiles$rho_20[2] <- mean(mod_boot_coefs$rho_20)
mod_quantiles$rho_20[3] <- quantile(mod_boot_coefs$rho_20, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_20[4] <- quantile(mod_boot_coefs$rho_20, probs=seq(0.025, 0.975, 0.95))[2]


mod_quantiles$rho_25[1] <- coef(m5a_u_f_fit)[9]
mod_quantiles$rho_25[2] <- mean(mod_boot_coefs$rho_25)
mod_quantiles$rho_25[3] <- quantile(mod_boot_coefs$rho_25, probs=seq(0.025, 0.975, 0.95))[1]
mod_quantiles$rho_25[4] <- quantile(mod_boot_coefs$rho_25, probs=seq(0.025, 0.975, 0.95))[2]

```


```{r}
mod_quantiles %<>% pivot_longer(cols = f:rho_25) %>% pivot_wider(., names_from="id")

```

```{r}
theme_set(theme_bw(base_size = 12))

rho_boot_plot <- mod_quantiles %>% filter(name %in% c("rho_15", "rho_20", "rho_25")) %>%
  mutate(name = gsub("rho_", "", x=name)) %>%
  ggplot(., aes(x = name, y=est, color = name)) + 
  geom_point(size = 3) + 
  geom_linerange(linewidth = 1, 
                 aes(ymin=lower.025, ymax=upper.975)) + 
  labs(x = expression(rho), y = "Estimate (Boostrapped 95% CI)", color = "Temp") + 
  theme(legend.position = "none") + 
  scale_color_manual(values = c("#FFC107", "#21918c", "#440154"))

rho_boot_plot

ggsave(here("workshop", "figures", "rho_boot_plot.png"), width = 3, height = 4)
```







