---
title: "base_models"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base", "src.R")) #load packages and some global variables
source(here("model_fitting", "prep.Rmd")) #clean data and declare functions
```

# Independent Model

This model assumes constant f and constant u for all treatments

$$
\frac{dR}{dt} = -L^{\gamma} fRS\\
$$


```{r, m1_sim}
m1_sim <- function(R, time, f, u, length, gamma, Z){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f*(length^gamma),
              u=u)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r, m1_ll}
m1_ll <- function(f, u){
  data <- tmp
  R_end <- as.data.frame(mapply(m1_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m1_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m1_u_f_fit <- mle2(m1_ll, start=list(u = 0.0001, f=1), 
                     control=list(parscale = c(u = 0.0001, f=1)),
                     skip.hessian=F, method="L-BFGS-B", lower=c(u = 0, f = 0), upper=c(u = 1, f = Inf))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_u_f_fit)

saveRDS(m1_u_f_fit, file = here("mle","update","m1_fit.rds"))
```


# Temperature-Dependent Model

This model includes an Arrhenius function to modify f and u separately as a function of temperature.


$$
\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\\  

u = ue^{T_{A}(1/T_{R}-1/T)}
$$


```{r, m2_sim}
m2_sim <- function(R, time, f, u, length, gamma, Z, arr_t_f, arr_t_u, ref_t, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f*(length^gamma)*exp(arr_t_f*(1/ref_t - 1/temp)),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r, m2_ll}
m2_ll <- function(f, u, arr_t_f, arr_t_u){
  data <- tmp
  R_end <- as.data.frame(mapply(m2_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                ref_t=ref_t,
                                temp=data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m2_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, u=u, 
                                length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                ref_t=ref_t,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


Now we use the optimizer
```{r, m2_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m2_u_f_fit <- mle2(m2_ll, start=list(u = 0.00001, f=1,
                                     arr_t_f = 10,
                                     arr_t_u = 10), 
                     control=list(parscale = c(u = 0.00001, f=1,
                                               arr_t_f = 10,
                                               arr_t_u = 10)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f=0, arr_t_u=0), 
                   upper=c(u = 1, f = Inf, arr_t_f=Inf, arr_t_u=Inf))
end_time <- Sys.time()
m2_runtime <- end_time - start_time
m2_runtime

coef(m2_u_f_fit)

saveRDS(m2_u_f_fit, file = here("mle","update","m2_fit.rds"))
```




# Resource-depdendent Model

This model includes a handling time function for f but no modification to u.


$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{1 + fL^{\gamma}hR}S \\
$$


```{r, m3_sim}
m3_sim <- function(R, time, f, u, length, gamma, Z, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=f*(length^gamma)/(1+f*(length^gamma)*h*R),
              u=u)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r, m3_ll}
m3_ll <- function(f, u, h, k){
  data <- tmp
  R_end <- as.data.frame(mapply(m3_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                h=h*fora_vol))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m3_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                h=h*life_vol))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


Now we use the optimizer
```{r, m3_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m3_u_f_fit <- mle2(m3_ll, start=list(u = 0.000001, f=1, h=1), 
                     control=list(parscale = c(u = 0.000001, f=1, h=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, h=0), 
                   upper=c(u = 1, f = Inf, h=Inf))
end_time <- Sys.time()
m3_runtime <- end_time - start_time
m3_runtime

coef(m3_u_f_fit)

saveRDS(m3_u_f_fit, file = here("mle","update","m3_fit.rds"))
```




# Full Model

This version uses an arrhenius function for both f and u and a handling time function for f only.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{1 + fe^{T_{A}(1/T_{R}-1/T)}hL^{\gamma}R} S \\
u = ue^{T_{A}(1/T_{R}-1/T)}
$$

```{r, m4_sim}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/(1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r, m4_ll}
m4_ll <- function(f, u, arr_t_f, arr_t_u, h){
  data <- tmp
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


Now we use the optimizer
```{r, m4_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m4_u_f_fit <- mle2(m4_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf))
end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_f_fit)

saveRDS(m4_u_f_fit, file = here("mle","update","m4_fit.rds"))
```