---
title: "interaction_models"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base", "src.R")) #load packages and some global variables
source(here("model_fitting", "prep.Rmd")) #clean data and declare functions
```


```{r, m4_sim}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/(1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

# Model 5 - Resource on temperature interaction

Same as model 4 but we include a linear interaction term for the arrhenius coefficient, thus representing the interactive effect of resources on the temperature effect

```{r, m5a_ll}
m5a_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + data$resource*p_f,
                                arr_t_u=arr_t_u + data$resource*p_u,
                                h=h*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + exp_data$resource*p_f,
                                arr_t_u=arr_t_u + exp_data$resource*p_u,
                                h=h*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


Need to rerun
```{r, m5a_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m5a_u_f_fit <- mle2(m5a_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf))
end_time <- Sys.time()
m5a_runtime <- end_time - start_time
m5a_runtime

coef(m5a_u_f_fit)

saveRDS(m5a_u_f_fit, file = here("mle","update","m5a_fit.rds"))
```

Model 5a with an exponential interaction term rather than linear

```{r, m5b_ll}
m5b_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*exp(data$resource*p_f),
                                arr_t_u=arr_t_u*exp(data$resource*p_u),
                                h=h*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*(exp_data$resource*p_f),
                                arr_t_u=arr_t_u*(exp_data$resource*p_u),
                                h=h*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m5b_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m5b_u_f_fit <- mle2(m5b_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf))
end_time <- Sys.time()
m5b_runtime <- end_time - start_time
m5b_runtime

coef(m5b_u_f_fit)

saveRDS(m5b_u_f_fit, file = here("mle","update","m5b_fit.rds"))
```

# Model 6 - Temperature on Resource interaction

Same as model 4 with a linear interaction for how handling time is affected by temperature, thus incoporating an interactive effect of temperature on the resource effect.

```{r, m6a_ll}
m6a_ll <- function(f, u, arr_t_f, arr_t_u, h, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=(h + data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=(h + exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m6a_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m6a_u_f_fit <- mle2(m6a_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, w=0.1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, w=0.1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, w=Inf))
end_time <- Sys.time()
m6a_runtime <- end_time - start_time
m6a_runtime

coef(m6a_u_f_fit)

saveRDS(m6a_u_f_fit, file = here("mle","update","m6a_fit.rds"))
```


Same as model 6a but with an exponential interactive term

```{r, m6b_ll}
m6b_ll <- function(f, u, arr_t_f, arr_t_u, h, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=(h + data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f,
                                arr_t_u=arr_t_u,
                                h=h*exp(exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m6b_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m6b_u_f_fit <- mle2(m6b_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, w=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, w=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, w=Inf))
end_time <- Sys.time()
m6b_runtime <- end_time - start_time
m6b_runtime

coef(m6b_u_f_fit)

saveRDS(m6b_u_f_fit, file = here("mle","update","m6b_fit.rds"))
```


# Model 7 - Full interaction

Full interaction model where both temperature and resources effects are functions of each other.

Model 7a is linear interaction terms

```{r, m7a_ll}
m7a_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + data$resource*p_f,
                                arr_t_u=arr_t_u + data$resource*p_u,
                                h=(h + data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + exp_data$resource*p_f,
                                arr_t_u=arr_t_u + exp_data$resource*p_u,
                                h=(h + exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m7a_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m7a_u_f_fit <- mle2(m7a_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf, w=Inf))
end_time <- Sys.time()
m7a_runtime <- end_time - start_time
m7a_runtime

coef(m7a_u_f_fit)

saveRDS(m7a_u_f_fit, file = here("mle","update","m7a_fit.rds"))
```

model 7b is linear effect of resources on temp and exponential effect of temperature on resources

```{r, m7b_ll}
m7b_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + data$resource*p_f,
                                arr_t_u=arr_t_u + data$resource*p_u,
                                h=h*exp(data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f + exp_data$resource*p_f,
                                arr_t_u=arr_t_u + exp_data$resource*p_u,
                                h=h*exp(exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m7b_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m7b_u_f_fit <- mle2(m7b_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf, w=Inf))
end_time <- Sys.time()
m7b_runtime <- end_time - start_time
m7b_runtime

coef(m7b_u_f_fit)

saveRDS(m7b_u_f_fit, file = here("mle","update","m7b_fit.rds"))
```

model 7c is exponential effect of resource on temp and linear effect of temp on resource

```{r, m7c_ll}
m7c_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*exp(data$resource*p_f),
                                arr_t_u=arr_t_u*exp(data$resource*p_u),
                                h=(h + data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*exp(exp_data$resource*p_f),
                                arr_t_u=arr_t_u*exp(exp_data$resource*p_u),
                                h=(h + exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m7c_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m7c_u_f_fit <- mle2(m7c_ll, start=list(u = 0.0001, f=1, arr_t_f=100, arr_t_u=100, h=1, p_f=1, p_u=0.1, w=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=100, arr_t_u=100, h=1, p_f=1, p_u=0.1, w=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf, w=Inf))
end_time <- Sys.time()
m7c_runtime <- end_time - start_time
m7c_runtime

coef(m7c_u_f_fit)

saveRDS(m7c_u_f_fit, file = here("mle","update","m7c_fit.rds"))
```

model 7d is exponential interactive effect both ways

```{r, m7d_ll}
m7d_ll <- function(f, u, arr_t_f, arr_t_u, h, p_f, p_u, w){
  data <- tmp
  
  R_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*fora_vol/1000, time=data$time/60/24, 
                                f=f/fora_vol,
                                 u = 0, #u actually not important for this part. just wanted to use a single deSolve function for both
                                 length=data$mm, gamma=gamma, Z=0,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*exp(data$resource*p_f),
                                arr_t_u=arr_t_u*exp(data$resource*p_u),
                                h=h*exp(data$temp*w)*fora_vol,
                                temp = data$temp))
  colnames(R_end) <- "R_end"
  data$end <- R_end$R_end
  data %<>% mutate(resid = log(end) - log(amt_rem*fora_vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_sum <- -sum(nll, na.rm = T)
  
  exp_data <- dataset %>% filter(exposed==TRUE)
#  exp_data <- dataset_tmp %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, R=exp_data$resource*life_vol/1000, time=exp_data$time, f=f/life_vol, 
                                u=u, length = exp_data$life_mm, gamma=gamma, Z=spore_conc*life_vol,
                                ref_t=ref_t,
                                arr_t_f=arr_t_f*exp(exp_data$resource*p_f),
                                arr_t_u=arr_t_u*exp(exp_data$resource*p_u),
                                h=h*exp(exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- nll_sum + -sum(exp_data$ll)
  return(nll_sum)
}
```


```{r, m7d_mle, eval=F}
start_time <- Sys.time()
tmp <- data
m7d_u_f_fit <- mle2(m7d_ll, start=list(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1), 
                     control=list(parscale = c(u = 0.0001, f=1, arr_t_f=10, arr_t_u=10, h=1, p_f=1, p_u=1, w=1)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, f = 0, arr_t_f = 0, arr_t_u = 0, h = 0, p_f=-Inf, p_u=-Inf, w=-Inf), 
                   upper=c(u = 1, f = Inf, arr_t_f = Inf, arr_t_u = Inf, h = Inf, p_f=Inf, p_u=Inf, w=Inf))
end_time <- Sys.time()
m7d_runtime <- end_time - start_time
m7d_runtime

coef(m7d_u_f_fit)

saveRDS(m7d_u_f_fit, file = here("mle","update","m7d_fit.rds"))
```