---
title: "prep"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = F}
library(here)
source(here("base","src.R")) #load packages and some global variables
```

# Notes
 - in the first data cleaning chunk, we removed individuals who were NA for inf because they died too young to assess. I'm not sure if this is the right way to handle these data. Maybe they should just be treated as uninfected instead.



# Read data and set global params

```{r}
fitness <- read.csv(here("raw_data/main_fitness_edit.csv")) #must be read.csv
fitness %<>% dplyr::select(tube, temp_id, REMOVED, KBP, final_date)
mort <-  read_csv(here("raw_data/main_mort_edit.csv"))
lengths <- read_csv(here("raw_data", "day5_length.csv")) #from life table
lengths %<>% filter(temp_id %in% c(15,20,25))


dataset <- left_join(mort,fitness) #life table data

data <- readRDS(here("processed_data","foraging_raw.rds")) #foraging rate assay
data_summ <- readRDS(here("processed_data", "foraging.rds")) #foraging rate assay summary

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID) #vectors for treatment IDs
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


fora_vol <- 15 #mL - volume of tube from foraging rate assay
life_vol <- 50 #mL - volume of tube from life table experiment
spore_conc <- 200 #spores/mL - spore inoculation concentration from life table experiment
gamma <- 2 #size correction term - results in length^2
ref_t <- 15 #celsius - referene temperature

```

"Dataset" are the data from the life table experiment
Requires a bit of cleaning
```{r}
dataset %<>% filter(species == "D") %>% #only daphnia for this analysis
  filter(temp %in% const_temp) #only constant temp for this analysis

dataset %<>% mutate(birthdate = "4/5/22", #set birth date for all daphnia
                    lifespan = as.numeric(mdy(final_date) - mdy(birthdate)), #calculate lifespan. final_date is date of death or end of expt
                    temp = as.numeric(temp),
                    treatment = paste(temp, resource, sep = "_")) %>% 
  filter(is.na(male)) %>% #remove males
  filter(is.na(missing)) %>% #remove missing. some daphnia were lost during experiment. these are removed from analysis
  filter(!is.na(inf)) #remove NAs for inf for estimating beta. sometimes they died too young to tell

dataset %<>% mutate(inf_status = inf, 
                    dead = ifelse(is.na(REMOVED) & is.na(KBP), 1, 0)) #marked as "dead" if they were not removed or killed by pipette (KBP)


dataset %<>% mutate(spore_exposure = 200, #spores/mL
                    uninf = 1-inf_status,
                    time = 1, #duration of exposure in days
                    trt = paste(temp, resource, species, sep = "_"))
```

We use average lengths later on. We need to use averages because we weren't able to measure length for every individual.
For the foraging rate assay, these are the actual lengths because we measured the length of each individual at the end of the assay.

For the life table data, these are the lengths of a representative number of individuals right before the rest were exposed to spores. We take an average for these lengths since we didn't have length data for every individual.

```{r}
lengths %<>% mutate(mm = raw_meas*17.86/1000)
#at default magnification (5.6x), 1 unit is equal to 17.86 micron

length_summ <- lengths %>% 
  group_by(temp_id, resource) %>% 
  summarize(life_mm = mean(mm),
            var = var(mm),
            sd = sd(mm),
            se = sd(mm)/sqrt(n())) %>%
  ungroup() %>%
  dplyr::select(temp_id, resource, life_mm)

length_summ %<>% add_row(temp_id=as.character(25), resource=as.numeric(0.5), life_mm=1.16) #midpoint between 1.0 and 0.1
```

Join length data to both dataframes
Some of the length data from the foraging rate assay are missing so we impute these values from the averages from the data we do have.
We were also missing length data for one treatment from the life table so we use the foraging rate data lengths to replace those as well.

```{r}
dataset %<>% left_join(length_summ)

length_summ %<>% mutate(ID = paste(temp_id, resource, sep="_")) %>% dplyr::select(-c(temp_id, resource))


mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))

mean_length_summ %<>% rename(fora_mm = "mm_mean")
dataset %<>% left_join(., mean_length_summ)
```


Every model formulation uses this defined system of ode's as the backbone to build the other models off of.
```{r}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  with(as.list(params),{
    dR <- -f*R*(S+I)
    dS <- -u*f*Z*S
    dI <- u*f*Z*S
    dZ <- -f*Z*(S+I)
    res <- c(dR, dS, dI, dZ)
    list(res)}
    )
}
```

