---
title: "bootstrap_u.Rmd"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))
```


# Read data and set global params

```{r}
fitness <- read.csv(here("raw_data/main_fitness_edit.csv")) #must be read.csv
fitness %<>% dplyr::select(tube, temp_id, REMOVED, KBP, final_date)
mort <-  read_csv(here("raw_data/main_mort_edit.csv"))
lengths <- read_csv(here("raw_data", "day5_length.csv")) #from life table
lengths %<>% filter(temp_id %in% c(15,20,25))


dataset <- left_join(mort,fitness) #life table data

data <- readRDS(here("processed_data","foraging_raw.rds")) #foraging rate assay
data_summ <- readRDS(here("processed_data", "foraging.rds")) #foraging rate assay summary

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


fora_vol <- 15 #mL
life_vol <- 50 #mL
spore_conc <- 200 #spores/mL
gamma <- 2 
ref_t <- 15 #celsius

```

Dataset are the data from the life table experiment
Requires a bit of cleaning
```{r}
dataset %<>% filter(species == "D") %>% #only daphnia for this analysis
  filter(temp %in% const_temp) #only constant temp for this analysis

dataset %<>% mutate(birthdate = ifelse(species == "daphnia", "4/5/22", "4/6/22"), 
                    lifespan = as.numeric(mdy(final_date) - mdy(birthdate)),
                    temp = as.numeric(temp),
                    treatment = paste(temp, resource, sep = "_")) %>% 
  filter(is.na(male)) %>% #remove males
  filter(is.na(missing)) %>% #remove missing
  filter(!is.na(inf)) #remove NAs for inf for estimating beta. sometimes they died too young to tell

dataset %<>% mutate(inf_status = inf, dead = ifelse(is.na(REMOVED) & is.na(KBP), 1, 0))


dataset %<>% mutate(spore_exposure = 200, #spores/mL
                    uninf = 1-inf_status,
                    time = 1, #duration of exposure in days
                    trt = paste(temp, resource, species, sep = "_"))
```

We use average lengths later on. We need to use averages because we weren't able to measure length for every individual.
For the foraging rate assay, these are the actual lengths because we measured the length of each individual at the end of the assay.

For the life table data, these are the lengths of a representative number of individuals right before the rest were exposed to spores. We take an average for these lengths since we didn't have length data for every individual.

```{r}
lengths %<>% mutate(mm = raw_meas*17.86/1000)
#at default magnification (5.6x), 1 unit is equal to 17.86 micron

length_summ <- lengths %>% 
  group_by(temp_id, resource) %>% 
  summarize(life_mm = mean(mm),
            var = var(mm),
            sd = sd(mm),
            se = sd(mm)/sqrt(n())) %>%
  ungroup() %>%
  dplyr::select(temp_id, resource, life_mm)

length_summ %<>% add_row(temp_id=as.character(25), resource=as.numeric(0.5), life_mm=1.16) #midpoint between 1.0 and 0.1
```

Join length data to both dataframes
Some of the length data from the foraging rate assay are missing so we impute these values from the averages from the data we do have.
We were also missing length data for one treatment from the life table so we use the foraging rate data lengths to replace those as well.

```{r}
dataset %<>% left_join(length_summ)

length_summ %<>% mutate(ID = paste(temp_id, resource, sep="_")) %>% dplyr::select(-c(temp_id, resource))


mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))

mean_length_summ %<>% rename(fora_mm = "mm_mean")
dataset %<>% left_join(., mean_length_summ)
```


```{r}
m6c_quantiles <- readRDS(file = here("mle", "m6c_quantiles.rds"))

f_est <- m6c_quantiles$f[1]
f_lower <- m6c_quantiles$f[3]
f_upper <- m6c_quantiles$f[4]

arr_f_est <- m6c_quantiles$arr[1]
arr_f_lower <- m6c_quantiles$arr[3]
arr_f_upper <- m6c_quantiles$arr[4]

h_est <- m6c_quantiles$h[1]
h_lower <- m6c_quantiles$h[3]
h_upper <- m6c_quantiles$h[4]

w_est <- m6c_quantiles$w[1]
w_lower <- m6c_quantiles$w[3]
w_upper <- m6c_quantiles$w[4]
```


```{r}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  with(as.list(params),{
    dR <- -f*R*(S+I)
    dS <- -u*f*Z*S
    dI <- u*f*Z*S
    dZ <- -f*Z*(S+I)
    res <- c(dR, dS, dI, dZ)
    list(res)}
    )
}
```

```{r}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m4_ll <- function(u, arr_t_u, rho){

  exp_data <- boot_data

  
  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f_est/life_vol, 
                                u=u*exp(exp_data$resource*rho), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = arr_t_u,
                                h = (h_est + exp_data$temp*w_est)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  # print(u)
  # print(arr_t_u)
  # print(rho)
  
  return(nll_sum)
}
```




```{r, 00}

iterations <- 10

m4_u_boot_00 <- list()

start_time <- Sys.time()
for(i in 1:iterations){
  
  boot_data <- dataset %>% 
        filter(exposed==TRUE) %>%
        group_by(treatment) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
  
  m4_u_boot_00[[i]] <- mle2(m4_ll, start=list(u = 0.0001, 
                                     arr_t_u=10, 
                                     rho=0.01), 
                     control=list(parscale = c(u = 0.0001, 
                                     arr_t_u=10, 
                                     rho=0.01)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, 
                           arr_t_f = 0, 
                           rho = -Inf), 
                   upper=c(u = Inf, 
                           arr_t_f = Inf, 
                           rho = Inf))
  print(i)
  end_time <- Sys.time()
  print(end_time-start_time)
}

end_time <- Sys.time()
print(end_time - start_time)

```



```{r, 00}

  iterations <- 10
  
  m6c_f_boot_00 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_00[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=10, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```