---
title: "Epidemiological Parameters"
format: html
editor: visual
---

# Estimating parameters

The purpose of this script is to estimate different parameters using life table data for daphnia and ceriodaphnia with and without infections reared under different temperature and resource conditions.

This table goes through all of the different treatment conditions. I should update this with sample sizes later.

+--------------+-----------------+------------------+------------+------------+
| Species      | Temperature (C) | Resource (mgC/L) | Exposure   | n          |
+==============+=================+==================+============+============+
| Daphnia      | -   15          | -   1.0          | -   Yes    |            |
|              | -   20          | -   0.5          | -   No     |            |
|              | -   25          | -   0.1          |            |            |
+--------------+-----------------+------------------+------------+------------+
| Daphnia      | -   +/- 1       | -   1.0          | -   Yes    |            |
|              | -   +/- 3       |                  | -   No     |            |
|              | -   +/- 7       |                  |            |            |
+--------------+-----------------+------------------+------------+------------+
| Ceriodaphnia | -   15          | -   1.0          | -   Yes    |            |
|              | -   20          |                  | -   No     |            |
|              | -   25          |                  |            |            |
+--------------+-----------------+------------------+------------+------------+

: Experimental Design

# R0

Previous experiments using this system have estimated R0 according to this formula. I'll have to go through this and do it myself later but for now we can trust them.

\$\$ R\emptyset = \frac { \beta S^* \sigma }{ \mu } \\

\beta = transmission rate \\

S\^\*= equilibrium susceptible host density \\

\sigma = spore yield \\

\mu = degradation rate \\ \$\$

Okay gotta go back and figure out how to fix the latex to render properly in quarto.

```{r}
#| label: load_packages
#| include: false

library(here)

source(here("base","src.R"))
library(bbmle)
```

```{r}
#| label: beta


```
