---
title: "Epidemiological Traits"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

```{r, message=F}
library(here)

source(here("base","src.R"))
```

```{r}
beta.summary <- readRDS(here("processed_data", "beta_summary.rds"))
lt_full <- readRDS(here("processed_data", "lt_full_summary.rds"))
spores <- readRDS(here("processed_data", "spore_yield.rds"))
```

# Beta

```{r}
beta_fig <- beta.summary %>% filter(species=="D" & temp %in% const_temp) %>% 
  ggplot(.,aes(x=temp, y = beta.est, color = temp)) +
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin = beta.025, ymax = beta.975), position = position_dodge(width = 0.5)) + 
  facet_wrap(. ~ as.factor(resource), nrow = 1) + 
  labs(y = "Beta", x = "Temp (C)")


```

<!-- Exposure dose, time, and volume were meant to be consistent across all treatments which means that Beta should end up as a function of the probability of infection. As expected, the patterns in Beta and probabilities of infection match well. -->

<!-- ```{r} -->
<!-- prevalence <- readRDS(here("processed_data", "prevalence.rds")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- prevalence %>% filter(temp %in% const_temp & species =="D") %>% -->
<!--   ggplot(.,aes(x=ID, y = prev, group = temp, color = temp))  + -->
<!--   geom_point(aes(), position = position_dodge(width = 0.5)) +  -->
<!--   geom_errorbar(aes(ymin = conf$lower, ymax = conf$upper), position = position_dodge(width = 0.5)) + -->
<!--   theme_minimal() + labs(title = "Probability of Infection") -->
<!-- ``` -->

# Susceptible host density

```{r}
lt_full %>% filter(species=="D", temp_var == 0) %>% 
  ggplot(.,aes(x=as.factor(temp_id),y=S.S.U, color=temp_id)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin=S.S.025, ymax=S.S.975)) + 
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(. ~ as.factor(resource), nrow = 1) + 
  labs(y = "Susceptible Host Density", x = "Temp (C)" )

```

# Spore yield

```{r, message = F}
# spores %>% filter(temp %in% const_temp & species =="D") %>%  
#   ggplot(., aes(x=temp, y = log_mean_yield)) + 
#   geom_point(aes(), position = position_dodge(width = 0.5)) + 
#   geom_line(aes(group = temp), position = position_dodge(width = 0.5)) +
#   geom_errorbar(aes(ymin = log_mean_yield-log_se, ymax = log_mean_yield+log_se), position = position_dodge(width = 0.5)) +
#   facet_wrap(vars(resource)) + 
#   labs(y = "ln(Average Spore Yield)", x = "Temp (C)")

spores %>% filter(temp %in% const_temp & species =="D") %>%  
  ggplot(., aes(x=temp, y = mean_yield, color = temp)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_line(aes(group = temp), position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = mean_yield-se, ymax = mean_yield+se), position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(vars(resource)) + 
  labs(y = "Average Spore Yield", x = "Temp (C)")
```


# R0

Parameters used

d = death rate (taken from bootstrap estimate) #ind/day

b = birth rate (taken from bootstrap estimate) #ind/day

K = carrying capacity (assumed constant) at 250 ind.


Parameters used for R0 include

S = susceptible host density (estimated from bootstrap data) ind.

B = transmission parameter (estimated from bootstrap) mL per day

A = spore yield # spores/ind.

M = degradation rate at 0.2 ml*spores/day


```{r}
lt_full %>% filter(species=="D", temp_var == 0) %>% 
  ggplot(.,aes(x=as.factor(temp_id),y=S.R_naught, color=temp_id)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin=S.R_naught.025, ymax=S.R_naught.975)) + 
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(. ~ as.factor(resource), nrow = 1) + 
  labs(y = "R0", x = "Temp (C)" )
```


# Beta

```{r}
beta.summary %>% filter(species=="D" & temp %in% const_temp) %>% 
  ggplot(.,aes(x=as.factor(resource), y = beta.est, color = temp)) +
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin = beta.025, ymax = beta.975), position = position_dodge(width = 0.5)) + 
  facet_wrap(. ~ as.factor(temp), nrow = 1) + 
  labs(y = "Beta", x = "Resource")

```

<!-- Exposure dose, time, and volume were meant to be consistent across all treatments which means that Beta should end up as a function of the probability of infection. As expected, the patterns in Beta and probabilities of infection match well. -->

<!-- ```{r} -->
<!-- prevalence <- readRDS(here("processed_data", "prevalence.rds")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- prevalence %>% filter(temp %in% const_temp & species =="D") %>% -->
<!--   ggplot(.,aes(x=ID, y = prev, group = temp, color = temp))  + -->
<!--   geom_point(aes(), position = position_dodge(width = 0.5)) +  -->
<!--   geom_errorbar(aes(ymin = conf$lower, ymax = conf$upper), position = position_dodge(width = 0.5)) + -->
<!--   theme_minimal() + labs(title = "Probability of Infection") -->
<!-- ``` -->

# Susceptible host density

```{r}
lt_full %>% filter(species=="D", temp_var == 0) %>% 
  ggplot(.,aes(x=as.factor(resource),y=S.S.U, color=temp_id)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin=S.S.025, ymax=S.S.975)) + 
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(. ~ as.factor(temp_id), nrow = 1) + 
  labs(y = "Susceptible Host Density", x = "Resource" )

```

# Spore yield

```{r, message = F}
# spores %>% filter(temp %in% const_temp & species =="D") %>%  
#   ggplot(., aes(x=temp, y = log_mean_yield)) + 
#   geom_point(aes(), position = position_dodge(width = 0.5)) + 
#   geom_line(aes(group = temp), position = position_dodge(width = 0.5)) +
#   geom_errorbar(aes(ymin = log_mean_yield-log_se, ymax = log_mean_yield+log_se), position = position_dodge(width = 0.5)) +
#   facet_wrap(vars(resource)) + 
#   labs(y = "ln(Average Spore Yield)", x = "Temp (C)")

spores %>% filter(temp %in% const_temp & species =="D") %>%  
  ggplot(., aes(x=as.factor(resource), y = mean_yield, color = temp)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_line(aes(group = temp), position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = mean_yield-se, ymax = mean_yield+se), position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(vars(temp)) + 
  labs(y = "Average Spore Yield", x = "Resource")
```


# R0

Parameters used

d = death rate (taken from bootstrap estimate) #ind/day

b = birth rate (taken from bootstrap estimate) #ind/day

K = carrying capacity (assumed constant) at 250 ind.


Parameters used for R0 include

S = susceptible host density (estimated from bootstrap data) ind.

B = transmission parameter (estimated from bootstrap) mL per day

A = spore yield # spores/ind.

M = degradation rate at 0.2 ml*spores/day


```{r}
lt_full %>% filter(species=="D", temp_var == 0) %>% 
  ggplot(.,aes(x=as.factor(resource),y=S.R_naught, color=temp_id)) + 
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_linerange(aes(ymin=S.R_naught.025, ymax=S.R_naught.975)) + 
  scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  facet_wrap(. ~ as.factor(temp_id), nrow = 1) + 
  labs(y = "R0", x = "Resource" )
```
