---
title: "Epidemiological Traits"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

```{r, message=F}
library(here)

source(here("base","src.R"))
```

```{r}
beta.summary <- readRDS(here("processed_data", "beta_summary.rds"))
```

Beta was estimated by bootstrapping 95% confidence intervals around a mean using data on probability of infection, exposure dose, exposure time, and exposure volume.

```{r}
beta.summary %>% filter(species=="D" & temp %in% const_temp) %>% ggplot(.,aes(x=trt, y = beta.est, color = temp)) +
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_errorbar(aes(ymin = beta.025, ymax = beta.975), position = position_dodge(width = 0.5)) +
  theme_minimal() + labs(y = "Beta", x = "ID", title = "Beta: Transmission Parameter")

```

Exposure dose, time, and volume were meant to be consistent across all treatments which means that Beta should end up as a function of the probability of infection. As expected, the patterns in Beta and probabilities of infection match well.

```{r}
prevalence <- readRDS(here("processed_data", "prevalence.rds"))
```

```{r}
prevalence %>% filter(temp %in% const_temp & species =="D") %>%
  ggplot(.,aes(x=ID, y = prev, group = temp, color = temp))  +
  geom_point(aes(), position = position_dodge(width = 0.5)) + 
  geom_errorbar(aes(ymin = conf$lower, ymax = conf$upper), position = position_dodge(width = 0.5)) +
  theme_minimal() + labs(title = "Probability of Infection")
```


```{r}
path <- here("figures", "prob_inf.png")
```


![](`r path`)

