---
title: "u_f_fits"
output: html_document
date: "`r Sys.Date()`"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))

library(ggnewscale)
```


# Notes

 - this version uses the best fitting f and tries to estiamte u under different formulations
 - each version should use the same u formulation from model 6c which is the full model with an exponential interaction term for the effect of temperature on the resource effect

# Read data and set global params

```{r}
fitness <- read.csv(here("raw_data/main_fitness_edit.csv")) #must be read.csv
fitness %<>% dplyr::select(tube, temp_id, REMOVED, KBP, final_date)
mort <-  read_csv(here("raw_data/main_mort_edit.csv"))
lengths <- read_csv(here("raw_data", "day5_length.csv")) #from life table
lengths %<>% filter(temp_id %in% c(15,20,25))


dataset <- left_join(mort,fitness) #life table data

data <- readRDS(here("processed_data","foraging_raw.rds")) #foraging rate assay
data_summ <- readRDS(here("processed_data", "foraging.rds")) #foraging rate assay summary

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


fora_vol <- 15 #mL
life_vol <- 50 #mL
spore_conc <- 200 #spores/mL
gamma <- 2 
ref_t <- 15 #celsius

```

Dataset are the data from the life table experiment
Requires a bit of cleaning
```{r}
dataset %<>% filter(species == "D") %>% #only daphnia for this analysis
  filter(temp %in% const_temp) #only constant temp for this analysis

dataset %<>% mutate(birthdate = ifelse(species == "daphnia", "4/5/22", "4/6/22"), 
                    lifespan = as.numeric(mdy(final_date) - mdy(birthdate)),
                    temp = as.numeric(temp),
                    treatment = paste(temp, resource, sep = "_")) %>% 
  filter(is.na(male)) %>% #remove males
  filter(is.na(missing)) %>% #remove missing
  filter(!is.na(inf)) #remove NAs for inf for estimating beta. sometimes they died too young to tell

dataset %<>% mutate(inf_status = inf, dead = ifelse(is.na(REMOVED) & is.na(KBP), 1, 0))


dataset %<>% mutate(spore_exposure = 200, #spores/mL
                    uninf = 1-inf_status,
                    time = 1, #duration of exposure in days
                    trt = paste(temp, resource, species, sep = "_"))
```

We use average lengths later on. We need to use averages because we weren't able to measure length for every individual.
For the foraging rate assay, these are the actual lengths because we measured the length of each individual at the end of the assay.

For the life table data, these are the lengths of a representative number of individuals right before the rest were exposed to spores. We take an average for these lengths since we didn't have length data for every individual.

```{r}
lengths %<>% mutate(mm = raw_meas*17.86/1000)
#at default magnification (5.6x), 1 unit is equal to 17.86 micron

length_summ <- lengths %>% 
  group_by(temp_id, resource) %>% 
  summarize(life_mm = mean(mm),
            var = var(mm),
            sd = sd(mm),
            se = sd(mm)/sqrt(n())) %>%
  ungroup() %>%
  dplyr::select(temp_id, resource, life_mm)

length_summ %<>% add_row(temp_id=as.character(25), resource=as.numeric(0.5), life_mm=1.16) #midpoint between 1.0 and 0.1
```

Join length data to both dataframes
Some of the length data from the foraging rate assay are missing so we impute these values from the averages from the data we do have.
We were also missing length data for one treatment from the life table so we use the foraging rate data lengths to replace those as well.

```{r}
dataset %<>% left_join(length_summ)

length_summ %<>% mutate(ID = paste(temp_id, resource, sep="_")) %>% dplyr::select(-c(temp_id, resource))


mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))

mean_length_summ %<>% rename(fora_mm = "mm_mean")
dataset %<>% left_join(., mean_length_summ)
```


```{r}
m6c_quantiles <- readRDS(file = here("mle", "m6c_quantiles.rds"))

f_est <- m6c_quantiles$f[1]
f_lower <- m6c_quantiles$f[3]
f_upper <- m6c_quantiles$f[4]

arr_f_est <- m6c_quantiles$arr[1]
arr_f_lower <- m6c_quantiles$arr[3]
arr_f_upper <- m6c_quantiles$arr[4]

h_est <- m6c_quantiles$h[1]
h_lower <- m6c_quantiles$h[3]
h_upper <- m6c_quantiles$h[4]

w_est <- m6c_quantiles$w[1]
w_lower <- m6c_quantiles$w[3]
w_upper <- m6c_quantiles$w[4]
```



# Independent Model

This model assumes constant f and constant u for all treatments

$$
\frac{dR}{dt} = -L^{\gamma} fRS\\
$$

We end up using this system of equations for everything and modify it by modifying how parameters are written out in the solver chunk.

```{r}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  with(as.list(params),{
    dR <- -f*R*(S+I)
    dS <- -u*f*Z*S
    dI <- u*f*Z*S
    dZ <- -f*Z*(S+I)
    res <- c(dR, dS, dI, dZ)
    list(res)}
    )
}
```

```{r}
m1_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u)
  
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r, m1_ll}
m1_ll <- function(f, u, arr_t_f, h, w){

  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_t_f,
                                h = (h + exp_data$temp*w)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  print(f)
  print(u)
  
  return(nll_sum)
}
```


```{r, eval=F}
start_time <- Sys.time()
tmp <- data
m1_u_fit <- mle2(m1_ll, start=list(u = 0.001, 
                                   f=f_est, 
                                   arr_t_f=arr_f_est,
                                   h=h_est,
                                   w=w_est), 
                     control=list(parscale = c(u = 0.001, 
                                               f=f_est, 
                                               arr_t_f=arr_f_est,
                                               h=h_est,
                                               w=w_est)),
                     skip.hessian=F, method="L-BFGS-B", 
                 lower=c(u = 0, 
                         f = f_lower,
                         arr_t_f = arr_f_lower,
                         h = h_lower,
                         w = w_lower), 
                 upper=c(u = 1, 
                         f = f_upper,
                         arr_t_f = arr_f_upper,
                         h = h_upper,
                         w = w_upper))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_u_fit)

saveRDS(m1_u_fit, file = here("mle","susc","m1_u_fit.rds"))
```

Always results in convergence failure

```{r, m1_ll}
m1_ll <- function(u){

  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m1_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f_est/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                h = (h_est + exp_data$temp*w_est)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  # print(u)
  
  return(nll_sum)
}
```


```{r, eval=F}
start_time <- Sys.time()
tmp <- data
m1_u_fit <- mle2(m1_ll, start=list(u = 0.0001), 
                     control=list(parscale = c(u = 0.0001)),
                     skip.hessian=F, method="L-BFGS-B", 
                 lower=c(u = 0), 
                 upper=c(u = 1))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_u_fit)

saveRDS(m1_u_fit, file = here("mle","susc","m1_u_fit.rds"))
```




# Temperature-Dependent Model

This model includes an Arrhenius function to modify f and u separately as a function of temperature.


$$
\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\\  
$$


```{r}
m2_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m2_ll <- function(u, arr_t_u){

  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m2_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f_est/life_vol, 
                                u=u, 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = arr_t_u,
                                h = (h_est + exp_data$temp*w_est)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  # print(u)
  # print(arr_t_u)
  
  return(nll_sum)
}
```


```{r, eval=F}
start_time <- Sys.time()
tmp <- data
m2_u_fit <- mle2(m2_ll, start=list(u = 0.0001,
                                   arr_t_u = 10), 
                     control=list(parscale = c(u = 0.0001,
                                   arr_t_u = 10)),
                     skip.hessian=F, method="L-BFGS-B", 
                 lower=c(u = 0, arr_t_u = 0), 
                 upper=c(u = 1, arr_t_u = Inf))
end_time <- Sys.time()
m2_runtime <- end_time - start_time
m2_runtime

coef(m2_u_fit)

saveRDS(m2_u_fit, file = here("mle","susc","m2_u_fit.rds"))
```


# Resource-dependent Model

u per resource and u with exponential function for resource

u per resource treatment

```{r}
m3_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m3u_ll <- function(u_low, u_med, u_high){

  
  nll_sum <- 0  
  u_nll <- 0
  u_vec <- c(f, u_low, u_med, u_high)
  for(j in 1:length(resource_IDs)){  
    
      exp_data <- dataset %>% filter(exposed==TRUE)
      exp_data %<>% filter(treatment == treatment_IDs[j])
      
      
      I_end <- as.data.frame(mapply(m3_sim, 
                                    R=exp_data$resource*life_vol/1000, 
                                    time=exp_data$time, 
                                    f=f_est/life_vol, 
                                    u=u_vec[j], 
                                    length = exp_data$life_mm, 
                                    gamma=gamma, 
                                    Z=spore_conc*life_vol,
                                    ref_t = ref_t,
                                    arr_t_f = arr_f_est,
                                    h = (h_est + exp_data$temp*w_est)*life_vol,
                                    temp=exp_data$temp))
    
      colnames(I_end) <- "I_end"
      
      exp_data %<>% cbind(I_end)
      
        inf_out <- function(inf_status, I_end){
        dbinom(x = inf_status, size = 1, prob=I_end, log=T)
        }
        
      exp_data %<>% 
        mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
      u_nll <- u_nll + -sum(exp_data$ll)
  }
  
  print(paste(u_low, u_med, u_high, sep ="_"))  

  nll_sum <- nll_sum + u_nll
  return(nll_sum)
}
```


Now we use the optimizer
```{r, eval=F}
start_time <- Sys.time()
tmp <- data

u_vec <- c(0.0001,#pass
           0.0001,#pass
           0.0001)#not working

m3_u_per_fit <- mle2(m3u_ll, start=list(u_low = u_vec[1],
                                       u_med = u_vec[2],
                                       u_high = u_vec[3]), 
                     control=list(parscale = c(u_low = u_vec[1],
                                       u_med = u_vec[2],
                                       u_high = u_vec[3])),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u_low = 0,
                           u_med = 0,
                           u_high = 0), 
                   upper=c(u_low = 1,
                           u_med = 1,
                           u_high = 1))
end_time <- Sys.time()
m3u_runtime <- end_time - start_time
m3u_runtime

coef(m3_u_per_fit)

saveRDS(m3_u_per_fit, file = here("mle","susc","m3_u_per_fit.rds"))
```




```{r}
m3_rho_ll <- function(u, rho){

  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m3_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f_est/life_vol, 
                                u=u*exp(exp_data$resource*rho), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                h = (h_est + exp_data$temp*w_est)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  print(u)
  print(rho)
  
  return(nll_sum)
}
```


```{r, eval=F}
start_time <- Sys.time()
tmp <- data
m3_u_exp_fit <- mle2(m3_rho_ll, start=list(u = 0.0001,
                                   rho = 0.001), 
                     control=list(parscale = c(u = 0.0001,
                                   rho = 0.001)),
                     skip.hessian=F, method="L-BFGS-B", 
                 lower=c(u = 0, rho = -Inf), 
                 upper=c(u = 1, rho = Inf))
end_time <- Sys.time()
m3_runtime <- end_time - start_time
m3_runtime

coef(m3_u_exp_fit)

saveRDS(m3_u_exp_fit, file = here("mle","susc","m3_u_exp_fit.rds"))
```


# Full Model

This version uses an arrhenius function for both f and u and a handling time function for f only.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{1 + fe^{T_{A}(1/T_{R}-1/T)}hL^{\gamma}R} S \\
$$

```{r}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m4_ll <- function(u, arr_t_u, rho){

  exp_data <- dataset %>% filter(exposed==TRUE)

  
  I_end <- as.data.frame(mapply(m4_sim, 
                                R=exp_data$resource*life_vol/1000, 
                                time=exp_data$time, 
                                f=f_est/life_vol, 
                                u=u*exp(exp_data$resource*rho), 
                                length = exp_data$life_mm, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = arr_t_u,
                                h = (h_est + exp_data$temp*w_est)*life_vol,
                                temp=exp_data$temp))

  colnames(I_end) <- "I_end"
  
  exp_data %<>% cbind(I_end)
  
    inf_out <- function(inf_status, I_end){
    dbinom(x = inf_status, size = 1, prob=I_end, log=T)
  }
  
  exp_data %<>% 
    mutate(ll = mapply(inf_out, inf_status = inf_status, I_end=I_end))
  nll_sum <- -sum(exp_data$ll)
  
  print(u)
  print(arr_t_u)
  print(rho)
  
  return(nll_sum)
}
```




```{r, eval=F}
start_time <- Sys.time()
tmp <- data
m4_u_fit <- mle2(m4_ll, start=list(u = 0.0001, 
                                     arr_t_u=10, 
                                     rho=0.01), 
                     control=list(parscale = c(u = 0.0001, 
                                     arr_t_u=10, 
                                     rho=0.01)),
                     skip.hessian=F, method="L-BFGS-B", 
                   lower=c(u = 0, 
                           arr_t_f = 0, 
                           rho = -Inf), 
                   upper=c(u = Inf, 
                           arr_t_f = Inf, 
                           rho = Inf))
end_time <- Sys.time()
m4_runtime <- end_time - start_time
m4_runtime

coef(m4_u_fit)

saveRDS(m4_u_fit, file = here("mle","susc","m4_u_rho_fit.rds"))
```






# Model 5 - Resource on temperature interaction

Same as model 4 but we include a linear interaction term for the arrhenius coefficient, thus representing the interactive effect of resources on the temperature effect



# Model 6 - Temperature on Resource interaction

Same as model 4 with a linear interaction for how handling time is affected by temperature, thus incoporating an interactive effect of temperature on the resource effect.



# Model 7 - Full interaction

Full interaction model where both temperature and resources effects are functions of each other.

Model 7a is linear interaction terms


```{r}
m1_u_fit <- readRDS(file = here("mle", "susc", "m1_u_fit.rds"))
m2_u_fit <- readRDS(file = here("mle", "susc", "m2_u_fit.rds"))
m3_u_per_fit <- readRDS(file = here("mle", "susc", "m3_u_per_fit.rds"))
m3_u_exp_fit <- readRDS(file = here("mle", "susc", "m3_u_exp_fit.rds"))
m4_u_fit <- readRDS(file = here("mle", "susc", "m4_u_rho_fit.rds"))
```


```{r}
getAIC <- function(model){
  return(2*length(coef(model))-(2*summary(model)@m2logL/-2))
}
```

```{r}
getAIC(m1_u_fit)
getAIC(m2_u_fit)
getAIC(m3_u_per_fit)
getAIC(m3_u_exp_fit)
getAIC(m4_u_fit)
```

















```{r}
fora_summ <- data %>% 
  mutate(ID = treatment_ID) %>%
  group_by(ID) %>% 
  summarize(end_r_mean = mean(amt_rem)*fora_vol/1000,
            end_r_se = (sd(amt_rem)/sqrt(n()))*fora_vol/1000)

prevalence <- readRDS(here("processed_data", "prevalence.rds"))
prevalence %<>% filter(temp %in% c(15, 20, 25)) %>% filter(species=="D") %>% mutate(ID = paste(temp, resource, sep="_")) %>% dplyr::select(-c(temp, resource, species))


viz_summ <- left_join(fora_summ, prevalence)
viz_summ %<>% left_join(., data_summ)
viz_summ %<>% left_join(., length_summ)
```

```{r}
m1_coef <- coef(m1_u_f_fit)
m1_f <- as.numeric(m1_coef[1])
m1_u <- as.numeric(m1_coef[2])

data_summ %<>% mutate(m1_rate = m1_f,
                      m1_u = m1_u,
                      m1_beta = m1_rate*m1_u)
```


```{r}
m2_coef <- coef(m2_u_f_fit)
m2_f <- as.numeric(m2_coef[1])
m2_u <- as.numeric(m2_coef[2])
m2_arr <- as.numeric(m2_coef[3])
m2_arr_u <- as.numeric(m2_coef[4])

data_summ %<>% mutate(m2_rate = (mm_mean^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)),
                      m2_u = m2_u*exp(m2_arr_u*(1/ref_t - 1/temp)),
                      m2_beta = m2_rate*m2_u)
```


```{r}
m3_coef <- coef(m3_u_f_fit)
m3_f <- as.numeric(m3_coef[1])
m3_u <- as.numeric(m3_coef[2])
m3_h <- as.numeric(m3_coef[3])

data_summ %<>% mutate(m3_rate = m3_f*(mm_mean^gamma)/(1+m3_f*(mm_mean^gamma)*m3_h*resource*fora_vol/1000),
                      m3_u = m3_u,
                      m3_beta = m3_rate*m3_u)
```


```{r}
m4_coef <- coef(m4_u_f_fit)
m4_f <- as.numeric(m4_coef[1])
m4_u <- as.numeric(m4_coef[2])
m4_arr <- as.numeric(m4_coef[3])
m4_arr_u <- as.numeric(m4_coef[4])
m4_h <- as.numeric(m4_coef[5])

data_summ %<>% mutate(m4_rate = (m4_f*exp(m4_arr*(1/ref_t - 1/temp))*(mm_mean^gamma))/(1+m4_f*exp(m4_arr*(1/ref_t - 1/temp))*(mm_mean^gamma)*m4_h*resource*fora_vol/1000),
                      m4_u = m4_u*exp(m4_arr_u*(1/ref_t - 1/temp)),
                      m4_beta = m4_rate*m4_u)
```


```{r}
data_summ %<>% mutate(rate_mean_ml_day=rate_len_mean*60*24,
                      rate_se_ml_day=rate_len_mean_se*60*24)
```



```{r}
viz_summ %<>% mutate(m1_I_end = mapply(m1_sim, R=resource*fora_vol/1000, 
                                       time=1, f=m1_f/life_vol,
                                 u = 0, 
                                 length=life_mm, gamma=gamma, Z=200*life_vol))
```


```{r}
viz_summ %<>% mutate(m1_I_end = mapply(m1_sim, 
                                       R=viz_summ$resource*fora_vol/1000, 
                                       time=1, 
                                       f=m1_f/life_vol, 
                                       u = m1_u, 
                                       length=viz_summ$life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol))

```

```{r}
viz_summ %<>% mutate(m2_I_end = mapply(m2_sim, R=resource*fora_vol/1000, 
                                       time=1, f=m1_f/life_vol,
                                       u = m2_u, 
                                       length=life_mm, gamma=gamma, Z=200*life_vol,
                                       arr_t_f = m2_arr, 
                                       arr_t_u = m2_arr_u,
                                       ref_t = ref_t,
                                       temp = temp))

```


```{r}
viz_summ %<>% mutate(m3_I_end = mapply(m3_sim, 
                                       R=resource*fora_vol/1000, 
                                       time=1, 
                                       f=m3_f/life_vol, 
                                       u = m3_u, 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       h = m3_h))
```

```{r}
viz_summ %<>% mutate(m4_I_end = mapply(m4_sim, 
                                       R=resource*fora_vol/1000, 
                                       time=1, 
                                       f=m4_f/life_vol, 
                                       u = m4_u, 
                                       length=life_mm, 
                                       gamma=gamma, 
                                       Z=200*life_vol,
                                       ref_t = ref_t,
                                       arr_t_f = m4_arr,
                                       arr_t_u = m4_arr_u,
                                       h = m4_h,
                                       temp = temp))
```

```{r}
viz_summ %>% ggplot(.,aes(x=resource, y=m1_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="independent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m2_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="temperature-dependent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m3_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="resource-dependent model")

viz_summ %>% ggplot(.,aes(x=resource, y=m4_I_end, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=prev, color=as.factor(temp)), size=4) + labs(title="full model")


```

```{r}
data_summ %>% ggplot(.,aes(x=resource, y=m1_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="independent model")

data_summ %>% ggplot(.,aes(x=resource, y=m2_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="temperature-dependent model")

data_summ %>% ggplot(.,aes(x=resource, y=m3_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="resource_dependent model")

data_summ %>% ggplot(.,aes(x=resource, y=m4_rate, color=as.factor(temp))) + geom_point(size = 3, shape=2) +
  new_scale_color() + geom_point(aes(x=resource, y=rate_mean_ml_day, color=as.factor(temp)), size=4) + labs(title="full model")

```
```{r, eval=F}
data_summ %>% ggplot(.,aes(x=resource, y=m1_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m2_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m3_u, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m4_u, color=as.factor(temp))) + geom_point()
```



```{r, eval=F}
data_summ %>% ggplot(.,aes(x=resource, y=m1_beta, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m2_beta, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m3_beta, color=as.factor(temp))) + geom_point()
data_summ %>% ggplot(.,aes(x=resource, y=m4_beta, color=as.factor(temp))) + geom_point()

```




