---
title: "susceptibility visualized"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))
library(ggnewscale)
```

# Read data and set global params

```{r}
fitness <- read.csv(here("raw_data/main_fitness_edit.csv")) #must be read.csv
fitness %<>% dplyr::select(tube, temp_id, REMOVED, KBP, final_date)
mort <-  read_csv(here("raw_data/main_mort_edit.csv"))
lengths <- read_csv(here("raw_data", "day5_length.csv")) #from life table
lengths %<>% filter(temp_id %in% c(15,20,25))


dataset <- left_join(mort,fitness) #life table data

data <- readRDS(here("processed_data","foraging_raw.rds")) #foraging rate assay
data_summ <- readRDS(here("processed_data", "foraging.rds")) #foraging rate assay summary

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


fora_vol <- 15 #mL
life_vol <- 50 #mL
spore_conc <- 200 #spores/mL
gamma <- 2 
ref_t <- 15 #celsius

```

Dataset are the data from the life table experiment
Requires a bit of cleaning
```{r}
dataset %<>% filter(species == "D") %>% #only daphnia for this analysis
  filter(temp %in% const_temp) #only constant temp for this analysis

dataset %<>% mutate(birthdate = ifelse(species == "daphnia", "4/5/22", "4/6/22"), 
                    lifespan = as.numeric(mdy(final_date) - mdy(birthdate)),
                    temp = as.numeric(temp),
                    treatment = paste(temp, resource, sep = "_")) %>% 
  filter(is.na(male)) %>% #remove males
  filter(is.na(missing)) %>% #remove missing
  filter(!is.na(inf)) #remove NAs for inf for estimating beta. sometimes they died too young to tell

dataset %<>% mutate(inf_status = inf, dead = ifelse(is.na(REMOVED) & is.na(KBP), 1, 0))


dataset %<>% mutate(spore_exposure = 200, #spores/mL
                    uninf = 1-inf_status,
                    time = 1, #duration of exposure in days
                    trt = paste(temp, resource, species, sep = "_"))
```

We use average lengths later on. We need to use averages because we weren't able to measure length for every individual.
For the foraging rate assay, these are the actual lengths because we measured the length of each individual at the end of the assay.

For the life table data, these are the lengths of a representative number of individuals right before the rest were exposed to spores. We take an average for these lengths since we didn't have length data for every individual.

```{r}
lengths %<>% mutate(mm = raw_meas*17.86/1000)
#at default magnification (5.6x), 1 unit is equal to 17.86 micron

length_summ <- lengths %>% 
  group_by(temp_id, resource) %>% 
  summarize(life_mm = mean(mm),
            var = var(mm),
            sd = sd(mm),
            se = sd(mm)/sqrt(n())) %>%
  ungroup() %>%
  dplyr::select(temp_id, resource, life_mm)

length_summ %<>% add_row(temp_id=as.character(25), resource=as.numeric(0.5), life_mm=1.16) #midpoint between 1.0 and 0.1
```

Join length data to both dataframes
Some of the length data from the foraging rate assay are missing so we impute these values from the averages from the data we do have.
We were also missing length data for one treatment from the life table so we use the foraging rate data lengths to replace those as well.

```{r}
dataset %<>% left_join(length_summ)

length_summ %<>% mutate(ID = paste(temp_id, resource, sep="_")) %>% dplyr::select(-c(temp_id, resource))


mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))

mean_length_summ %<>% rename(fora_mm = "mm_mean")
dataset %<>% left_join(., mean_length_summ)
```

```{r}
m6c <- readRDS(here("mle","m6c_f_fit.rds")) # EXP-EXP

m6c_coef <- coef(m6c)

f_est <- m6c_coef[1]
arr_f_est <- m6c_coef[2]
h_est <- m6c_coef[3]
w_est <- m6c_coef[4]
```


```{r}
m1_u_fit <- readRDS(file = here("mle", "susc", "m1_u_fit.rds"))
m2_u_fit <- readRDS(file = here("mle", "susc", "m2_u_fit.rds"))
m3_u_per_fit <- readRDS(file = here("mle", "susc", "m3_u_per_fit.rds"))
m3_u_exp_fit <- readRDS(file = here("mle", "susc", "m3_u_exp_fit.rds"))
m4_u_fit <- readRDS(file = here("mle", "susc", "m4_u_rho_fit.rds"))
# m5a_u_fit <- readRDS(file = here("mle", "susc", "m5a_u_rho_fit.rds"))
# m5b_u_fit <- readRDS(file = here("mle", "susc", "m5b_u_rho_fit.rds"))
m5u_per_fit <- readRDS(file = here("mle", "susc", "m5u_per_fit.rds"))
```


```{r}
getAIC <- function(model){
  return(2*length(coef(model))-(2*summary(model)@m2logL/-2))
}
```

```{r}
getAIC(m1_u_fit)
getAIC(m2_u_fit)
getAIC(m3_u_per_fit)
getAIC(m3_u_exp_fit)
getAIC(m4_u_fit)
# getAIC(m5a_u_fit)
# getAIC(m5b_u_fit)
getAIC(m5u_per_fit)
```

```{r}
m1_aic <- getAIC(m1_u_fit)
m2_aic <- getAIC(m2_u_fit)
m3_aic <- getAIC(m3_u_exp_fit)
m4_aic <- getAIC(m4_u_fit)
```



```{r}
getAIC(m6c)
getAIC(m6c) + getAIC(m2_u_fit)
```



```{r}
gamma <- 2
ref_t <- 15
vol <- 15
mean_time <- mean(data_summ$time_mean)
mean_length <- mean(data_summ$mm_mean, na.rm=T)
```


```{r}
fora_summ <- data %>% 
  mutate(ID = treatment_ID) %>%
  group_by(ID) %>% 
  summarize(end_r_mean = mean(amt_rem)*fora_vol/1000,
            end_r_se = (sd(amt_rem)/sqrt(n()))*fora_vol/1000)

prevalence <- readRDS(here("processed_data", "prevalence.rds"))
prevalence %<>% filter(temp %in% c(15, 20, 25)) %>% filter(species=="D") %>% mutate(ID = paste(temp, resource, sep="_")) %>% dplyr::select(-c(species))

prevalence %<>% mutate(temp = as.numeric(temp),
                       resource = as.numeric(as.character(resource)))

viz_summ <- left_join(fora_summ, prevalence)
viz_summ %<>% left_join(., data_summ)
viz_summ %<>% left_join(., length_summ)
```


```{r, units}
data_summ %<>% mutate(rate_len_mean = rate_len_mean*60*24,
                      rate_len_mean_se = rate_len_mean_se*60*24)
```


```{r}
temp_range <- seq(15,25,by=0.1)
resource_range <- seq(0.1,1,by=0.01)

seq_data <- tibble(temp=c(),
                   resourece=c())

for (i in 1:length(temp_range)){
  tmp <- tibble(temp = temp_range[i],
                resource = seq(0.1,1,by=0.01))
  seq_data %<>% bind_rows(., tmp)
}

```

```{r, echo=F}
seq_data %<>% mutate(temp_factor = as.factor(case_when(temp==25 ~ 25,
                                             temp==20 ~ 20,
                                             temp==15 ~ 15)))
```


```{r}
data_summ_se <- data_summ %>% dplyr::select(temp, resource, rate_len_mean, rate_len_mean_se)
seq_data %<>% left_join(., data_summ_se)
seq_data %<>% left_join(., prevalence)

```


```{r}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  S <- x[2]
  I <- x[3]
  Z <- x[4]
  with(as.list(params),{
    dR <- -f*R*(S+I)
    dS <- -u*f*Z*S
    dI <- u*f*Z*S
    dZ <- -f*Z*(S+I)
    res <- c(dR, dS, dI, dZ)
    list(res)}
    )
}
```

```{r}
m1_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u)
  
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m2_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m3_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```

```{r}
m4_sim <- function(R, time, f, u, length, gamma, Z, ref_t, arr_t_f, arr_t_u, h, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              S=1,
              I=0,
              Z=Z)
  params <- c(f=(f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma))/
                (1+f*exp(arr_t_f*(1/ref_t - 1/temp))*(length^gamma)*h*R),
              u=u*exp(arr_t_u*(1/ref_t - 1/temp)))
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  if(Z == 0) {
  end_data <- slice_max(output, time)[,2]
  }
  else {
  end_data <- slice_max(output, time)[,4]  
  }
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(end_data)
}
```





# plotting function

```{r}
seq_plot <- function(I_end){
  seq_data %>% filter(temp %in% c(15,20,25)) %>%
  ggplot(.) +
  geom_line(aes(x=resource, 
                y=!!sym(I_end),
                group=temp_factor,
                color=as.factor(temp_factor))) +
  geom_point(aes(x=resource, 
                  y=prev, 
                  group = as.factor(temp), 
                  color = as.factor(temp),
                  shape = as.factor(temp)),
             size=3) + 
    geom_linerange(aes(x=resource, 
                       ymin=conf$lower,
                       ymax=conf$upper,
                       color=as.factor(temp))) +
#    scale_color_manual(values = c("#FFC107", "#1E88E5", "#D81B60")) +
    scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  labs(x="Resource", y="Proportion\n Infected", color="Temperature", shape="Temperature", title = "") 
}

seq_plot_temp <- function(rate){
  seq_data %>% filter(resource %in% c(0.1, 0.5, 1)) %>%
  ggplot(.) +
  geom_line(aes(x=temp, 
                y=!!sym(rate),
                group=resource,
                color=as.factor(resource))) +
  geom_point(aes(x=temp, 
                  y=prev, 
                  group = as.factor(resource), 
                  color = as.factor(resource),
                  shape = as.factor(resource))) +
        geom_linerange(aes(x=temp, 
                       ymin=conf$lower,
                       ymax=conf$upper,
                       color=as.factor(resource))) + 
    scale_color_manual(values = c("#CABD88", "#CA5216", "#65320D")) +
  labs(x="Temperature", y="Proportion\n Infected", color="", shape="", title = "") 
}

```






# Fitting foraging rate

```{r}
data_summ %>% ggplot(., aes(x=as.factor(resource), y=rate_len_mean, color=as.factor(temp))) +
  geom_point(size=2) +
  geom_linerange(aes(ymin=rate_len_mean-rate_len_mean_se,
                     ymax=rate_len_mean+rate_len_mean_se)) +
  labs(x="Resource", y="Foraging rate (mL/min)", color="Temperature")
```

```{r}
f_mod <- f_est
h_mod <- h_est

data_summ %<>% mutate(clearance = 
                        (f_mod*exp(arr_f_est*(1/ref_t - 1/temp)))/
                        (1+f_est*exp(arr_f_est*(1/ref_t - 1/temp))*(h_mod*exp(w_est*temp))*resource/15))


```


```{r}
m1_coef <- coef(m1_u_fit)
m1_u <- as.numeric(m1_coef[1])

data_summ %<>% mutate(m1_u = m1_u)
```


```{r}
m2_coef <- coef(m2_u_fit)
m2_u <- as.numeric(m2_coef[1])
m2_arr_u <- as.numeric(m2_coef[2])

data_summ %<>% mutate(m2_u = m2_u*exp(m2_arr_u*(1/ref_t - 1/temp)))
```

```{r}
m3_per_coef <- coef(m3_u_per_fit)

m3_u_low <- as.numeric(m3_per_coef[1])
m3_u_med <- as.numeric(m3_per_coef[2])
m3_u_high <- as.numeric(m3_per_coef[3])

data_summ %<>% mutate(m3_u = case_when(resource==0.1 ~ m3_u_low,
                                       resource==0.5 ~ m3_u_med,
                                       resource==1 ~ m3_u_high,))
```

```{r}
m3_coef <- coef(m3_u_exp_fit)

m3_u <- as.numeric(m3_coef[1])
m3_rho <- as.numeric(m3_coef[2])

data_summ %<>% mutate(m3_u = m3_u*exp(m3_rho*resource))
```


```{r}
m4_coef <- coef(m4_u_fit)

m4_u <- as.numeric(m4_coef[1])
m4_arr_u <- as.numeric(m4_coef[2])
m4_rho <- as.numeric(m4_coef[3])

data_summ %<>% mutate(m4_u = m4_u*exp(m4_arr_u*(1/ref_t - 1/temp))*exp(m4_rho*resource))
```




```{r}
seq_data %<>% mutate(m1_I_end = mapply(m1_sim, 
                                R=resource*life_vol/1000, 
                                time=mean_time, 
                                f=f_est/life_vol, 
                                u=m1_u, 
                                length = mean_length, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                h = h_est*exp(temp*w_est),
                                temp=temp))

```

```{r}
seq_data %<>% mutate(m2_I_end = mapply(m2_sim, 
                                R=resource*life_vol/1000, 
                                time=mean_time, 
                                f=f_est/life_vol, 
                                u=m2_u, 
                                length = mean_length, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = m2_arr_u,
                                h = h_est*exp(temp*w_est),
                                temp=temp))

```


```{r}
seq_data %<>% mutate(m3_per_I_end = mapply(m3_sim, 
                                    R=resource*life_vol/1000, 
                                    time=mean_time, 
                                    f=f_est/life_vol, 
                                    u=case_when(resource==0.1 ~ m3_u_low,
                                                resource==0.5 ~ m3_u_med,
                                                resource==1 ~ m3_u_high), 
                                    length = mean_length, 
                                    gamma=gamma, 
                                    Z=spore_conc*life_vol,
                                    ref_t = ref_t,
                                    arr_t_f = arr_f_est,
                                    h = h_est*exp(temp*w_est),
                                    temp=temp))
```

```{r}
seq_data %<>% mutate(m3_I_end = mapply(m3_sim, 
                                    R=resource*life_vol/1000, 
                                    time=mean_time, 
                                    f=f_est/life_vol, 
                                    u=m3_u*exp(m3_rho*resource), 
                                    length = mean_length, 
                                    gamma=gamma, 
                                    Z=spore_conc*life_vol,
                                    ref_t = ref_t,
                                    arr_t_f = arr_f_est,
                                    h = h_est*exp(temp*w_est),
                                    temp=temp))
```


```{r}
seq_data %<>% mutate(m4_I_end = mapply(m4_sim, 
                                R=resource*life_vol/1000, 
                                time=mean_time, 
                                f=f_est/life_vol, 
                                u=m4_u*exp(resource*m4_rho), 
                                length = mean_length, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = m4_arr_u,
                                h = h_est*exp(temp*w_est),
                                temp=temp))
```


```{r}
viz_summ %<>% mutate(m1_I_end = mapply(m1_sim, 
                                R=resource*life_vol/1000, 
                                time=time_mean, 
                                f=f_est/life_vol, 
                                u=m1_u, 
                                length = mm_mean, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                h = h_est*exp(temp*w_est),
                                temp=temp))

```

```{r}
viz_summ %<>% mutate(m2_I_end = mapply(m2_sim, 
                                R=resource*life_vol/1000, 
                                time=time_mean, 
                                f=f_est/life_vol, 
                                u=m2_u, 
                                length = mm_mean, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = m2_arr_u,
                                h = h_est*exp(temp*w_est),
                                temp=temp))

```


```{r}
viz_summ %<>% mutate(m3_per_I_end = mapply(m3_sim, 
                                    R=resource*life_vol/1000, 
                                    time=time_mean, 
                                    f=f_est/life_vol, 
                                    u=case_when(resource==0.1 ~ m3_u_low,
                                                resource==0.5 ~ m3_u_med,
                                                resource==1 ~ m3_u_high), 
                                    length = mm_mean, 
                                    gamma=gamma, 
                                    Z=spore_conc*life_vol,
                                    ref_t = ref_t,
                                    arr_t_f = arr_f_est,
                                    h = h_est*exp(temp*w_est),
                                    temp=temp))
```

```{r}
viz_summ %<>% mutate(m3_I_end = mapply(m3_sim, 
                                    R=resource*life_vol/1000, 
                                    time=time_mean, 
                                    f=f_est/life_vol, 
                                    u=m3_u*exp(m3_rho*resource), 
                                    length = mm_mean, 
                                    gamma=gamma, 
                                    Z=spore_conc*life_vol,
                                    ref_t = ref_t,
                                    arr_t_f = arr_f_est,
                                    h = h_est*exp(temp*w_est),
                                    temp=temp))
```


```{r}
viz_summ %<>% mutate(m4_I_end = mapply(m4_sim, 
                                R=resource*life_vol/1000, 
                                time=time_mean, 
                                f=f_est/life_vol, 
                                u=m4_u*exp(resource*m4_rho), 
                                length = mm_mean, 
                                gamma=gamma, 
                                Z=spore_conc*life_vol,
                                ref_t = ref_t,
                                arr_t_f = arr_f_est,
                                arr_t_u = m4_arr_u,
                                h = h_est*exp(temp*w_est),
                                temp=temp))
```




```{r}
saveRDS(seq_data, file=here("u_fit.rds"))
```


```{r}
inf_data <- seq_data %>% filter(temp %in% c(15,20,25)) %>%
  ggplot(.) +
  geom_point(aes(x=resource, 
                  y=prev, 
                  group = as.factor(temp), 
                  color = as.factor(temp),
                  shape = as.factor(temp)),
             size=3) + 
    geom_linerange(aes(x=resource, 
                       ymin=conf$lower,
                       ymax=conf$upper,
                       color=as.factor(temp))) +
#    scale_color_manual(values = c("#FFC107", "#1E88E5", "#D81B60")) +
    scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) + 
  labs(x="Resource", y="Proportion\n Infected", color="Temperature", shape="Temperature", title = "Infection Assay") 

ggsave("inf_data.png", inf_data, path=here("mle/fit_plots"), width = 7.29, height = 4.51)

```



```{r}
m1_plot <- seq_plot("m1_I_end") + labs(title = paste("Size-dependent only. AIC =", round(m1_aic, 3)))
m2_plot <- seq_plot("m2_I_end") + labs(title = paste("Temperature-dependent. AIC =", round(m2_aic, 3)))
m3_plot <- seq_plot("m3_I_end") + labs(title = paste("Resource-dependent. AIC =", round(m3_aic, 3)))
m4_plot <- seq_plot("m4_I_end") + labs(title = paste("Full model. AIC =", round(m4_aic, 3)))

ggsave("m1_u_fit.png", m1_plot, path=here("mle/fit_plots"), width = 7.29, height = 4.51)
ggsave("m2_u_fit.png", m2_plot, path=here("mle/fit_plots"), width = 7.29, height = 4.51)
ggsave("m3_u_fit.png", m3_plot, path=here("mle/fit_plots"), width = 7.29, height = 4.51)
ggsave("m4_u_fit.png", m4_plot, path=here("mle/fit_plots"), width = 7.29, height = 4.51)

```



```{r}
m1_plot
m2_plot
m3_plot
m4_plot
```




heatmap of prevalence

```{r}
seq_data %>% ggplot(.,aes(x=resource, y=temp, fill=m2_I_end)) + geom_tile() + scale_fill_viridis_c()
```













