---
title: "bootstrap f"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))

library(doParallel)
```

Objective: Bootstrap confidence intervals for f and associated parameters for the best fitting model from the model comparison for estimating foraging rate across treatments

Which model is the best fitting model?
```{r}
readRDS(here("mle", "aic_table.rds"))
```

Model 6c is the best fitting model
This model includes both an arrhenius function for affecting temperature and assumes a type-ii functional response for resource concentration and also includes an exponential interactive function for the effects of temperature on the resource effect
```{r}
m6c <- readRDS(here("mle","m6c_f_fit.rds")) # EXP-EXP
```

In order to bootstrap confidence intervals around the estimate, we will resample with replacement from the data used to generate these estimates. We will do this many times (~1000) and measure quantiles of the data to understand the bounds in which 95% of the estimates lie.

read data
```{r}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


vol <- 15 #volume of tube from experiment in mL
```

Some of the lengths are missing so we impute these missing values by using the average length from that treatment
```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))
```


We want to subset the data randomly but we don't want to oversample from some treatments and undersample from other treatments.

This is just a test
```{r, eval=F}
data_boot <- data %>% 
  group_by(treatment_ID) %>%
  slice_sample(., prop=1, replace=T) %>%
  ungroup()

asdf <- data %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

jkl <- data_boot %>% group_by(treatment_ID) %>%
  summarize(mean = mean(amt_rem_tot),
            n = n())

asdf
jkl
```

slice_sample is set to keep the amount of data per treatment the same (30), but resamples from the data with replacement which causes the means to be different. It looks like it is working!





We use the same base solver function from the "full model" (model 4)
```{r}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/
              (1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


The negative log-likelihood function incorporates the interactive effects into the estimates for the arrhenius coefficient (arr_t) and handling time (h)

```{r}
m6c_ll <- function(f, arr_t, h, w){

  data <- tmp 
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, 
                                 h=h*data$vol*exp(w*data$temp)))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)

}
```


Finally, we use our optimizer to get the maximum likelihood estimate for all parameters
We'll include the bootstrapping here

```{r, 00}

  iterations <- 10
  
  m6c_f_boot_00 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_00[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=10, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 01}

  iterations <- 10
  
  m6c_f_boot_01 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_01[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 02}

  iterations <- 10
  
  m6c_f_boot_02 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_02[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 03}

  iterations <- 10
  
  m6c_f_boot_03 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_03[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 04}

  iterations <- 10
  
  m6c_f_boot_04 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_04[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```

```{r, 05}

  iterations <- 10
  
  m6c_f_boot_05 <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot_05[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=20, arr_t=30, h=15, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=20, arr_t=30, h=15, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)

```


262 iterations run by 4/8/24

60 iterations run later on 4/8/24

bind lists
```{r}
length(m6c_f_boot_00)
length(m6c_f_boot_01)
length(m6c_f_boot_02)
length(m6c_f_boot_03)
length(m6c_f_boot_04)
length(m6c_f_boot_05)

m6c_f_boot <- c(m6c_f_boot_00,
                m6c_f_boot_01,
                m6c_f_boot_02,
                m6c_f_boot_03,
                m6c_f_boot_04,
                m6c_f_boot_05)
```

Add to older iterations
```{r}
# m6c_f_boot_read <- readRDS(file = here("mle", "m6c_f_boot_full.rds"))
# m6c_f_boot <- c(m6c_f_boot, m6c_f_boot_read)
# 
# saveRDS(m6c_f_boot, file = here("mle", "m6c_f_boot_full.rds"))
```


```{r}
m6c_f_boot <- readRDS(file = here("mle", "m6c_f_boot_full.rds"))
```



```{r}
tib_length <- length(m6c_f_boot)

m6c_boot_coefs <- tibble(f = rep_len(0, tib_length),
                         arr = rep_len(0, tib_length),
                         h = rep_len(0, tib_length),
                         w = rep_len(0, tib_length))


for(i in 1:length(m6c_f_boot)){
  if(m6c_f_boot[[i]]@details[4] == 52){
    print(paste(i, "convergence_failure", sep="_"))
    m6c_boot_coefs$f[i] <- NA
    m6c_boot_coefs$arr[i] <- NA
    m6c_boot_coefs$h[i] <- NA
    m6c_boot_coefs$w[i] <- NA
  }
  else if(m6c_f_boot[[i]]@min == 0){
    print(paste(i, "zero_ll", sep="_"))
    m6c_boot_coefs$f[i] <- NA
    m6c_boot_coefs$arr[i] <- NA
    m6c_boot_coefs$h[i] <- NA
    m6c_boot_coefs$w[i] <- NA
  }
  else{
  boot_coef <- coef(m6c_f_boot[[i]])
  m6c_boot_coefs$f[i] <- as.numeric(boot_coef[1])
  m6c_boot_coefs$arr[i] <- as.numeric(boot_coef[2])
  m6c_boot_coefs$h[i] <- as.numeric(boot_coef[3])
  m6c_boot_coefs$w[i] <- as.numeric(boot_coef[4])
  }
}
```

```{r}
m6c_boot_coefs %<>% drop_na()

m6c_boot_coefs %>% ggplot(., aes(x = f)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = arr)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = h)) + geom_histogram()
m6c_boot_coefs %>% ggplot(., aes(x = w)) + geom_histogram()

```

quantiles
```{r}
m6c_quantiles <- tibble(id = c("est", "mean", "lower.025", "upper.975"),
                        f = NA,
                        arr = NA,
                        h = NA,
                        w = NA)

m6c_quantiles$f[1] <- coef(m6c)[1]
m6c_quantiles$f[2] <- mean(m6c_boot_coefs$f)
m6c_quantiles$f[3] <- quantile(m6c_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$f[4] <- quantile(m6c_boot_coefs$f, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$arr[1] <- coef(m6c)[2]
m6c_quantiles$arr[2] <- mean(m6c_boot_coefs$arr)
m6c_quantiles$arr[3] <- quantile(m6c_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$arr[4] <- quantile(m6c_boot_coefs$arr, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$h[1] <- coef(m6c)[3]
m6c_quantiles$h[2] <- mean(m6c_boot_coefs$h)
m6c_quantiles$h[3] <- quantile(m6c_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$h[4] <- quantile(m6c_boot_coefs$h, probs=seq(0.025, 0.975, 0.95))[2]

m6c_quantiles$w[1] <- coef(m6c)[4]
m6c_quantiles$w[2] <- mean(m6c_boot_coefs$w)
m6c_quantiles$w[3] <- quantile(m6c_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[1]
m6c_quantiles$w[4] <- quantile(m6c_boot_coefs$w, probs=seq(0.025, 0.975, 0.95))[2]
```

```{r}
saveRDS(m6c_quantiles, file = here("mle", "m6c_quantiles.rds"))
```



Everything below here is still being workshopped









```{r}
get_fits <- function(iters){
  
  iterations <- iters
  
  m6c_f_boot <- list()
  
  start_time <- Sys.time()
  for(i in 1:iterations){
      boot_data <- data %>% 
        group_by(treatment_ID) %>%
        slice_sample(., prop=1, replace=T) %>%
        ungroup()
        
      tmp <- boot_data

      m6c_f_boot[[i]] <- mle2(m6c_ll,
                            skip.hessian = T,
                            start=list(f=10, arr_t=50, h=1, w=0.1),
                            method = "L-BFGS-B",
                            lower = c(f=0, arr_t=0, h=0, w=-Inf),
                            upper = c(Inf, Inf, Inf, Inf),
                            control=list(parscale=c(f=10, arr_t=50, h=1, w=0.1), maxit=10000))
      print(i)
      end_time <- Sys.time()
      print(end_time-start_time)
  }
  end_time <- Sys.time()
  
  print(end_time-start_time)
  
  return(m6c_f_boot)
}
```


```{r}
asdf <- get_fits(3)
```



```{r}
m6c_fits_a <- get_fits(50)
saveRDS(m6c_fits_a, file = here("mle", "m6c_fits_a.rds"))

m6c_fits_b <- get_fits(50)
saveRDS(m6c_fits_b, file = here("mle", "m6c_fits_b.rds"))

m6c_fits_c <- get_fits(50)
saveRDS(m6c_fits_c, file = here("mle", "m6c_fits_c.rds"))

m6c_fits_d <- get_fits(50)
saveRDS(m6c_fits_d, file = here("mle", "m6c_fits_d.rds"))

m6c_fits_e <- get_fits(50)
saveRDS(m6c_fits_e, file = here("mle", "m6c_fits_e.rds"))

m6c_fits_f <- get_fits(50)
saveRDS(m6c_fits_f, file = here("mle", "m6c_fits_f.rds"))

m6c_fits_g <- get_fits(50)
saveRDS(m6c_fits_g, file = here("mle", "m6c_fits_g.rds"))

m6c_fits_h <- get_fits(50)
saveRDS(m6c_fits_h, file = here("mle", "m6c_fits_h.rds"))

m6c_fits_i <- get_fits(50)
saveRDS(m6c_fits_i, file = here("mle", "m6c_fits_i.rds"))

m6c_fits_j <- get_fits(50)
saveRDS(m6c_fits_j, file = here("mle", "m6c_fits_j.rds"))

```

```{r}
m6c_fits_1 <- get_fits(100)
saveRDS(m6c_fits_1, file = here("mle", "m6c_fits_1.rds"))

m6c_fits_2 <- get_fits(100)
saveRDS(m6c_fits_2, file = here("mle", "m6c_fits_2.rds"))

m6c_fits_3 <- get_fits(100)
saveRDS(m6c_fits_3, file = here("mle", "m6c_fits_3.rds"))

m6c_fits_4 <- get_fits(100)
saveRDS(m6c_fits_4, file = here("mle", "m6c_fits_4.rds"))

m6c_fits_5 <- get_fits(100)
saveRDS(m6c_fits_5, file = here("mle", "m6c_fits_5.rds"))

```


```{r}
head(m6c_fits_b)
```




```{r}
saveRDS(m6c_f_boot, file = here("mle","m6c_f_boot.rds"))
```

```{r}
saveRDS(m6c_fits_a, file = here("mle", "m6c_fits_a.rds"))
```





This should bootstrap the data. The only confusing part is that tmp must be declared before running the foreach loop. The results from the loop are all different so it appears to be reinitializing tmp within each loop but I'm not sure why it doesn't work without this being initialized first.
```{r}
registerDoParallel()
getDoParWorkers()

iterations <- 10

start_time <- Sys.time()

tmp <- data

m6c_f_boot_par <- foreach(1:iterations) %dopar% {

    tmp <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
    
      
    estimate <-mle2(m6c_ll,
                    skip.hessian = T,
                    start=list(f=10, arr_t=50, h=0.01, w=0.1),
                    method = "L-BFGS-B",
                    lower = c(f=0, arr_t=0, h=0, w=-Inf),
                    upper = c(Inf, Inf, Inf, Inf),
                    control=list(parscale=c(f=10, arr_t=50, h=0.01, w=0.1), maxit=10000))
    estimate
    

}
end_time <- Sys.time()

end_time-start_time
registerDoSEQ()

saveRDS(m6c_f_boot_par, file = here("mle","m6c_f_boot_par.rds"))
```



# Test
Parallelization does appear to make it faster

```{r, m0_num_sol}
m0_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -f*R
    res <- c(dR)
    list(res)}
    )
}

```



```{r, m0_sim}
m0_sim <- function(R, time, f){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f)
  output <- as.data.frame(lsoda(y=xstart, times, m0_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m0_ll}
m0_ll <- function(f){
  data <- tmp
  m0_end <- as.data.frame(mapply(m0_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol))
  colnames(m0_end) <- "m0_end"
  data$end <- m0_end$m0_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```



```{r}
get_m0_fits <- function(iters){

iterations <- iters

m0_f_fit_boot <- list()

start_time <- Sys.time()
for(i in 1:iterations){
    print(i)
    boot_data <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
      
    tmp <- boot_data
    
    m0_f_fit_boot[[i]] <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10),
                control=list(parscale=c(f=10), maxit=10000))

}
end_time <- Sys.time()

end_time-start_time
return(m0_f_fit_boot)
}


#saveRDS(m7c_f_fit, file = here("mle","m7c_f_boot.rds"))
```

```{r}
jkl <- get_m0_fits(5)
```




```{r}
registerDoParallel()
getDoParWorkers()

iterations <- 10

start_time <- Sys.time()

m0_f_boot_par_ <- foreach(1:iterations) %dopar% {
    
    tmp <- data %>% 
      group_by(treatment_ID) %>%
      slice_sample(., prop=1, replace=T) %>%
      ungroup()
    
    
    estimate <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10),
                control=list(parscale=c(f=10), maxit=10000))
    
    estimate
}


end_time <- Sys.time()

end_time-start_time
registerDoSEQ()

#saveRDS(m0_f_boot_par, file = here("mle","m0_f_boot_100.rds"))

```
