---
title: "interaction model parameters visualized"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))
library(ggnewscale)
library(patchwork)
```

# Note!!

This script needs to be fixed for the visualizations to account for h being changed for model 6c. h was fixed for this model so that it is not in units of per mL but that means that it does not align with everything else. Eventually, everything should be fixed so that it is not per mL for h but the get_rate function should be fixed so that the resource is per tube (i.e. divided by 15 because the tube was 1 tube/15mL...I think)



First, make basic plot that shows temperature gradient on x-axis, foraging rate on y-axis, and a geom layer for resource concentration. This will be the actual data and will be consistent between each of the model fit visualizations.

```{r, data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))
m0 <- readRDS(here("mle", "m0_f_fit.rds"))
m1 <- readRDS(here("mle", "m1_f_fit.rds"))


m2 <- readRDS(here("mle", "m2_f_fit.rds"))
m3 <- readRDS(here("mle", "m3_f_fit.rds"))

m4 <- readRDS(here("mle", "m4_f_fit.rds"))

m6c <- readRDS(here("mle", "m6c_f_fit.rds"))


```

```{r}
m0_coef <- m0@coef

m4_coef <- m4@coef


m6c_coef <- m6c@coef

gamma <- 2
ref_t <- 15
vol <- 15
mean_time <- mean(data$time/60/24)
```

```{r, units}
data_summ %<>% mutate(rate_len_mean = rate_len_mean*60*24,
                      rate_len_mean_se = rate_len_mean_se*60*24)

mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))
```


```{r}
temp_range <- seq(15,25,by=0.1)
resource_range <- seq(min(data$amt_init), max(data$amt_init),by=0.01)
resource_range <- append(resource_range, values = c(0.1, 0.5, 1))

seq_data <- tibble(temp=c(),
                   resourece=c())

for (i in 1:length(temp_range)){
  tmp <- tibble(temp = temp_range[i],
                resource = resource_range)
  seq_data %<>% bind_rows(., tmp)
}


```

```{r, echo=F}
seq_data %<>% mutate(temp_factor = as.factor(case_when(temp==25 ~ 25,
                                             temp==20 ~ 20,
                                             temp==15 ~ 15)))
```

```{r}
lm(mm ~ resource + temp, data = data)

length_coef <- coef(lm(mm ~ resource + temp, data = data))


interpolate_length <- function(resource, temp){
  length <- length_coef[1] + resource*length_coef[2] + temp*length_coef[3]
}

seq_data %<>% mutate(length = mapply(interpolate_length, 
                                     resource = resource,
                                     temp = temp))
```

```{r}
lm(amt_init ~ resource, data = data)

proj_res_coef <- coef(lm(amt_init ~ resource, data = data))

interpolate_resources <- function(resource){
  output <- proj_res_coef[1] + resource*proj_res_coef[2]
}

seq_data %<>% mutate(proj_res = mapply(interpolate_resources,
                                       resource = resource))
```




```{r}
data_summ_se <- data_summ %>% dplyr::select(temp, resource, rate_len_mean, rate_len_mean_se, amt_init_mean)
seq_data %<>% left_join(., data_summ_se)
```



# AIC

```{r}
getAIC <- function(model){
  return(2*length(coef(model))-(2*summary(model)@m2logL/-2))
}
```

Log-Likelihoods

```{r}
getAIC(m1)
getAIC(m2)
getAIC(m3)
getAIC(m4)
getAIC(m6c)
```






# Fitting foraging rate

```{r}
fora_data <- data_summ %>% ggplot(., aes(x=as.factor(resource), y=rate_len_mean, color=as.factor(temp))) +
  geom_point(size=2) +
  geom_linerange(aes(ymin=rate_len_mean-rate_len_mean_se,
                     ymax=rate_len_mean+rate_len_mean_se)) +
#    scale_color_manual(values = c("#FFC107", "#1E88E5", "#D81B60")) +
    scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) +
  labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", title="Foraging Rate Assay")

fora_data 

#ggsave("fora_data.png", fora_data, path=here("mle/fit_plots"))

```





Now let's get the results from the model
```{r}
m0_f <- as.numeric(m0_coef[1])
data_summ %<>% mutate(m0_rate = m0_f)
```


$$
observed\; f = \frac{fe^{T_{A}(1/T_{R}-1/T)}}{1 + fe^{T_{A}(1/T_{R}-1/T)}hR} \\
$$

```{r}
m1_coef <- coef(m1)
m1_f <- as.numeric(m1_coef[1])

data_summ %<>% mutate(m1_rate = mm_mean^gamma*m1_f)
seq_data %<>% mutate(m1_rate = length^gamma*m1_f)
```


```{r}
m2_coef <- coef(m2)
m2_f <- as.numeric(m2_coef[1])
m2_arr <- as.numeric(m2_coef[2])

data_summ %<>% mutate(m2_rate = (mm_mean^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
seq_data %<>% mutate(m2_rate = (length^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
```


```{r}
m3_coef <- coef(m3)
m3_f <- as.numeric(m3_coef[1])
m3_h <- as.numeric(m3_coef[2])

data_summ %<>% mutate(m3_rate = ((m3_f*mm_mean^gamma)/(1+m3_f*mm_mean^gamma*m3_h*resource/1000)))

seq_data %<>% mutate(m3_rate=((m3_f*length^gamma)/(1+m3_f*length^gamma*m3_h*resource/1000)))
```



```{r}
get_rate <- function(f, arr, temp, h, resource, length){
  ((f*length^gamma*exp(arr*(1/ref_t - 1/temp)))/
     (1+f*length^gamma*exp(arr*(1/ref_t - 1/temp))*h*resource))
}
```



```{r}
m4_coef
m4_f <- as.numeric(m4_coef[1])
m4_arr <- as.numeric(m4_coef[2])
m4_h <- as.numeric(m4_coef[3])

data_summ %<>% mutate(m4_rate = mapply(get_rate, f=m4_f, arr=m4_arr, temp=data_summ$temp, h=m4_h, resource=data_summ$resource/1000, length = mm_mean))

seq_data %<>% mutate(m4_rate = mapply(get_rate, f=m4_f, arr=m4_arr, temp=seq_data$temp, h=m4_h, resource=seq_data$resource/1000, length = length))
```





```{r}
m6c_coef
m6c_f <- as.numeric(m6c_coef[1])
m6c_arr <- as.numeric(m6c_coef[2])
m6c_h <- as.numeric(m6c_coef[3])
m6c_w <- as.numeric(m6c_coef[4])

  data_summ %<>% mutate(m6c_rate = mapply(get_rate, f=m6c_f, arr=m6c_arr, h=m6c_h*exp(m6c_w*data_summ$temp), temp=data_summ$temp, resource=data_summ$resource/1000, length = mm_mean))
  seq_data %<>% mutate(m6c_rate = mapply(get_rate, f=m6c_f, arr=m6c_arr, h=m6c_h*exp(m6c_w*seq_data$temp), temp=seq_data$temp, resource=seq_data$resource/1000, length = length))
```






# Interaction parameters



```{r}
m6_range <- tibble(temp = temp_range)

m6_range %<>% mutate(h = m4_h,
                     h_c = (m6c_h*exp(m6c_w*temp)))

h_plot <- m6_range %>% ggplot(., aes(x=temp, y=h_c)) + 
  geom_line(size=2) +
  scale_x_continuous(breaks = c(15, 20, 25)) +
  scale_y_continuous(breaks = c(200, 400, 600, 800)) + 
  labs(x = "Temperature (C)", y = "Handling time (days/mgC)", title = "")

#ggsave("h_plot.png", h_plot, path=here("workshop","figures"))


```



# Final Resource Concentration

```{r, m1_num_sol}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*R
    res <- c(dR)
    list(res)}
    )
}

```

```{r, m1_sim}
m1_sim <- function(R, time, f, length, gamma){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  

  return(r_end)
}
```


```{r, m2_num_sol}
m2_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*R
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m2_sim}
m2_sim <- function(R, time, f, length, gamma, ref_t, arr_t, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp)
  output <- as.data.frame(lsoda(y=xstart, times, m2_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  

  return(r_end)
}
```


```{r, m3_num_sol}
m3_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(1+f*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```


```{r, m3_sim}
m3_sim <- function(R, time, f, length, gamma, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m3_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  

  return(r_end)
}
```



```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  

  return(r_end)
}
```




```{r}
seq_data %<>% mutate(m1_R_end = mapply(m1_sim,
                                       R = resource*vol/1000,
                                       time = mean_time,
                                       f=m1_f/vol,
                                       length = length,
                                       gamma = 2))
```

```{r}
seq_data %<>% mutate(m2_R_end = mapply(m2_sim,
                                       R = resource*vol/1000,
                                       time = mean_time,
                                       f=m2_f/vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m2_arr,
                                       temp = temp))
```

```{r}
seq_data %<>% mutate(m3_R_end = mapply(m3_sim,
                                       R = resource*vol/1000,
                                       time = mean_time,
                                       f=m3_f/vol,
                                       length = length,
                                       gamma = 2,
                                       h = m3_h))
```

```{r}
seq_data %<>% mutate(m4_R_end = mapply(m4_sim,
                                       R = resource*vol/1000,
                                       time = mean_time,
                                       f=m4_f/vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m4_arr,
                                       temp = temp,
                                       h = m4_h))
```

```{r}
seq_data %<>% mutate(m6c_R_end = mapply(m4_sim,
                                       R = resource*vol/1000,
                                       time = mean_time,
                                       f=m6c_f/vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m6c_arr,
                                       temp = temp,
                                       h = m6c_h*exp(m6c_w*temp)))
```


```{r}
r_end_mean <- 
  data %>% 
  mutate(amt_consumed_theor = resource-amt_rem) %>% 
  group_by(temp, resource) %>% 
  summarize(amt_rem_mean = mean(amt_rem),
            amt_rem_se = sd(amt_rem)/sqrt(n()),
            amt_consumed_mean = mean(amt_consumed),
            amt_consumed_se = sd(amt_consumed)/sqrt(n()),
            amt_consumed_mean_theor = mean(amt_consumed_theor),
            amt_consumed_se_theor = sd(amt_consumed_theor)/sqrt(n())) %>%
  ungroup()
```

```{r}
seq_data %<>% left_join(., r_end_mean)
data_summ %<>% left_join(., r_end_mean)
```


```{r}
seq_data %<>% 
  mutate(m1_consumed = amt_init_mean*15/1000 - m1_R_end,
         m2_consumed = amt_init_mean*15/1000 - m2_R_end,
         m3_consumed = amt_init_mean*15/1000 - m3_R_end,
         m4_consumed = amt_init_mean*15/1000 - m4_R_end,
         m6c_consumed = amt_init_mean*15/1000 - m6c_R_end)
```



# Spores consumed

```{r, m1_num_sol}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  Z <- x[2]
  with(as.list(params),{
    dR <- -(length^gamma)*f*R
    dZ <- -(length^gamma)*f*Z
    res <- c(dR, dZ)
    list(res)}
    )
}

```

```{r, m1_sim}
m1_sim <- function(R, time, f, length, gamma, Z){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              Z=Z)
  params <- c(f=f,
              length=length,
              gamma=gamma)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  end <- slice_min(output, time)[,3] - slice_max(output, time)[,3]
  

  return(end)
}
```


```{r, m2_num_sol}
m2_num_sol <- function(t, x, params){
  R <- x[1]
  Z <- x[2]
  with(as.list(params),{
    dR <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*R
    dZ <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*Z
    res <- c(dR, dZ)
    list(res)}
    )
}
```

```{r, m2_sim}
m2_sim <- function(R, time, f, length, gamma, ref_t, arr_t, temp, Z){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              Z=Z)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp)
  output <- as.data.frame(lsoda(y=xstart, times, m2_num_sol, params))
  
  end <- slice_min(output, time)[,3] - slice_max(output, time)[,3]
  

  return(end)
}
```


```{r, m3_num_sol}
m3_num_sol <- function(t, x, params){
  R <- x[1]
  Z <- x[2]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(1+f*(length^gamma)*h*R))
    dZ <- -((f*length^gamma*Z)/(1+f*(length^gamma)*h*R))
    res <- c(dR, dZ)
    list(res)}
    )
}
```


```{r, m3_sim}
m3_sim <- function(R, time, f, length, gamma, h, Z){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              Z=Z)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m3_num_sol, params))
  
  end <- slice_min(output, time)[,3] - slice_max(output, time)[,3]
  

  return(end)
}
```



```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  Z <- x[2]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    dZ <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma))/
              (1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))*Z
    res <- c(dR, dZ)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h, Z){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R,
              Z=Z)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  end <- slice_min(output, time)[,3] - slice_max(output, time)[,3]
  

  return(end)
}
```




```{r}
exposure <- 200
life_vol <- 50

seq_data %<>% mutate(m1_Z_end = mapply(m1_sim,
                                       R = resource*life_vol/1000,
                                       time = 1,
                                       f=m1_f/life_vol,
                                       length = length,
                                       gamma = 2,
                                       Z = exposure*life_vol))
```

```{r}
seq_data %<>% mutate(m2_Z_end = mapply(m2_sim,
                                       R = resource*life_vol/1000,
                                       time = 1,
                                       f=m2_f/life_vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m2_arr,
                                       temp = temp,
                                       Z = exposure*life_vol))
```

```{r}
seq_data %<>% mutate(m3_Z_end = mapply(m3_sim,
                                       R = resource*life_vol/1000,
                                       time = 1,
                                       f=m3_f/life_vol,
                                       length = length,
                                       gamma = 2,
                                       h = m3_h,
                                       Z = exposure*life_vol))
```

```{r}
seq_data %<>% mutate(m4_Z_end = mapply(m4_sim,
                                       R = resource*life_vol/1000,
                                       time = 1,
                                       f=m4_f/life_vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m4_arr,
                                       temp = temp,
                                       h = m4_h,
                                       Z = exposure*life_vol))
```

```{r}
seq_data %<>% mutate(m6c_Z_end = mapply(m4_sim,
                                       R = resource*life_vol/1000,
                                       time = 1,
                                       f=m6c_f/life_vol,
                                       length = length,
                                       gamma = 2,
                                       ref_t = 15,
                                       arr_t = m6c_arr,
                                       temp = temp,
                                       h = m6c_h*exp(m6c_w*temp),
                                       Z = exposure*life_vol))
```


```{r, eval=F}
saveRDS(seq_data, file=here("model_fitting","foraging","rate_fit.rds"))
```






