---
title: "full_interaction"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE}
library(here)
library(tidyverse)
library(deSolve)
library(magrittr)
library(bbmle)
library(latex2exp)
library(AICcmodavg)
```

```{r, set theme}
theme_set(theme_minimal())

```


```{r, real data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


vol <- 15
```

Some of the lengths are missing so we impute these missing values by using the average length from that treatment
```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))
```

```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

# Model 7 - Full Interaction Model

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.

```{r}
for(i in 1:3){
  for(j in 1:3){
    print(i*3 + j - 3) #fun check to make sure we count from 1 to 9
  }
}
```

```{r}
m7_ll <- function(f, arr_t_0.1, arr_t_0.5, arr_t_1, h_15, h_20, h_25){
  arr_t_vec <- c(arr_t_0.1, arr_t_0.5, arr_t_1)
  h_vec <- c(h_15, h_20, h_25)
  nll_vec <- c()
  for (i in 1:length(temp_IDs)){
  temp_data <- tmp %>% filter(temp == temp_IDs[i])

    for (j in 1:length(resource_IDs)){
    data <- temp_data %>% filter(resource == resource_IDs[j])
    output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                   length=data$mm, gamma=2, arr_t=arr_t_vec[j], ref_t=15, temp=data$temp, h=h_vec[i]*data$vol))
    colnames(output) <- "endpoint"
    data$end <- output$endpoint
    data %<>% mutate(resid = log(end) - log(amt_rem))
    
      nll <- dnorm(data$resid, 
                   mean = 0, 
                   sd = sd(data$resid, na.rm = T), 
                   log = T)
      nll_vec[i*3 + j - 3] <- -sum(nll, na.rm = T)
    }
  }
  sum(nll_vec)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7_f_fit <- mle2(m7_ll,
                skip.hessian = T,
                start=list(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h_15=0.1, h_20=0.1, h_25=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t_0.1=50, arr_t_0.5=50, arr_t_1=50, h_15=0.1, h_20=0.1, h_25=0.1), maxit=10000))
end_time <- Sys.time()
m7_runtime <- end_time-start_time
m7_runtime

coef(m7_f_fit)

saveRDS(m7_f_fit, file = here("mle","m7_f_fit.rds"))
```


# Model 7 - Full Interaction Model - continuous

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.


```{r}
m7a_ll <- function(f, arr_t, h){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t*data$resource, ref_t=15, temp=data$temp, h=h*data$vol*data$temp))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7a_f_fit <- mle2(m7a_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.1), maxit=10000))
end_time <- Sys.time()
m7a_runtime <- end_time-start_time
m7a_runtime

coef(m7a_f_fit)

saveRDS(m7a_f_fit, file = here("mle","m7a_f_fit.rds"))
```


# Model 7 - Full Interaction Model - linear-linear

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.


```{r}
m7b_ll <- function(f, arr_t, h, p, w){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=p*data$resource + arr_t, ref_t=15, temp=data$temp, h=(w*data$temp + h)*data$vol))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7b_f_fit <- mle2(m7b_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.1, p=1, w=0.01),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, -Inf, -Inf),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.1, p=1, w=0.01), maxit=10000))
end_time <- Sys.time()
m7b_runtime <- end_time-start_time
m7b_runtime

coef(m7b_f_fit)

saveRDS(m7b_f_fit, file = here("mle","m7b_f_fit.rds"))
```

# Model 7 - Full Interaction Model - exponential-exponential

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.


```{r}
m7c_ll <- function(f, arr_t, h, p, w){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t*exp(p*data$resource), ref_t=15, temp=data$temp, h=h*data$vol*exp(w*data$temp)))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7c_f_fit <- mle2(m7c_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.1, p=0.1, w=0.1),
                method = "L-BFGS-B",
                lower = c(f=0, arr_t=0, h=0, p=-Inf, w=-Inf),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.1, p=0.1, w=0.1), maxit=10000))
end_time <- Sys.time()
m7c_runtime <- end_time-start_time
m7c_runtime

coef(m7c_f_fit)

saveRDS(m7c_f_fit, file = here("mle","m7c_f_fit.rds"))
```

# Model 7 - Full Interaction Model - linear-exponential

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.


```{r}
m7d_ll <- function(f, arr_t, h, p, w){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=p*data$resource + arr_t, ref_t=15, temp=data$temp, h=h*data$vol*exp(w*data$temp)))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7d_f_fit <- mle2(m7d_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.1, p=1, w=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, -Inf, -Inf),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.1, p=1, w=0.1), maxit=10000))
end_time <- Sys.time()
m7d_runtime <- end_time-start_time
m7d_runtime

coef(m7d_f_fit)

saveRDS(m7d_f_fit, file = here("mle","m7d_f_fit.rds"))
```

# Model 7 - Full Interaction Model - exponential-linear

This is a full interaction model that will see if there are interactions between both temperature and resource on each other.


```{r}
m7e_ll <- function(f, arr_t, h, p, w){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t*exp(p*data$resource), ref_t=15, temp=data$temp, h=(w*data$temp + h)*data$vol))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m7e_f_fit <- mle2(m7e_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.1, p=0.1, w=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, -Inf, -Inf),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.1, p=0.1, w=0.1), maxit=10000))
end_time <- Sys.time()
m7e_runtime <- end_time-start_time
m7e_runtime

coef(m7e_f_fit)

saveRDS(m7e_f_fit, file = here("mle","m7e_f_fit.rds"))
```
