---
title: "interaction model parameters visualized"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F}
library(here)
source(here("base","src.R"))
library(ggnewscale)
```

# Note!!

This script needs to be fixed for the visualizations to account for h being changed for model 6c. h was fixed for this model so that it is not in units of per mL but that means that it does not align with everything else. Eventually, everything should be fixed so that it is not per mL for h but the get_rate function should be fixed so that the resource is per tube (i.e. divided by 15 because the tube was 1 tube/15mL...I think)



First, make basic plot that shows temperature gradient on x-axis, foraging rate on y-axis, and a geom layer for resource concentration. This will be the actual data and will be consistent between each of the model fit visualizations.

```{r, data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))
m0 <- readRDS(here("mle", "m0_f_fit.rds"))
m1 <- readRDS(here("mle", "m1_f_fit.rds"))


m2 <- readRDS(here("mle", "m2_f_fit.rds"))
m3 <- readRDS(here("mle", "m3_f_fit.rds"))

m4 <- readRDS(here("mle", "m4_f_fit.rds"))

m5 <- readRDS(here("mle", "m5_f_fit.rds"))
m5a <- readRDS(here("mle", "m5a_f_fit.rds"))
m5b <- readRDS(here("mle", "m5b_f_fit.rds"))
m5c <- readRDS(here("mle", "m5c_f_fit.rds"))

m6 <- readRDS(here("mle", "m6_f_fit.rds"))
m6a <- readRDS(here("mle", "m6a_f_fit.rds"))
m6b <- readRDS(here("mle", "m6b_f_fit.rds"))
m6c <- readRDS(here("mle", "m6c_f_fit.rds"))

m7 <- readRDS(here("mle", "m7_f_fit.rds"))
m7a <- readRDS(here("mle", "m7a_f_fit.rds"))
m7b <- readRDS(here("mle", "m7b_f_fit.rds"))
m7c <- readRDS(here("mle", "m7c_f_fit.rds"))
m7d <- readRDS(here("mle", "m7d_f_fit.rds"))
m7e <- readRDS(here("mle", "m7e_f_fit.rds"))
```

```{r}
m0_coef <- m0@coef

m4_coef <- m4@coef
m5_coef <- m5@coef
m5a_coef <- m5a@coef
m5b_coef <- m5b@coef
m5c_coef <- m5c@coef

m6_coef <- m6@coef
m6a_coef <- m6a@coef
m6b_coef <- m6b@coef
m6c_coef <- m6c@coef

m7_coef <- m7@coef
m7a_coef <- m7a@coef
m7b_coef <- m7b@coef
m7c_coef <- m7c@coef
m7d_coef <- m7d@coef
m7e_coef <- m7e@coef

gamma <- 2
ref_t <- 15
vol <- 15
mean_time <- mean(data$time/60/24)
mean_length <- mean(data$mm, na.rm=T)
```

```{r, units}
data_summ %<>% mutate(rate_len_mean = rate_len_mean*60*24,
                      rate_len_mean_se = rate_len_mean_se*60*24)
```


```{r}
temp_range <- seq(15,25,by=0.1)
resource_range <- seq(0.1,1,by=0.01)

seq_data <- tibble(temp=c(),
                   resourece=c())

for (i in 1:length(temp_range)){
  tmp <- tibble(temp = temp_range[i],
                resource = seq(0.1,1,by=0.01))
  seq_data %<>% bind_rows(., tmp)
}

m7_range <- seq_data
```

```{r, echo=F}
seq_data %<>% mutate(temp_factor = as.factor(case_when(temp==25 ~ 25,
                                             temp==20 ~ 20,
                                             temp==15 ~ 15)))
```


```{r}
data_summ_se <- data_summ %>% dplyr::select(temp, resource, rate_len_mean, rate_len_mean_se)
seq_data %<>% left_join(., data_summ_se)
```



# AIC

```{r}
getAIC <- function(model){
  return(2*length(coef(model))-(2*summary(model)@m2logL/-2))
}
```

Log-Likelihoods
```{r}
m4_aic <- getAIC(m4)

m5_aic <- getAIC(m5)
m5a_aic <- getAIC(m5a)
m5b_aic <- getAIC(m5b)
m5c_aic <- getAIC(m5c)

m6_aic <- getAIC(m6)
m6a_aic <- getAIC(m6a)
m6b_aic <- getAIC(m6b)
m6c_aic <- getAIC(m6c)

m7_aic <- getAIC(m7)
m7a_aic <- getAIC(m7a)
m7b_aic <- getAIC(m7b)
m7c_aic <- getAIC(m7c)
m7d_aic <- getAIC(m7d)
m7e_aic <- getAIC(m7e)
```


# plotting function

```{r}
seq_plot <- function(rate){
  seq_data %>% filter(temp %in% c(15,20,25)) %>%
  ggplot(.) +
  geom_line(aes(x=resource, 
                y=!!sym(rate),
                group=temp_factor,
                color=as.factor(temp_factor))) +
  geom_point(aes(x=resource, 
                  y=rate_len_mean, 
                  group = as.factor(temp), 
                  color = as.factor(temp),
                  shape = as.factor(temp)),
             size=3) + 
    geom_linerange(aes(x=resource, 
                       ymin=rate_len_mean-rate_len_mean_se,
                       ymax=rate_len_mean+rate_len_mean_se,
                       color=as.factor(temp))) +
#    scale_color_manual(values = c("#FFC107", "#1E88E5", "#D81B60")) +
    scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) +
  labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "") 
}

seq_plot_temp <- function(rate){
  seq_data %>% filter(resource %in% c(0.1, 0.5, 1)) %>%
  ggplot(.) +
  geom_line(aes(x=temp, 
                y=!!sym(rate),
                group=resource,
                color=as.factor(resource))) +
  geom_point(aes(x=temp, 
                  y=rate_len_mean, 
                  group = as.factor(resource), 
                  color = as.factor(resource),
                  shape = as.factor(resource))) +
        geom_linerange(aes(x=temp, 
                       ymin=rate_len_mean-rate_len_mean_se,
                       ymax=rate_len_mean+rate_len_mean_se,
                       color=as.factor(resource))) + 
    scale_color_manual(values = c("#CABD88", "#CA5216", "#65320D")) +
  labs(x="Temperature", y="Foraging rate (mL/day)", color="", shape="", title = "") 
}

```




# Fitting foraging rate

```{r}
fora_data <- data_summ %>% ggplot(., aes(x=as.factor(resource), y=rate_len_mean, color=as.factor(temp))) +
  geom_point(size=2) +
  geom_linerange(aes(ymin=rate_len_mean-rate_len_mean_se,
                     ymax=rate_len_mean+rate_len_mean_se)) +
#    scale_color_manual(values = c("#FFC107", "#1E88E5", "#D81B60")) +
    scale_color_manual(values = c("#619CFF", "#00BA38", "#F8766D")) +
  labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", title="Foraging Rate Assay")

fora_data 

ggsave("fora_data.png", fora_data, path=here("mle/fit_plots"))

```





Now let's get the results from the model
```{r}
m0_f <- as.numeric(m0_coef)
data_summ %<>% mutate(m0_rate = m0_f)
```


$$
observed\; f = \frac{fe^{T_{A}(1/T_{R}-1/T)}}{1 + fe^{T_{A}(1/T_{R}-1/T)}hR} \\
$$

```{r}
m1_coef <- coef(m1)
m1_f <- as.numeric(m1_coef[1])

data_summ %<>% mutate(m1_rate = mm_mean^gamma*m1_f)
seq_data %<>% mutate(m1_rate = mean_length^gamma*m1_f)
```


```{r}
m2_coef <- coef(m2)
m2_f <- as.numeric(m2_coef[1])
m2_arr <- as.numeric(m2_coef[2])

data_summ %<>% mutate(m2_rate = (mm_mean^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
seq_data %<>% mutate(m2_rate = (mean_length^gamma)*m2_f*exp(m2_arr*(1/ref_t - 1/temp)))
```


```{r}
m3_coef <- coef(m3)
m3_f <- as.numeric(m3_coef[1])
m3_h <- as.numeric(m3_coef[2])

data_summ %<>% mutate(m3_rate = ((m3_f)/(1+m3_f*m3_h*resource)))

seq_data %<>% mutate(m3_rate=((m3_f)/(1+m3_f*m3_h*resource)))
```



```{r}
get_rate <- function(f, arr, temp, h, resource){
  ((f*exp(arr*(1/ref_t - 1/temp)))/(1+f*exp(arr*(1/ref_t - 1/temp))*h*resource))
}
```



```{r}
m4_coef
m4_f <- as.numeric(m4_coef[1])
m4_arr <- as.numeric(m4_coef[2])
m4_h <- as.numeric(m4_coef[3])

data_summ %<>% mutate(m4_rate = mapply(get_rate, f=m4_f, arr=m4_arr, temp=data_summ$temp, h=m4_h, resource=data_summ$resource))

seq_data %<>% mutate(m4_rate = mapply(get_rate, f=m4_f, arr=m4_arr, temp=seq_data$temp, h=m4_h, resource=seq_data$resource))
```




```{r}
m5b_coef
m5b_f <- as.numeric(m5b_coef[1])
m5b_arr <- as.numeric(m5b_coef[2])
m5b_h <- as.numeric(m5b_coef[3])
m5b_p <- as.numeric(m5b_coef[4])

data_summ %<>% mutate(m5b_rate = mapply(get_rate, f=m5b_f, arr=data_summ$resource*m5b_p + m5b_arr, h=m5b_h, temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m5b_rate = mapply(get_rate, f=m5b_f, arr=seq_data$resource*m5b_p + m5b_arr, h=m5b_h, temp=seq_data$temp, resource=seq_data$resource))
  
m5c_coef
m5c_f <- as.numeric(m5c_coef[1])
m5c_arr <- as.numeric(m5c_coef[2])
m5c_h <- as.numeric(m5c_coef[3])
m5c_p <- as.numeric(m5c_coef[4])

  data_summ %<>% mutate(m5c_rate = mapply(get_rate, f=m5c_f, arr=m5c_arr*exp(data_summ$resource*m5c_p), h=m5c_h, temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m5c_rate = mapply(get_rate, f=m5c_f, arr=m5c_arr*exp(seq_data$resource*m5c_p), h=m5c_h, temp=seq_data$temp, resource=seq_data$resource))
```


```{r}
m6b_coef
m6b_f <- as.numeric(m6b_coef[1])
m6b_arr <- as.numeric(m6b_coef[2])
m6b_h <- as.numeric(m6b_coef[3])
m6b_w <- as.numeric(m6b_coef[4])

data_summ %<>% mutate(m6b_rate = mapply(get_rate, f=m6b_f, arr=m6b_arr, h=(m6b_h + m6b_w*data_summ$temp), temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m6b_rate = mapply(get_rate, f=m5c_f, arr=m6b_arr, h=(m6b_h + m6b_w*seq_data$temp), temp=seq_data$temp, resource=seq_data$resource))
  
m6c_coef
m6c_f <- as.numeric(m6c_coef[1])
m6c_arr <- as.numeric(m6c_coef[2])
m6c_h <- as.numeric(m6c_coef[3])/15
m6c_w <- as.numeric(m6c_coef[4])

  data_summ %<>% mutate(m6c_rate = mapply(get_rate, f=m6c_f, arr=m6c_arr, h=m6c_h*exp(m6c_w*data_summ$temp), temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m6c_rate = mapply(get_rate, f=m6c_f, arr=m6c_arr, h=m6c_h*exp(m6c_w*seq_data$temp), temp=seq_data$temp, resource=seq_data$resource))
```


```{r}

m7b_coef
m7b_f <- as.numeric(m7b_coef[1])
m7b_arr <- as.numeric(m7b_coef[2])
m7b_h <- as.numeric(m7b_coef[3])
m7b_p <- as.numeric(m7b_coef[4])
m7b_w <- as.numeric(m7b_coef[5])

  data_summ %<>% mutate(m7b_rate = mapply(get_rate, f=m7b_f, arr=data_summ$resource*m7b_p + m7b_arr, h=m7b_h + m7b_w*data_summ$temp, temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m7b_rate = mapply(get_rate, f=m7b_f, arr=seq_data$resource*m7b_p + m7b_arr, h=m7b_h + m7b_w*seq_data$temp, temp=seq_data$temp, resource=seq_data$resource))
  
m7c_coef
m7c_f <- as.numeric(m7c_coef[1])
m7c_arr <- as.numeric(m7c_coef[2])
m7c_h <- as.numeric(m7c_coef[3])
m7c_p <- as.numeric(m7c_coef[4])
m7c_w <- as.numeric(m7c_coef[5])

      data_summ %<>% mutate(m7c_rate = mapply(get_rate, f=m7c_f, arr=m7c_arr*exp(data_summ$resource*m7c_p), h=m7c_h*exp(m7c_w*data_summ$temp), temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m7c_rate = mapply(get_rate, f=m7c_f, arr=m7c_arr*exp(seq_data$resource*m7c_p), h=m7c_h*exp(m7c_w*seq_data$temp), temp=seq_data$temp, resource=seq_data$resource))
  
m7d_coef
m7d_f <- as.numeric(m7d_coef[1])
m7d_arr <- as.numeric(m7d_coef[2])
m7d_h <- as.numeric(m7d_coef[3])
m7d_p <- as.numeric(m7d_coef[4])
m7d_w <- as.numeric(m7d_coef[5])

      data_summ %<>% mutate(m7d_rate = mapply(get_rate, f=m7d_f, arr=data_summ$resource*m7d_p + m7d_arr, h=m7d_h*exp(m7d_w*data_summ$temp), temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m7d_rate = mapply(get_rate, f=m7d_f, arr=m7d_arr*exp(seq_data$resource*m7d_p), h=m7d_h*exp(m7d_w*seq_data$temp), temp=seq_data$temp, resource=seq_data$resource))
  
m7e_coef
m7e_f <- as.numeric(m7e_coef[1])
m7e_arr <- as.numeric(m7e_coef[2])
m7e_h <- as.numeric(m7e_coef[3])
m7e_p <- as.numeric(m7e_coef[4])
m7e_w <- as.numeric(m7e_coef[5])

      data_summ %<>% mutate(m7e_rate = mapply(get_rate, f=m7e_f, arr=m7e_arr*exp(data_summ$resource*m7e_p), h=m7e_h + m7e_w*data_summ$temp, temp=data_summ$temp, resource=data_summ$resource))
  seq_data %<>% mutate(m7e_rate = mapply(get_rate, f=m7e_f, arr=m7e_arr*exp(seq_data$resource*m7e_p), h=m7e_h + m7e_w*seq_data$temp, temp=seq_data$temp, resource=seq_data$resource))

```

```{r}
saveRDS(seq_data, file=here("rate_fit.rds"))
```




```{r}
m1_plot <- seq_plot("m1_rate") + labs(title = "Size-dependent model")
m2_plot <- seq_plot("m2_rate") + labs(title = "Temperature-dependent model")
m3_plot <- seq_plot("m3_rate") + labs(title = "Resource-dependent model")
m4_plot_base <- seq_plot("m4_rate") + labs(title = "Temp. and Res. dependent model")
m4_plot <- seq_plot("m4_rate") + labs(title = paste("No Interaction. AIC =", round(m4_aic, 3)))
m5b_plot <- seq_plot("m5b_rate") + labs(title = paste("arr_t(resource) ~ LINEAR. AIC =", round(m5b_aic, 3)))
m5c_plot <- seq_plot("m5c_rate") + labs(title = paste("arr_t(resource) ~ EXP. AIC =", round(m5c_aic, 3)))
m4_plot
m5b_plot
m5c_plot

ggsave("m1_fit.png", m1_plot, path=here("mle/fit_plots"))
ggsave("m2_fit.png", m2_plot, path=here("mle/fit_plots"))
ggsave("m3_fit.png", m3_plot, path=here("mle/fit_plots"))
ggsave("m4_fit_base.png", m4_plot_base, path=here("mle/fit_plots"))
ggsave("m4_fit.png", m4_plot, path=here("mle/fit_plots"))
ggsave("m5b_fit.png", m5b_plot, path=here("mle/fit_plots"))
ggsave("m5c_fit.png", m5c_plot, path=here("mle/fit_plots"))
```

```{r}
m6b_plot <- seq_plot("m6b_rate") + labs(title = paste("h(temp) ~ LINEAR. AIC =", round(m6b_aic, 3)))
m6c_plot <- seq_plot("m6c_rate") + labs(title = paste("h(temp) ~ EXP. AIC =", round(m6c_aic, 3)))
m4_plot
m6b_plot
m6c_plot


ggsave("m6b_fit.png", m6b_plot, path=here("mle/fit_plots"))
ggsave("m6c_fit.png", m6c_plot, path=here("mle/fit_plots"))

```

```{r}
m7b_plot <- seq_plot("m7b_rate") + labs(title = paste("arr_t-h ~ LINEAR-LINEAR AIC =", round(m7b_aic, 3)))
m7c_plot <- seq_plot("m7c_rate") + labs(title = paste("arr_t-h ~ EXP-EXP AIC =", round(m7c_aic, 3)))
m7d_plot <- seq_plot("m7d_rate") + labs(title = paste("arr_t-h ~ LINEAR-EXP AIC =", round(m7d_aic, 3)))
m7e_plot <- seq_plot("m7e_rate") + labs(title = paste("arr_t-h ~ EXP-LINEAR AIC =", round(m7e_aic, 3)))

m4_plot
m7b_plot
m7c_plot
m7d_plot
m7e_plot


ggsave("m7b_fit.png", m7b_plot, path=here("mle/fit_plots"))
ggsave("m7c_fit.png", m7c_plot, path=here("mle/fit_plots"))
ggsave("m7d_fit.png", m7d_plot, path=here("mle/fit_plots"))
ggsave("m7e_fit.png", m7e_plot, path=here("mle/fit_plots"))

```


Make a plot that shows the 3 best models

```{r}
best_three_fit <- seq_data %>% dplyr::select(resource, temp_factor, m7c_rate, m6c_rate, m7d_rate) %>%
  filter(temp_factor %in% c(15, 20, 25)) %>%
  mutate("exp-exp" = m7c_rate, "h(T)~exp" = m6c_rate, "lin-exp" = m7d_rate) %>%
  dplyr::select(-c(m7c_rate, m6c_rate, m7d_rate)) %>%
  pivot_longer(cols=c('exp-exp', 'h(T)~exp', 'lin-exp')) %>%
  ggplot(.,aes(x=resource, y=value, group = interaction(name, temp_factor),color=temp_factor)) +
  geom_line(aes(linetype=name)) +
  scale_linetype_manual(values = c(1, 3, 5)) +
  geom_point(data=data_summ, aes(x=resource, 
                            y=rate_len_mean, 
                            group = as.factor(temp), 
                            color = as.factor(temp),
                            shape = as.factor(temp))) + 
  labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "3 Best Models", linetype="Model") 

best_three_fit

ggsave("best_three_fit.png", best_three_fit, path=here("mle/fit_plots"))
```


```{r}
seq_data %>% na.omit() %>%
  ggplot(.) +
  geom_line(aes(x=resource, 
                y=m7c_rate,
                group=temp_factor,
                color="black")) +
  new_scale_color() +
  geom_line(aes(x=resource, 
                y=m6c_rate,
                group=temp_factor,
                color="blue")) +
  new_scale_color() +
  geom_line(aes(x=resource, 
                y=m7d_rate,
                group=temp_factor,
                color="purple")) +
  geom_point(data=data_summ, aes(x=resource, 
                            y=rate_len_mean, 
                            group = as.factor(temp), 
                            color = as.factor(temp),
                            shape = as.factor(temp))) + 
  labs(x="Resource", y="Foraging rate (mL/day)", color="Temperature", shape="Temperature", title = "") 

```





# Interaction parameters

## Resource on temp

How does arr_t vary over resources?

```{r}
m5_range <- tibble(resource = resource_range)
m5_range %<>% mutate(arr_t = m4_arr,
                     arr_t_b = resource*m5b_p + m5b_arr,
                     arr_t_c = m5c_arr*exp(m5c_p*resource))

m5_range %<>% pivot_longer(cols=c(arr_t, arr_t_b, arr_t_c))

arr_labels <- c(arr_t = "constant",
                arr_t_b = "linear",
                arr_t_c = "exp")

m5_arr_plot <- m5_range %>% ggplot(., aes(x=resource, y=value, group=name, color=name)) + geom_line() + 
  labs(x="Resource Concentration",
       y=expression("Arrhenius Temp."(T[A])),
       color="Interaction") + 
  scale_color_discrete(labels = arr_labels)

m5_arr_plot

ggsave("m5_arr_plot.png", m5_arr_plot, path=here("mle/fit_plots"))


```

```{r}
m6_range <- tibble(temp = temp_range)

m6_range %<>% mutate(h = m4_h*15,
                     h_b = (m6b_h*15 + m6b_w*temp),
                     h_c = (m6c_h*15*exp(m6c_w*temp)))

m6_range %<>% pivot_longer(cols=c(h, h_b, h_c))

h_labels <- c(h = "constant",
              h_b = "linear",
              h_c = "exp")

m6_h_plot <- m6_range %>% ggplot(., aes(x=temp, y=value, group=name, color=name)) + geom_line() + 
  labs(x="Temperature",
       y="Handling Time (h)",
       color="Interaction") + 
  scale_color_discrete(labels = h_labels)

m6_h_plot


ggsave("m6_h_plot.png", m6_h_plot, path=here("mle/fit_plots"))

```

```{r}
m7_arr_t_range <- m7_range %>% mutate(m4_arr = m4_arr,
                                      arr_b = resource*m7b_p + m7b_arr,
                               arr_c = m7c_arr*exp(m7c_p*resource),
                               arr_d = resource*m7d_p + m7d_arr,
                               arr_e = m7e_arr*exp(m7e_p*resource))
m7_h_range <- m7_range %>% mutate(m4_h = m4_h,
                                  h_b = (m7b_h + m7b_w*temp)*vol,
                               h_c = m7c_h*exp(m7c_w*temp)*vol,
                               h_d = m7d_h*exp(m7d_w*temp)*vol,
                               h_e = (m7e_h + m7e_w*temp)*vol)
```

```{r}
m7_arr_t_range %<>% pivot_longer(cols=c(m4_arr, arr_b,arr_c,arr_d,arr_e))

m7_h_range %<>% pivot_longer(cols=c(m4_h, h_b,h_c,h_d,h_e))
```


```{r}
m7_arr_labels <- c(m4_arr = "none",
                   arr_b = paste("LINEAR-linear\np =", round(m7b_p, 2)),
                   arr_c = paste("\nEXP-exp\np =", round(m7c_p, 2)),
                   arr_d = paste("\nLINEAR-exp\np =", round(m7d_p, 2)),
                   arr_e = paste("\nEXP-linear\np =", round(m7e_p, 2)))
m7_h_labels <- c(m4_h = "none",
                 h_b = paste("linear-LINEAR\nw =", round(m7b_w, 2)),
                 h_c = paste("\nexp-EXP\nw =", round(m7c_w, 2)),
                 h_d = paste("\nlinear-EXP\nw =", round(m7d_w, 2)),
                 h_e = paste("\nexp-LINEAR\nw =", round(m7e_w, 2)))
```

```{r}
m7_arr_plot <- m7_arr_t_range %>% ggplot(.,aes(x=resource, y=value, group=name, color=name)) + geom_line() +
  labs(x = "Resource concentration",
       y = expression("Arrhenius Temp."(T[A])),
       color = "Interaction",
       title = "Interactions across Resource") + 
  scale_color_manual(values = c("#004D40", "#1E88E5", "#D81B60", "#FFC107", "#B8C50C"),
                     labels = m7_arr_labels)

m7_arr_plot

ggsave("m7_arr_plot.png", m7_arr_plot, path=here("mle/fit_plots"))
```


```{r}
m7_h_plot <- m7_h_range %>% ggplot(.,aes(x=temp, y=value, group=name, color=name)) + 
  geom_line() +
  labs(x = "Temperature",
       y = "Handling Time (h)",
       color = "Interaction",
       title = "Interactions across Temperature") + 
  scale_color_manual(values = c("#004D40", "#1E88E5", "#D81B60", "#FFC107", "#B8C50C"),
                     labels = m7_h_labels)

m7_h_plot

ggsave("m7_h_plot.png", m7_h_plot, path=here("mle/fit_plots"))
```




