---
title: "foraging rate estimates"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, message=FALSE}
library(here)
library(tidyverse)
library(deSolve)
library(magrittr)
library(bbmle)
library(latex2exp)
library(AICcmodavg)
```

```{r, set theme}
theme_set(theme_minimal())

```


```{r, real data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


vol <- 15
```

Some of the lengths are missing so we impute these missing values by using the average length from that treatment
```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))


```




# Model 0 - Basic model


Let's try this with the same units as the foraging rate data. ml/min. So R should be mgC/mL and S should be hosts/mL
$$
\frac{dR}{dt} = -fRS \\
$$

```{r, m0_num_sol}
m0_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -f*R
    res <- c(dR)
    list(res)}
    )
}

```



```{r, m0_sim}
m0_sim <- function(R, time, f){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f)
  output <- as.data.frame(lsoda(y=xstart, times, m0_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m0_ll}
m0_ll <- function(f, sd_est){
  data <- tmp
  m0_end <- as.data.frame(mapply(m0_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol))
  colnames(m0_end) <- "m0_end"
  data$end <- m0_end$m0_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd(data$resid),
    #              log = T)
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$amt_rem*vol/1000,
    #              mean = mean(data$end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$sqrt_data_end,
    #              mean = mean(data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$log_data_end,
    #              mean = mean(data$log_model_end),
    #              sd = sd_est,
    #              log = T)
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }

    nll_sum
    #-sum(nll)
}
```



```{r, m0_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m0_f_fit <- mle2(minuslogl=m0_ll, skip.hessian=T,
                start=list(f=10,
                           sd_est = 0.01),
                control=list(parscale=c(f=10,
                                        sd_est = 0.01), maxit=10000))
end_time <- Sys.time()
m0_runtime <- end_time - start_time
m0_runtime

coef(m0_f_fit)

saveRDS(m0_f_fit, file = here("mle","m0_f_fit.rds"))

```

```{r, m0_f_fit output}
summary(readRDS(here("mle","m0_f_fit.rds")))
```


# Model 1 - Independent model

Recreate Alex's results from Model 1

$$
\frac{dR}{dt} = -L^{\gamma} fRS\\
$$

```{r, m1_num_sol}
m1_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*R
    res <- c(dR)
    list(res)}
    )
}

```

```{r, m1_sim}
m1_sim <- function(R, time, f, length, gamma){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma)
  output <- as.data.frame(lsoda(y=xstart, times, m1_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m1_ll}
m1_ll <- function(f, sd_est){
  data <- tmp
  m1_end <- as.data.frame(mapply(m1_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2))
  colnames(m1_end) <- "m1_end"
  data$end <- m1_end$m1_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd(data$resid),
    #              log = T)
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$amt_rem*vol/1000,
    #              mean = mean(data$end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$sqrt_data_end,
    #              mean = mean(data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$log_data_end,
    #              mean = mean(data$log_model_end),
    #              sd = sd_est,
    #              log = T)
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }

    nll_sum
    #-sum(nll)
}
```


Now we use the optimizer
```{r, m1_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m1_f_fit <- mle2(minuslogl=m1_ll, skip.hessian=T, #method="Nelder-Mead", 
              start=list(f=10,
                         sd_est = 0.01),
              control=list(parscale=c(f=10, sd_est = 0.001), maxit=10000))
end_time <- Sys.time()
m1_runtime <- end_time - start_time
m1_runtime

coef(m1_f_fit)

saveRDS(m1_f_fit, file = here("mle","m1_f_fit.rds"))
```

```{r, m1_f_fit}
summary(readRDS(here("mle","m1_f_fit.rds")))
```



# Model 2 - Temperature-dependent model


$$
\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\\

\frac{1}{RS}\frac{dR}{dt} = -L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)} RS\frac{1}{RS}\\

-L^{\gamma}fe^{T_{A}(1/T_{R}-1/T)}\\
$$


```{r, m2_num_sol}
m2_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -(length^gamma)*f*exp(arr_t*(1/ref_t - 1/temp))*R
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m2_sim}
m2_sim <- function(R, time, f, length, gamma, ref_t, arr_t, temp){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp)
  output <- as.data.frame(lsoda(y=xstart, times, m2_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```


```{r, m2_ll}
m2_ll <- function(f, arr_t, sd_est){
  data <- tmp
  m2_end <- as.data.frame(mapply(m2_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp))
  colnames(m2_end) <- "m2_end"
  data$end <- m2_end$m2_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd(data$resid),
    #              log = T)
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$amt_rem*vol/1000,
    #              mean = mean(data$end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$sqrt_data_end,
    #              mean = mean(data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$log_data_end,
    #              mean = mean(data$log_model_end),
    #              sd = sd_est,
    #              log = T)
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }

    nll_sum
    #-sum(nll)
}
```





```{r, m2_mle, eval = FALSE}
start_time <- Sys.time()
tmp <- data
m2_f_fit <- mle2(m2_ll,
                skip.hessian = T,
                start=list(f=5,
                           arr_t=50,
                           sd_est=0.001),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=5, arr_t=50, sd_est=0.001), maxit=10000))

end_time <- Sys.time()
m2_runtime <- end_time - start_time
m2_runtime

coef(m2_f_fit)

saveRDS(m2_f_fit, file = here("mle","m2_f_fit.rds"))
```

```{r, m2_f_fit}
summary(readRDS(here("mle", "m2_f_fit.rds")))
```




# Model 3 - Resource-dependent model

I try to incorporate resource-dependence by using an equation for the type II functional response.



$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{1 + fL^{\gamma}hR} \\

\frac{1}{RS}\frac{dR}{dt} = - \frac{fL^{\gamma}R}{1 + fL^{\gamma}hR} \frac{1}{RS}\\

per-capita f = - \frac{fL^{\gamma}}{1 + fL^{\gamma}hR} \\
$$




```{r, m3_num_sol}
m3_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(1+f*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```


```{r, m3_sim}
m3_sim <- function(R, time, f, length, gamma, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m3_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m3_ll}
m3_ll <- function(f, h, sd_est){
  data <- tmp
  output <- as.data.frame(mapply(m3_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, h=h))
  colnames(output) <- "end"
  data$end <- output$end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd(data$resid),
    #              log = T)
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$amt_rem*vol/1000,
    #              mean = mean(data$end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$sqrt_data_end,
    #              mean = mean(data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$log_data_end,
    #              mean = mean(data$log_model_end),
    #              sd = sd_est,
    #              log = T)
    nll_sum <- 0
    for(i in 1:length(treatment_IDs)){
      treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
      nll <- dnorm(treatment_data$sqrt_data_end,
                 mean = mean(treatment_data$sqrt_model_end),
                 sd = sd_est,
                 log = T)
      nll_sum <- -sum(nll) + nll_sum
    }

    nll_sum
    #-sum(nll)
}
```


```{r, m3_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m3_f_fit <- mle2(m3_ll,
                skip.hessian = T,
                start=list(f=40,
                           h=100,
                           sd_est=0.001),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=40, h=100, sd_est=0.001), maxit=10000))
end_time <- Sys.time()
m3_runtime <- end_time-start_time
m3_runtime

coef(m3_f_fit)

saveRDS(m3_f_fit, file = here("mle","m3_f_fit.rds"))
```

```{r, m3_f_fit}
summary(readRDS(here("mle", "m3_f_fit.rds")))
```

# Model 3b - Half-Saturation Method


I try to incorporate resource-dependence by using an equation for the type II functional response.



$$
\frac{dR}{dt} = - \frac{fL^{\gamma}R}{k + R} \\
$$




```{r, m3a_num_sol}
m3a_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*length^gamma*R)/(k+R))
    res <- c(dR)
    list(res)}
    )
}
```


```{r, m3a_sim}
m3a_sim <- function(R, time, f, length, gamma, k){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              k=k)
  output <- as.data.frame(lsoda(y=xstart, times, m3a_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m3a_ll}
m3a_ll <- function(f, k){
  data <- tmp
  output <- as.data.frame(mapply(m3a_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, k=k))
  colnames(output) <- "end"
  data$end <- output$end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid), 
                 log = T)
    -sum(nll)
}
```


```{r, m3a_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m3a_f_fit <- mle2(m3a_ll,
                skip.hessian = T,
                start=list(f=5,
                           k=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0),
                upper = c(Inf, Inf),
                control=list(parscale=c(f=5, k=0.1), maxit=10000))
end_time <- Sys.time()
m3a_runtime <- end_time-start_time
m3a_runtime

coef(m3a_f_fit)

saveRDS(m3a_f_fit, file = here("mle","m3a_f_fit.rds"))
```

```{r, m3a_f_fit}
#summary(readRDS(here("mle", "m3_f_fit.rds")))
```



# Model 4 - Temperature and resource-dependent model

I try to incorporate both here by just smashing everything together.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{1 + fe^{T_{A}(1/T_{R}-1/T)}L^{\gamma}hR} \\
$$


```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m4_ll}
m4_ll <- function(f, arr_t, h, sd_est){
  data <- tmp
  m4_end <- as.data.frame(mapply(m4_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, h=h))
  colnames(m4_end) <- "m4_end"
  data$end <- m4_end$m4_end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  data %<>% mutate(sqrt_model_end = sqrt(end),
                   sqrt_data_end = sqrt(amt_rem*vol/1000),
                   log_model_end = log(end),
                   log_data_end = log(amt_rem*vol/1000))
  
    nll <- dnorm(data$resid,
                 mean = 0,
                 sd = sd(data$resid),
                 log = T)
    # nll <- dnorm(data$resid,
    #              mean = 0,
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$amt_rem*vol/1000,
    #              mean = mean(data$end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$sqrt_data_end,
    #              mean = mean(data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll <- dnorm(data$log_data_end,
    #              mean = mean(data$log_model_end),
    #              sd = sd_est,
    #              log = T)
    # nll_sum <- 0
    # for(i in 1:length(treatment_IDs)){
    #   treatment_data <- data %>% filter(treatment_ID == treatment_IDs[i])
    #   nll <- dnorm(treatment_data$sqrt_data_end,
    #              mean = mean(treatment_data$sqrt_model_end),
    #              sd = sd_est,
    #              log = T)
    #   nll_sum <- -sum(nll) + nll_sum
    # }
    # 
    # nll_sum
    -sum(nll)
}
```



```{r, m4_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m4_f_fit <- mle2(m4_ll,
                skip.hessian = T,
                start=list(f=5, arr_t=50, h=100, sd_est=0.001),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=5, arr_t=50, h=100, sd_est=0.001), maxit=10000))
end_time <- Sys.time()
m4_runtime <- end_time-start_time
m4_runtime

coef(m4_f_fit)

saveRDS(m4_f_fit, file = here("mle","m4_f_fit.rds"))
```

```{r, m4_f_fit}
summary(readRDS(here("mle","m4_f_fit.rds")))
```


# Model 4a - Temperature and resource-dependent model - half saturation method

I try to incorporate both here by just smashing everything together.

$$
\frac{dR}{dt} = -\frac{fe^{T_{A}(1/T_{R}-1/T)} L^{\gamma}R}{k + R} \\
$$


```{r, m4_num_sol}
m4a_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(k+R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4a_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, k){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              k=k)
  output <- as.data.frame(lsoda(y=xstart, times, m4a_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

```{r, m4_ll}
m4a_ll <- function(f, arr_t, k){
  data <- tmp
  output <- as.data.frame(mapply(m4a_sim, R=data$amt_init*data$vol/1000, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, k=k))
  colnames(output) <- "end"
  data$end <- output$end
  #data %<>% mutate(resid = log(end) - log(amt_rem*vol/1000))
  data %<>% mutate(resid = sqrt(end) - sqrt(amt_rem*vol/1000))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid), 
                 log = T)
    -sum(nll)
}
```


```{r, m4_mle, eval = F}
start_time <- Sys.time()
tmp <- data
m4a_f_fit <- mle2(m4a_ll,
                skip.hessian = T,
                start=list(f=5, arr_t=50, k=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=5, arr_t=50, k=0.1), maxit=10000))
end_time <- Sys.time()
m4a_runtime <- end_time-start_time
m4a_runtime

coef(m4a_f_fit)

saveRDS(m4a_f_fit, file = here("mle","m4a_f_fit.rds"))
```

```{r, m4_f_fit}
#summary(readRDS(here("mle","m4a_f_fit.rds")))
```


# Parameter Check

How different are the parameters for each treatment?

```{r, eval=F}
test_fit <- list(c())
for(i in 1:length(treatment_IDs)){
  tmp <- data %>% filter(treatment_ID==treatment_IDs[i])
  test_fit[i] <- mle2(m4_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=1), maxit=10000))
}

for(i in 1:length(treatment_IDs)){
  print(test_fit[[i]]@coef)
}
```












