---
title: "temp_on_rsc"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE}
library(here)
library(tidyverse)
library(deSolve)
library(magrittr)
library(bbmle)
library(latex2exp)
library(AICcmodavg)
```

```{r, set theme}
theme_set(theme_minimal())

```


```{r, real data}
data <- readRDS(here("processed_data","foraging_raw.rds"))
data_summ <- readRDS(here("processed_data", "foraging.rds"))

data %<>% mutate(treatment_ID = paste(temp, resource, sep = "_"))

data %<>% mutate(resource_tot = resource*vol) #resource_tot is the total amount of resources in our tube. resource concentration * total volume of tube 

treatment_IDs <- unique(data$treatment_ID)
resource_IDs <- unique(data$resource)
temp_IDs <- unique(data$temp)


vol <- 15
```

Some of the lengths are missing so we impute these missing values by using the average length from that treatment
```{r}
mean_length_summ <- data_summ %>% dplyr::select(temp, resource, mm_mean)
data %<>% left_join(., mean_length_summ)
data %<>% mutate(mm = if_else(!is.na(mm), mm, mm_mean))
```

```{r, m4_num_sol}
m4_num_sol <- function(t, x, params){
  R <- x[1]
  with(as.list(params),{
    dR <- -((f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*R)/(1+f*exp(arr_t*(1/ref_t - 1/temp))*(length^gamma)*h*R))
    res <- c(dR)
    list(res)}
    )
}
```

```{r, m4_sim}
m4_sim <- function(R, time, f, length, gamma, arr_t, ref_t, temp, h){
  times <- seq(0, time, by=0.01)
  xstart <- c(R=R)
  params <- c(f=f,
              length=length,
              gamma=gamma,
              arr_t=arr_t,
              ref_t=ref_t,
              temp=temp,
              h=h)
  output <- as.data.frame(lsoda(y=xstart, times, m4_num_sol, params))
  
  r_end <- slice_max(output, time)[,2]
  
  # r_end <- ifelse(r_end<0, 0, r_end) #ensure that final resource concentration is never negative
  #probably unnecessary
  return(r_end)
}
```

# Model 6 - Temperature on Resource Interaction

This model uses a different handling time for each temperature level to see if there is an effect of temperature on the resource effect.

```{r}
m6_ll <- function(f, arr_t, h_15, h_20, h_25){
  h_vec <- c(h_15, h_20, h_25)
  nll_vec <- c()
  for (i in 1:length(temp_IDs)){
  data <- tmp %>% filter(temp == temp_IDs[i])
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, h=h_vec[i]*data$vol))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    nll_vec[i] <- -sum(nll, na.rm = T)
  }
  sum(nll_vec)
}
```


```{r}
start_time <- Sys.time()
tmp <- data
m6_f_fit <- mle2(m6_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h_15=0.1, h_20=0.1, h_25=0.1),
                method = "L-BFGS-B",
                lower = c(0, 0, 0, 0, 0),
                upper = c(Inf, Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h_15=0.1, h_20=0.1, h_25=0.1), maxit=10000))
end_time <- Sys.time()
m6_runtime <- end_time-start_time
m6_runtime

coef(m6_f_fit)

saveRDS(m6_f_fit, file = here("mle","m6_f_fit.rds"))
```

# Model 6 - Temperature on Resource Interaction - continuous

This model uses a different handling time that is temperature-dependent

```{r}
m6a_ll <- function(f, arr_t, h){

  data <- tmp 
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp,
                                 h=h*data$vol*data$temp))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)

}
```


```{r}
start_time <- Sys.time()
tmp <- data
m6a_f_fit <- mle2(m6a_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.01),
                method = "L-BFGS-B",
                lower = c(0, 0, 0),
                upper = c(Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.01), maxit=10000))
end_time <- Sys.time()
m6a_runtime <- end_time-start_time
m6a_runtime

coef(m6a_f_fit)

saveRDS(m6a_f_fit, file = here("mle","m6a_f_fit.rds"))
```


# Model 6 - Temperature on Resource Interaction - linear

This model uses a different handling time that is temperature-dependent


```{r}
m6b_ll <- function(f, arr_t, h, w){

  data <- tmp 
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, 
                                 h=(h + w*data$temp)*data$vol))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)

}
```


```{r}
start_time <- Sys.time()
tmp <- data
m6b_f_fit <- mle2(m6b_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=0.01, w=0.01),
                method = "L-BFGS-B",
                lower = c(f=0, arr_t=0, h=0, w=-Inf),
                upper = c(Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=0.01, w=0.01), maxit=10000))
end_time <- Sys.time()
m6b_runtime <- end_time-start_time
m6b_runtime

coef(m6b_f_fit)

saveRDS(m6b_f_fit, file = here("mle","m6b_f_fit.rds"))
```


# Model 6 - Temperature on Resource Interaction - exponential

This model uses a different handling time that is temperature-dependent


```{r}
m6c_ll <- function(f, arr_t, h, w){

  data <- tmp 
  output <- as.data.frame(mapply(m4_sim, R=data$amt_init, time=data$time/60/24, f=f/data$vol,
                                 length=data$mm, gamma=2, arr_t=arr_t, ref_t=15, temp=data$temp, 
                                 h=h*exp(w*data$temp)))
  colnames(output) <- "endpoint"
  data$end <- output$endpoint
  data %<>% mutate(resid = log(end) - log(amt_rem))
  
    nll <- dnorm(data$resid, 
                 mean = 0, 
                 sd = sd(data$resid, na.rm = T), 
                 log = T)
    -sum(nll, na.rm = T)

}
```


```{r}
start_time <- Sys.time()
tmp <- data
m6c_f_fit <- mle2(m6c_ll,
                skip.hessian = T,
                start=list(f=10, arr_t=50, h=10, w=0.1),
                method = "L-BFGS-B",
                lower = c(f=0, arr_t=0, h=0, w=-Inf),
                upper = c(Inf, Inf, Inf, Inf),
                control=list(parscale=c(f=10, arr_t=50, h=10, w=0.1), maxit=10000))
end_time <- Sys.time()
m6c_runtime <- end_time-start_time
m6c_runtime

coef(m6c_f_fit)

saveRDS(m6c_f_fit, file = here("mle","m6c_f_fit.rds"))
```

