---
title: "Power Analysis"
author: "Daniel Suh"
date: "2/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, Packages, message=F}
library(tidyverse)
library(magrittr)
library(pwr)
```



Power analyses require values for four different variables:

 - *Effect Size.* The quantified magnitude of a result present in the population. Effect size is calculated using a specific statistical measure, such as Pearson’s correlation coefficient for the relationship between variables or Cohen’s d for the difference between groups.
 - *Sample Size.* The number of observations in the sample.
 - *Significance.* The significance level used in the statistical test, e.g. alpha. Often set to 5% or 0.05.
 - *Statistical Power.* The probability of accepting the alternative hypothesis if it is true.
 
 Typical method includes using pilot data to estimate effect size to be used for power analysis. However, some suggest that multiple biases can occur in a priori power analyses using pilot data that lead to unpowered studies. [https://doi.org/10.1016/j.jesp.2017.09.004] These authors suggest to skip pilot studies and instead arbitrarily choose a medium effect size or to perform sequential analyses where data are collected in multiple phases as needed.
 
 To start, I will just try to do a power analysis with an arbitrary effect size of Cohen's d of 0.8, significance of 0.05, and power of 0.8.
 
 one-way anova power analysis
```{r}
pwr.anova.test(k = 3, n = , f = 0.4, sig.level = 0.05, power = 0.8)
```
 
